---
title: "Exploratory data analysis for the new data"
author: "Oluwayomi Akinfenwa"
date: "08/02/2024"
output:
  pdf_document:
    toc: yes
    toc_depth: '4'
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

Creating a folder to store all the plots

```{r, libraries, include = FALSE}
if (!dir.exists(here::here("Saved_Plots")))
  dir.create(here::here("Saved_Plots"))
```

Sourcing the file containing all the data needed for this analysis from the Rmd file named: 01_PISA_Analysis_Data.Rmd.
This file contains the raw data from OECD website and all the necessary data for this analysis.

```{r loading the data}
sys.source("01_BRMS_PISA_Analysis_Data.R", envir = knitr::knit_global())
```

### Exploratory data analysis

The first step of this analysis is to fit a separate linear model on the data for each country and visualise the model fit grouping the countries by their region and income categories.

**Fitting a linear regression model on the data set**
**Fitting a linear regression model on the data set**

```{r}
library(broom)
## The function reframe- creates a new data-frame by applying functions (in the previous line of code) to columns of an existing data frame.

#Weighted least squares. The weight is the reciprocal of the square of the standard error.
Country_Model <- PISA_Europe_Data |>
  nest_by(Country) |>
  mutate(mod = list(lm(math ~ year_orig,  data = data))) |>
  reframe(tidy(mod))|>
   select(Country, term, estimate)

### Tidying the estimates
### We are interested in arranging the countries according to their increasing slope.
Country_Model_IS <- Country_Model  |>
   pivot_wider(values_from = estimate, names_from = term) |>
   rename("slope" = "year_orig") |>
  mutate(slopesign = sign(slope)) |>
  left_join(Country_region, join_by(Country)) |>
  select(-c(Country_num, region_num)) |>
  arrange(slope)
```

#### Visualisations - Creating the plots.

```{r}
##Merging the slope-sign with the Pisa data so that i can rearrange by both country and slope-sign
Slopesign <- Country_Model_IS |>
  select(Country, slope)

PISA_Europe_Data1 <- PISA_Europe_Data |>
  left_join(Slopesign, join_by(Country))

PISA_Europe_Data1$facet <- factor(PISA_Europe_Data1$Region, 
                  levels = c("Western Europe", "Northern Europe", "Eastern Europe","Southern Europe"))

Country_Model_IS$facet <- factor(Country_Model_IS$Region, 
                  levels = c("Western Europe","Northern Europe","Eastern Europe", "Southern Europe"))


## Our interest is to create a data frame with both region and country as a dataframe assigning colors to them.
Region_color <- c("Eastern Europe" = "lightsteelblue2",
                  "Northern Europe"="lavenderblush2", 
                  "Southern Europe"= "bisque2",
                  "Western Europe"="#ACE1AF")

Colors <- country_region |>
  mutate(color = Region_color[Region]) |>mutate(Country = stringr::str_replace_all(Country, stringr::fixed("Bosnia& Herzegovina"), "Bosnia&\nHerzegovina")) |>
  mutate(Country = stringr::str_replace_all(Country, stringr::fixed("United Kingdom"), "United\nKingdom")) |>
  select(group = Country, color)|>
  as.data.frame()

Reg <- data.frame(group =paste(unique(country_region$Region)),
          color = c("bisque2","#ACE1AF","lightsteelblue2","lavenderblush2"))

Reg <-Reg |>
mutate(group = recode_factor(group,
                             `Southern Europe` = "Southern\nEurope",
                           `Western Europe` = "Western\nEurope" ,
                          `Eastern Europe` = "Eastern\nEurope" ,
                         `Northern Europe` = "Northern\nEurope"))

#This is necessary for the grid of the plots to specify the colors for each region.
Group <- rbind(Reg, Colors)
```

#### Visualising the independent model fit on each country - Grouping by region.

```{r}
## In ascending slope
pdf("Saved_Plots/fits_grouped_by_Region.pdf",
    width = 11.5,
    height = 9.3)
P <- ggplot(data = PISA_Europe_Data1,
            aes(x=year_orig, y=math))+
  geom_point(color = "grey35")+
  geom_abline(data= Country_Model_IS, 
              aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  facet_ragged_rows(vars(facet = facet), 
                    vars(reorder(Country, slope)),
                    scales = "free_y",
                    switch = "y",
                  labeller=label_wrap_gen(width=6))+
  scale_x_continuous(breaks = seq(-15,0,3),labels = function(x) x+2018) +
  scale_y_continuous(position = "right")+
  labs(x= " ", y = " ",  color = "Slope") + 
  scale_color_manual(values = c("firebrick2", "blue"), labels = c("negative", "positive"), na.translate = F)+
  theme(legend.position = "bottom", legend.box.spacing = unit(-0.6, "lines"),
        legend.text = element_text(size = 11.5),
        panel.spacing.y = unit(1.2, "lines"),
        plot.subtitle = element_text(family = "Serif"),
        axis.text.x = element_text(angle = 55, hjust = 0.5, vjust = 0.5,size = 8.5, face = "bold"),strip.text.x = element_text(size = 9.42,face = "bold"),
        strip.text.y = element_text(size = 10,face = "bold"),
        axis.text.y = element_text(size = 10,face = "bold"))+
  ggtitle("Separate linear model fit of average maths scores over time for each country")

G <- ggplotGrob(P)
# g$layout$name
Strip <- which(grepl('strip', G$layout$name)) 


for (i in Strip){
  j <- which(grepl('rect', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- G$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, Group$group)
  if (isTRUE( !is.na(st))){
    G$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Group[st, "color"]
  }
}

grid.draw(G)

dev.off()
```



#### Visualising the independent model fit on each country - Grouping by income.

```{r}
pdf("Saved_Plots/fit_grouped_by income.pdf",
    width = 11.5,
    height = 9.3)

middle_income <- ggplot(data = filter(PISA_Europe_Data1, Income== "Middle Income"),
         aes(x=year_orig, y=math))+
  geom_point(color = "grey35")+
   geom_abline(data= filter(Country_Model_IS, Income== "Middle Income"), 
               aes(slope=slope, intercept= `(Intercept)`),color = "blue")+
  ggh4x::facet_wrap2(vars(Income, reorder(Country, slope)), ncol = 10,
  strip = ggh4x::strip_nested(bleed = TRUE))+
  labs(x = " ", y = " ") +
  scale_y_continuous(position = "right",breaks = seq(350,500, 50))+
  scale_x_continuous(breaks = seq(-15,0,3),labels = function(x) x+2018)+
  theme(strip.background = element_rect(fill="aquamarine2"),
    strip.text.x = element_text(size = 9.2,face = "bold", color = "black"),
        axis.text.y = element_text(size = 10,face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5,face = "bold"),
        plot.title = element_text(hjust = 0.5))

high_income <- ggplot(data = filter(PISA_Europe_Data1, Income== "High Income"),
         aes(x=year_orig, y=math))+
   geom_point(color = "grey35")+
   geom_abline(data= filter(Country_Model_IS, Income== "High Income"), 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  scale_y_continuous(position = "right")+
  ggh4x::facet_wrap2(vars(Income, reorder(Country, slope)), ncol = 10, 
                     strip = ggh4x::strip_nested(bleed = TRUE))+
  ggtitle("Separate linear model fit of average math scores for each country")+
  scale_color_manual(values = c("firebrick2", "blue"), labels = c("negative", "positive"))+ 
  labs(x = " ", y = " ", color = "Slope") +
 scale_x_continuous(breaks = seq(-15,0,3),labels = function(x) x+2018) +
  theme(strip.background = element_rect(fill="thistle3"),
    strip.text.x = element_text(size = 9.2,face = "bold", color = "black"),
        axis.text.y = element_text(size = 10,face = "bold"),
        axis.text.x = element_blank(),
        axis.ticks.x=element_blank(),
        panel.spacing.y = unit(1, "lines"),
        legend.text = element_text(size = 11.5),
        plot.title = element_text(hjust = 0.5))

high_income/middle_income +
  plot_layout(widths = 1, heights = c(5, 1), guides = "collect") &
   theme(legend.position = "bottom",
         legend.box.spacing = unit(-0.6, "lines"))

dev.off()
```