---
title: "Visuals to compare the model estimates using ggragged"
author: "Oluwayomi Akinfenwa"
date: "18/03/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Sourcing the Rmd file containing the fitted models and the extracted estimates.

```{r, libraries, include = FALSE}
source(knitr::purl("04_BRMS_Model_Estimates.Rmd"))

#sys.source("04_BRMS_Model_Estimates.R", envir = knitr::knit_global())
```

A plot showing the model estimates and credible intervals (80% and 95%), facet by country and connecting the dots for the estimates from the 4 models (An independent model fits, Country-specific model and Region, Income, Income-Region hierarchical models) using *ggragged*.

```{r}
## Hierarchical estimates
##Intercepts
Combined_Int_estimates <- rbind(Country_Int_est,Region_Int_est, Income_Int_est,
                              IncomeRegion_Int_est) |>
  arrange(Country)

Combined_Slop_estimates <- rbind(Country_Slop_est,Region_Slop_est, Income_Slop_est,
                              IncomeRegion_Slop_est)|>
  arrange(Country)

Combined_Int_estimates$Model <- factor(Combined_Int_estimates$Model, 
                  levels = c("Country \nModel","Region \nModel", "Income \nModel", "Income-Region \nModel"))

Combined_Slop_estimates$Model <- factor(Combined_Slop_estimates$Model, 
                  levels = c("Country \nModel","Region \nModel", "Income \nModel", "Income-Region \nModel"))

## Countries estimates
Combined_Int_Estimates <- rbind(CountryInd_Int_Est,
                            Country_Int_Est,Region_Int_Est,
                            Income_Int_Est,Income_Region_Int_Est) |>
  arrange(Country)

Combined_Slop_Estimates <- rbind(CountryInd_Slop_Est,
                            Country_Slop_Est,Region_Slop_Est,
                            Income_Slop_Est,Income_Region_Slop_Est) |>
  arrange(Country)

Combined_Int_Estimates$Model <- factor(Combined_Int_Estimates$Model, 
                 levels = c("Independent \nModel","Country \nModel",
                             "Region \nModel", "Income \nModel",
                             "Income-Region \nModel"))

Combined_Slop_Estimates$Model <- factor(Combined_Slop_Estimates$Model, 
                  levels = c("Independent \nModel","Country \nModel",
                            "Region \nModel", "Income \nModel",
                             "Income-Region \nModel"))
```

#### Creating a facet with the incomeregion according to the number of countries in each region.

Re-creating the plots of the model estimates (country estimates and the hierarchical estimates) using the ggragged package, to facilitate comparison across the countries in the same group.

```{r}
#The income grouping is necessary to specify different color for each income group, hence, the need to left_join the Country_income names.
Combined_Int_Estimates <- Combined_Int_Estimates |>
left_join(select(Country_income, Country, Income), join_by(Country)) |>
  mutate(Income_Region = stringr::str_replace_all(Income_Region,
          stringr::fixed("_ "), "\n"))

Combined_Int_estimates <- Combined_Int_estimates |>
left_join(select(Country_income, Country, Income), join_by(Country)) |>
  mutate(Income_Region = stringr::str_replace_all(Income_Region,
          stringr::fixed("_ "), "\n"))

Combined_Slop_Estimates <- Combined_Slop_Estimates |>
left_join(select(Country_income, Country, Income), join_by(Country)) |>
  mutate(Income_Region = stringr::str_replace_all(Income_Region,
          stringr::fixed("_ "), "\n"))

Combined_Slop_estimates <- Combined_Slop_estimates |>
left_join(select(Country_income, Country, Income), join_by(Country)) |>
  mutate(Income_Region = stringr::str_replace_all(Income_Region,
          stringr::fixed("_ "), "\n"))

#-------------------------------------------------------------------------------
# Creating a facet for the income-region group.
# Intercept
Combined_Int_Estimates$facet <- factor(Combined_Int_Estimates$Income_Region,
        levels = c("Middle Income\nEastern Europe", "Middle Income\nSouthern Europe", "High Income\nEastern Europe", "High Income\nSouthern Europe","High Income\nWestern Europe","High Income\nNorthern Europe"))

Combined_Int_estimates$facet <- factor(Combined_Int_estimates$Income_Region,
        levels = c("Middle Income\nEastern Europe", "Middle Income\nSouthern Europe", "High Income\nEastern Europe", "High Income\nSouthern Europe","High Income\nWestern Europe","High Income\nNorthern Europe"))

# Slope
Combined_Slop_Estimates$facet <- factor(Combined_Slop_Estimates$Income_Region,
                                        levels = c("Middle Income\nEastern Europe", "Middle Income\nSouthern Europe", "High Income\nEastern Europe", "High Income\nSouthern Europe","High Income\nWestern Europe","High Income\nNorthern Europe"))

Combined_Slop_estimates$facet <- factor(Combined_Slop_estimates$Income_Region,
                                        levels = c("Middle Income\nEastern Europe", "Middle Income\nSouthern Europe", "High Income\nEastern Europe", "High Income\nSouthern Europe","High Income\nWestern Europe","High Income\nNorthern Europe"))
```

#### Creating the colors for the grid.draws

```{r}
## Creating a grid for colors
Names <- Country_incomeregion |>
  select(Country, Region, Income, Income_Region)

# Specifying color flag for the different model fitted
color_flag <- c("Independent \nModel" ="darkolivegreen4" ,
                "Country \nModel" ="purple2",
                "Region \nModel" = "blue3",
                "Income \nModel" = "brown4",
                "Income-Region \nModel"= "darkgoldenrod3")

## Specifying color flag for the income-region grouping
IR_color_flag <- c("Middle Income_ Eastern Europe" = "lightsteelblue2",
                   "Middle Income_ Southern Europe" = "bisque2", 
                   "High Income_ Eastern Europe" = "lightsteelblue2", 
                   "High Income_ Southern Europe" = "bisque2",
                   "High Income_ Western Europe" = "#ACE1AF",
                   "High Income_ Northern Europe" = "lavenderblush2")

## Specifying color flag for the income grouping
Income_color <- c("High Income" = "black",
                  "Middle Income" = "magenta3")

IR <- data.frame(group =paste(unique(Combined_Int_Estimates$Income_Region)),
                  color_IR = c("bisque2", "#ACE1AF", "lightsteelblue2", "bisque2","lightsteelblue2","lavenderblush2"), color_I = c("magenta3", "black","magenta3", "black", "black", "black"))

IR_color <- Names |>
  mutate(color_IR = IR_color_flag[Income_Region],
         color_I = Income_color[Income]) |>
  mutate(Country = stringr::str_replace_all(Country, stringr::fixed("Bosnia& Herzegovina"), "Bosnia&\nHerzegovina")) |>
  select(group = Country, color_IR, color_I) |>
  as.data.frame()

IR_Colors <- rbind(IR, IR_color)
```

Creating plots of the model estimates using the ggragged package.

```{r}
## Comparing the model estimates
if (!dir.exists(here::here("Saved_Plots/Comparison_Visuals")))
  dir.create(here::here("Saved_Plots/Comparison_Visuals"))

Intc <- ggplot(data = Combined_Int_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = Combined_Int_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.28, position=position_nudge(x = 0.20), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_ragged_rows(vars(facet),
                    vars(Country),
                    scales = "free_y",
                    labeller = label_wrap_gen(width= 17))+
  labs(x = " ", y = "Intercept Estimates")+ theme_bw()+
  theme(
    axis.text.x = element_blank(), axis.ticks.x=element_blank(),
    strip.text.x = element_text(size = 11.5, face = "plain",
            margin = margin(0.12,0,0.12,0, "cm")),
      axis.text.y = element_text(size = 11,face = "bold"),
      axis.title=element_text(size=14, face="bold"),
     legend.position = "bottom", legend.text=element_text(size=11, face = "italic"))

Slop <- ggplot(data = Combined_Slop_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = Combined_Slop_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.28, position=position_nudge(x = 0.20), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_ragged_rows(vars(facet),
                    vars(Country),
                    scales = "free_y",
                    labeller = label_wrap_gen(width= 17))+
  labs(x = " ", y = "Slope Estimates")+
  theme_bw()+
  theme(
    axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 11.5, face = "plain",
                                    margin = margin(0.12,0,0.12,0, "cm")),
        axis.text.y = element_text(size = 11,face = "bold"),
      axis.title=element_text(size=14,face="bold"),
     legend.position = "bottom", legend.text=element_text(size=11, face = "italic"))
```

### The plots

```{r}
pdf("Saved_Plots/Comparison_Visuals/ggragged_Intercept.pdf",
    width = 14,
    height = 10)
G <- ggplotGrob(Intc)
# g$layout$name
Strip <- which(grepl('strip', G$layout$name)) 

for (i in Strip){
  j <- which(grepl('rect', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- G$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, IR_Colors$group)
  if (isTRUE( !is.na(st))){
    G$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- IR_Colors[st, "color_IR"]
    r <- which(grepl('text', G$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    G$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- IR_Colors[st, "color_I"]
  }
}
grid.draw(G)
dev.off()

###Slope
pdf("Saved_Plots/Comparison_Visuals/ggragged_Slope.pdf",
    width = 14,
    height = 10)

P <- ggplotGrob(Slop)

strip <- which(grepl('strip', P$layout$name))

for (i in strip){
  j <- which(grepl('rect', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, IR_Colors$group)
  if (isTRUE( !is.na(st))){
    P$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- IR_Colors[st, "color_IR"]
    r <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- IR_Colors[st, "color_I"]
  }
}
grid.draw(P)
dev.off()
```

#### Comparing country estimates

```{r}
intc <- ggplot(data = Combined_Int_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = Combined_Int_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.28, position=position_nudge(x = 0.20), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_ragged_rows(vars(facet),
                    vars(Country),
                    labeller = label_wrap_gen(width= 17))+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(
    axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 11.5, face = "plain",
                                    margin = margin(0.12,0,0.12,0, "cm")),
        axis.text.y = element_text(size = 11,face = "bold"),
      axis.title=element_text(size=15,face="bold"),
     legend.position = "bottom", legend.text=element_text(size=11, face = "bold.italic"))

slop <- ggplot(data = Combined_Slop_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = Combined_Slop_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.28, position=position_nudge(x = 0.20), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_ragged_rows(vars(facet),
                    vars(Country),
                    labeller = label_wrap_gen(width= 17))+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(
    axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 11.5, face = "plain",
                                    margin = margin(0.12,0,0.12,0, "cm")),
        axis.text.y = element_text(size = 10,face = "bold"),
      axis.title=element_text(size=15,face="bold"),
     legend.position = "bottom", legend.text=element_text(size=11, face = "bold.italic"))
  
#-------------------------------------------------------------------------------

pdf("Saved_Plots/Comparison_Visuals/Comparing-countries-ggragged_Intercept.pdf",
    width = 14,
    height = 10)
g <- ggplotGrob(intc)
# g$layout$name
Strip <- which(grepl('strip', g$layout$name)) 

for (i in Strip){
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, IR_Colors$group)
  if (isTRUE( !is.na(st))){
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- IR_Colors[st, "color_IR"]
    r <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- IR_Colors[st, "color_I"]
  }
}
grid.draw(g)
dev.off()

###Slope
pdf("Saved_Plots/Comparison_Visuals/Comparing-countries-ggraggedSlope.pdf",
    width = 14,
    height = 10)

P <- ggplotGrob(slop)

strip <- which(grepl('strip', P$layout$name))

for (i in strip){
  j <- which(grepl('rect', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, IR_Colors$group)
  if (isTRUE( !is.na(st))){
    P$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- IR_Colors[st, "color_IR"]
    r <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- IR_Colors[st, "color_I"]
  }
}
grid.draw(P)
dev.off()
```


