---
title: "Visuals to compare the model estimates using geofacet"
author: "Oluwayomi Akinfenwa"
date: "21/03/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading the Rmd file containing the BRMS model fitting and extracting the model estimates.

```{r, libraries, include = FALSE}
source(knitr::purl("04_JAGS_Model_Estimates.Rmd"))
```

A plot showing the model estimates and credible intervals (80% and 95%), facet by country and connecting the dots for the estimates from the 4 models (An independent model fits, Country-specific model and Region, Income, Income-Region hierarchical models).

```{r}
## Hierarchical estimates
##Intercepts
JAGS_Combined_Int_estimates <- rbind(JAGS_Country_Int_est, JAGS_Region_Int_est, 
                                JAGS_Income_Int_est, JAGS_IncomeRegion_Int_est) |>
  arrange(Country)

JAGS_Combined_Slop_estimates <- rbind(JAGS_Country_Slop_est, JAGS_Region_Slop_est, JAGS_Income_Slop_est, JAGS_IncomeRegion_Slop_est)|>
  arrange(Country)

JAGS_Combined_Int_estimates$Model <- factor(JAGS_Combined_Int_estimates$Model, 
                  levels = c("Country \nModel","Region \nModel", "Income \nModel", "Income-Region \nModel"))

JAGS_Combined_Slop_estimates$Model <- factor(JAGS_Combined_Slop_estimates$Model, 
                  levels = c("Country \nModel","Region \nModel", "Income \nModel", "Income-Region \nModel"))

## Countries estimates
JAGS_Combined_Int_Estimates <- rbind(JAGS_CountryInd_Int_Est,
                            JAGS_Country_Int_Est, JAGS_Region_Int_Est,
                            JAGS_Income_Int_Est, JAGS_Income_Region_Int_Est) |>
  arrange(Country)

JAGS_Combined_Slop_Estimates <- rbind(JAGS_CountryInd_Slop_Est,
                            JAGS_Country_Slop_Est, JAGS_Region_Slop_Est,
                            JAGS_Income_Slop_Est, JAGS_Income_Region_Slop_Est) |>
  arrange(Country)


JAGS_Combined_Int_Estimates$Model <- factor(JAGS_Combined_Int_Estimates$Model, 
                 levels = c("Independent \nModel","Country \nModel",
                             "Region \nModel", "Income \nModel",
                             "Income-Region \nModel"))

JAGS_Combined_Slop_Estimates$Model <- factor(JAGS_Combined_Slop_Estimates$Model, 
                  levels = c("Independent \nModel","Country \nModel",
                            "Region \nModel", "Income \nModel",
                             "Income-Region \nModel"))
```

```{r}
## Creating a grid for colors
Names <- country_region |>
  left_join(INCOME, join_by(Country == Country))

Region_color <- c("Eastern Europe" = "lightsteelblue2",
                  "Northern Europe"="lavenderblush2", 
                  "Southern Europe"= "bisque2",
                  "Western Europe"="#ACE1AF")

Income_color <- c("High Income" = "black",
                  "Middle Income" = "magenta3")

Colors <- Names |>
  select(Country, Region, Income) |>
  mutate(color_region = Region_color[Region],
         color_income = Income_color[Income]) |>
  as.data.frame()


color_flag <- c("Independent \nModel" ="darkolivegreen4" ,
                "Country \nModel" ="purple2",
                "Region \nModel" = "blue3",
                "Income \nModel" = "brown4",
                "Income-Region \nModel"= "darkgoldenrod3")

```

### The plots using the geo_facet to group the countries according to its position on the map.

```{r}
load(here::here("PISA_Data", "ISO Code.Rdata"))
C_codes <- ISO_Group |> filter(Continent == "Europe") |>
  select(name =Country, code = CNT)
 C_codes$name <- as.character(C_codes$name)
 C_codes <- C_codes |> arrange(name)


row<-c(7,5,3,4,5,5,6,4,2,1,1,5,3,7,4,1,2,6,2,4,
       2,4,6,7,4,6,3,1,3,6,4,2,5,3,5,6,1,5,3,2)

col<-c(6,4,7,2,6,8,5,5,4,7,6,2,4,7,6,1,1,4,7,4,
       6,3,7,4,8,6,3,4,5,1,7,8,7,6,5,2,5,3,8,2)

geo_grid <- cbind(row,col,C_codes)


## Comparing the model estimates
if (!dir.exists(here::here("Saved_Plots/Comparison_Visuals")))
  dir.create(here::here("Saved_Plots/Comparison_Visuals"))

JAGS_Int <- ggplot(data = JAGS_Combined_Int_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = JAGS_Combined_Int_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid, scales= "free_y")+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
        axis.text.y = element_text(size = 10,face = "bold"),
      axis.title=element_text(size=14,face="bold"),
     legend.position = "bottom", legend.text=element_text(size=11, face = "italic"))

JAGS_Slope <- ggplot(data = JAGS_Combined_Slop_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
    ggdist::stat_pointinterval(data = JAGS_Combined_Slop_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.28, position=position_nudge(x = 0.20), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid, scales= "free_y")+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
        axis.text.y = element_text(size = 10,face = "bold"),
      axis.title=element_text(size=14,face="bold"),
     legend.position = "bottom", legend.text=element_text(size=11, face = "italic"))
  
#-------------------------------------------------------------------------------

pdf("Saved_Plots/Comparison_Visuals/JAGS_Intercept.pdf",
    width = 14,
    height = 10)
G <- get_geofacet_grob(JAGS_Int) # for geo_facet plots
# g <- ggplotGrob(p) # for other ggplots

stript <- which(grepl('strip-t', G$layout$name)) 

for (i in stript){
  j <- which(grepl('rect', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- G$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext,Colors$Country)
  if (!is.na(st)){
    G$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
    r <- which(grepl('text', G$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    G$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- Colors[st, "color_income"]
  } 
}

grid.draw(G)
dev.off()

###Slope
pdf("Saved_Plots/Comparison_Visuals/JAGS_Slope.pdf",
    width = 14,
    height = 10)

P <- get_geofacet_grob(JAGS_Slope) # for geo_facet plots

stript <- which(grepl('strip-t', P$layout$name)) 

for (i in stript){
  j <- which(grepl('rect', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext,Colors$Country)
  if (!is.na(st)){
    P$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
    r <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- Colors[st, "color_income"]
  } 
}

grid.draw(P)
dev.off()
```

#### Comparing country estimates

```{r}
JAGS_int <- ggplot(data = JAGS_Combined_Int_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "dashed")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = JAGS_Combined_Int_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.28, position=position_nudge(x = 0.20), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid)+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
        axis.text.y = element_text(size = 10,face = "bold"),
      axis.title=element_text(size=14,face="bold"),
     legend.position = "bottom", legend.text=element_text(size=11, face = "italic"))

JAGS_slop <- ggplot(data = JAGS_Combined_Slop_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "dashed")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
    ggdist::stat_pointinterval(data = JAGS_Combined_Slop_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid, scales= "free_y")+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
        axis.text.y = element_text(size = 10,face = "bold"),
      axis.title=element_text(size=14,face="bold"),
     legend.position = "bottom", legend.text=element_text(size=11, face = "italic"))
  
#-------------------------------------------------------------------------------

pdf("Saved_Plots/Comparison_Visuals/JAGS_Comparingcountry_Intercept.pdf",
    width = 14,
    height = 10)
g <- get_geofacet_grob(JAGS_int) # for geo_facet plots
# g <- ggplotGrob(p) # for other ggplots

stript <- which(grepl('strip-t', g$layout$name)) 

for (i in stript){
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext,Colors$Country)
  if (!is.na(st)){
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
    r <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- Colors[st, "color_income"]
  } 
}

grid.draw(g)
dev.off()

###Slope
pdf("Saved_Plots/Comparison_Visuals/JAGS_Comparingcountry_Slope.pdf",
    width = 14,
    height = 10)

P <- get_geofacet_grob(JAGS_slop) # for geo_facet plots

stript <- which(grepl('strip-t', P$layout$name)) 

for (i in stript){
  j <- which(grepl('rect', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext,Colors$Country)
  if (!is.na(st)){
    P$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
    r <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- Colors[st, "color_income"]
  } 
}

grid.draw(P)
dev.off()
```



### Selecting few countries to investigate.

Countries with one data point, and countries where the hierarchical structure downweight its estimate are worthy of careful observation.

Countries like; Albania, Belarus, Ukraine, Moldova, Macedonia,
Finland, Luxembourg, Liechtenstein, Czechia, Switzerland.

We want to investigate 10 countries. The first thing to do is to filter out the regression line on the data across the different fitted model for these countries.

```{r}
QCountries <- c("Albania", "Belarus", "Ukraine", "Moldova", "Macedonia",
                "Bosnia and Herzegovina","Finland", "Luxembourg", 
                "Liechtenstein", "Czechia", "Sweden", "Germany")

#Filtering the colors for the selected countries
QColors <- Colors |>
  filter(Country %in% QCountries)


pdf("Saved_Plots/Comparison_Visuals/JAGS_few-country_fit.pdf",
    width = 12,
    height = 9)

ggplot(data = filter(PISA_Europe_Data, Country %in% QCountries), 
       aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_wrap2(~Country, nrow = 4)+
  geom_abline(data=filter(JAGS_CountryInd_ISEst, Country %in% QCountries), aes(slope=year_orig, intercept= Intercept), color="lightseagreen")+
  geom_abline(data=filter(JAGS_Country_IS_Est, Country %in% QCountries), 
              aes(slope=year_orig, intercept= Intercept), color="magenta3")+
  geom_abline(data=filter(JAGS_Rcountry_IS_Est, Country %in% QCountries),
              aes(slope=year_orig, intercept= Intercept), color="blue3")+
geom_abline(data=filter(JAGS_Icountry_IS_Est, Country %in% QCountries),
            aes(slope=year_orig, intercept= Intercept), color="yellow4")+
 geom_abline(data=filter(JAGS_IRcountry_IS_Est, Country %in% QCountries),
             aes(slope=year_orig, intercept= Intercept), color="indianred")+
  scale_x_continuous(breaks = seq(-15,0,3),labels = function(x) x+2018)+
  xlab("year")+ ggtitle("Independent Model = lightseagreen \n Country-specific model = Magenta \n Region hierarchical model = blue \n Income hierarchical model = yellow \n Income-Region hierarchical model = Indianred")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

dev.off()
```

```{r}
## Intercept
A1 <- ggplot(data=filter(JAGS_Combined_Int_Estimates, Country %in% QCountries))+
geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = filter(JAGS_Combined_Int_estimates, Country %in% QCountries),
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
 ggh4x::facet_wrap2(~Country, scales= "free_y", nrow = 4)+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
      legend.position = "bottom")

#Comparing the country estimates 
a1 <- ggplot(data=filter(JAGS_Combined_Int_Estimates, Country %in% QCountries))+
geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = filter(JAGS_Combined_Int_estimates, Country %in% QCountries),
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3, alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
 ggh4x::facet_wrap2(~Country, nrow = 4)+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
      legend.position = "bottom")

pdf("Saved_Plots/Comparison_Visuals/JAGS_FewerC_Intercept.pdf",
    width = 12,
    height = 9)

G <- ggplotGrob(A1)
# g$layout$name
Strip <- which(grepl('strip', G$layout$name)) 


for (i in Strip){
  j <- which(grepl('rect', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- G$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, QColors$Country)
  if (!is.na(st)){
    G$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- QColors[st, "color_region"]
    r <- which(grepl('text', G$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    G$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- QColors[st, "color_income"]
  }
}
grid.draw(G)
dev.off()
```


```{r}
## Slope

A2 <- ggplot(data=filter(JAGS_Combined_Slop_Estimates, Country %in% QCountries))+
geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = filter(JAGS_Combined_Slop_estimates, Country %in% QCountries),
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
 ggh4x::facet_wrap2(~Country, scales= "free_y", nrow = 4)+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
      legend.position = "bottom")

#Comparing the country estimates 
a2 <- ggplot(data=filter(JAGS_Combined_Slop_Estimates, Country %in% QCountries))+
geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = filter(JAGS_Combined_Slop_estimates, Country %in% QCountries),
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3, alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
 ggh4x::facet_wrap2(~Country, nrow = 4)+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
      legend.position = "bottom")

pdf("Saved_Plots/Comparison_Visuals/JAGS_FewerC_Slope.pdf",
    width = 12,
    height = 9)

G2 <- ggplotGrob(A2)
# g$layout$name
Strip2 <- which(grepl('strip', G2$layout$name)) 

for (i in Strip2){
  j <- which(grepl('rect', G2$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', G2$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- G2$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, QColors$Country)
  if (!is.na(st)){
    G2$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- QColors[st, "color_region"]
    r <- which(grepl('text', G2$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    G2$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- QColors[st, "color_income"]
  }
}
grid.draw(G2)
dev.off()

pdf("Saved_Plots/Comparison_Visuals/JAGS_FewerC_Comparing-country-Slope.pdf",
    width = 12,
    height = 9)

g <- ggplotGrob(a2)
# g$layout$name
Strip <- which(grepl('strip', g$layout$name)) 


for (i in Strip){
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, QColors$Country)
  if (!is.na(st)){
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- QColors[st, "color_region"]
    r <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- QColors[st, "color_income"]
  }
}
grid.draw(g)
dev.off()
```