---
title: "Model predictions from BRMS Model"
author: "Oluwayomi Akinfenwa"
date: "11/03/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Sourcing the indexing file containing the data and the country, region, income, income-region names and indexing.

```{r, data, include = FALSE}
sys.source("01_BRMS_PISA_Analysis_Data.R", envir = knitr::knit_global())
```

Creating a folder to store all the plots

```{r, libraries, include = FALSE}
if (!dir.exists(here::here("Saved_Plots/Pred_differences")))
  dir.create(here::here("Saved_Plots/Pred_differences"))
```

## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```

### Pulling the posterior draws estimates for the year 2022.

#### ytilde estimates from all the models

```{r}
#Independent model fit
CountryInd_model_pred <- SPred_grid|>
add_predicted_rvars(CountryInd_BRMSModel) |>
rename(pred = .prediction)

#Country_specific model
Country_model_pred <- Pred_grid|>
  add_predicted_rvars(Country_BRMSModel) |>
  rename(pred = .prediction)

#Region hierarchical model
Region_model_pred <- Pred_grid|>
  add_predicted_rvars(Region_BRMSModel) |>
  rename(pred = .prediction)

#Income hierarchical model                         
Income_model_pred <- Pred_grid|>
  add_predicted_rvars(Income_BRMSModel) |>
  rename(pred = .prediction)

#Income_Region hierarchical model
IR_model_pred <- Pred_grid|>
  add_predicted_rvars(IncomeRegion_BRMSModel) |>
  rename(pred = .prediction)
```

### Based on the recommendations from our last meeting, we want to calculate the
### probability of the posterior prediction less than the observed PISA scores for year 2022.

```{r}
#the observed values for 2022
yobserved <- Pisa_Europe_Data |>
  filter(year == "2022")

#Independent model fit
IndCountry_Pred <- CountryInd_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math)) |>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Country_specific model
Country_Pred <- Country_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Region hierarchical model
Region_Pred <- Region_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Income hierarchical model
Income_Pred <- Income_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Income-Region hierarchical model
IR_Pred <- IR_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 
```

#### Visualising the probability of the pred values less than or equal the observed PISA 2022 scores.

```{r}
pdf("Saved_Plots/Pred_differences/Pred_diff_IndM.pdf",
    width = 10,
    height = 7)
ggplot(data =IndCountry_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed")+
  ggtitle("Independent country model \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/Pred_diff_CM.pdf",
    width = 10,
    height = 7)
ggplot(data = Country_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Country-specific model \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/Pred_diff_RM.pdf",
    width = 10,
    height = 7)
ggplot(data = Region_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Region Hierarchical \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/Pred_diff_IM.pdf",
    width = 10,
    height = 7)
ggplot(data = Income_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Income Hierarchical \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/Pred_diff_IRM.pdf",
    width = 10,
    height = 7)
ggplot(data = IR_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Income-Region Hierarchical model \n The difference between the predicted value and the observed value.")
dev.off()
```