---
title: "Plotting the distribution of the Sigmas of the paramter and hyper-parameter across all the fitted models"
author: "Oluwayomi Akinfenwa"
date: "27/03/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

Sourcing the file containing all the data needed for this analysis from the Rmd file named: 01_PISA_Analysis_Data.Rmd.
This file contains the raw data from OECD website and all the necessary data for this analysis.

```{r loading the data}
sys.source("01_BRMS_PISA_Analysis_Data.R", envir = knitr::knit_global())
```


## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```

### Pulling the sigma estimates from all the fitted models

#### Sigma estimates from the independent-country-specific model

```{r}
#get_variables(CountryInd_BRMSModel)

#pulling the sigma estimates from the model iterations for the  CountryInd_BRMSModel.

CountryInd_sigma <-posterior::as_draws(CountryInd_BRMSModel, 
                variable = "sigma",regex = TRUE) |>
  purrr::map_dfr(as_tibble) 

#plotting the distribution of the sigma from the Independent country model.
# I decided to use the geom_halfeyeh() instead of the geom_density() because it generates a combination of a density and stat_pointintervalh denoting the density, point estimates alongside the uncertainty intervals for draws from the sigma distribution.
CountryInd_sigma |>
  ggplot(aes(x = sigma)) +
  geom_halfeyeh()+ ggtitle("global Sigma distribution for Independent country model")
```

#### Sigma estimates from the country-specific model

```{r}
#get_variables(Country_BRMSModel)

#pulling the sigma estimates from the model iterations for the  CountryInd_BRMSModel.
#Intercept
Country_I_sigma <- spread_draws(Country_BRMSModel, sd_Country__Intercept) |>
  rename(sigma =`sd_Country__Intercept`)

#Slope
Country_S_sigma <- spread_draws(Country_BRMSModel, sd_Country__year_orig) |>
  rename(sigma =`sd_Country__year_orig`)

#plotting the distribution of the sigma from the country-specific model.
# I decided to use the stat_halfeye() instead of the geom_density() because it generates a combination of a density and stat_pointintervalh denoting the density, point estimates alongside the uncertainty intervals for draws from the sigma distribution.
Country_I_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye() + ggtitle("Sigma distribution attached to the Intercept parameter for Country-specific model")

Country_S_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye()+ ggtitle("Sigma distribution attached to the Slope parameter for Country-specific model")
```

#### Sigma estimates from the Region hierarchical model

```{r}
#get_variables(Region_BRMSModel)

#pulling the sigma estimates from the model iterations for the  Region_BRMSModel.
#The hierarchical structure
#Intercept
Region_I_sigma <- spread_draws(Region_BRMSModel, sd_Region__Intercept) |>
  rename(sigma =`sd_Region__Intercept`)

#Slope
Region_S_sigma <- spread_draws(Region_BRMSModel, sd_Region__year_orig) |>
  rename(sigma =`sd_Region__year_orig`)

#The country  variations
#Intercept
RegionC_I_sigma <- spread_draws(Region_BRMSModel, sd_Country__Intercept) |>
  rename(sigma =`sd_Country__Intercept`)

#Slope
RegionC_S_sigma <- spread_draws(Region_BRMSModel, sd_Country__year_orig) |>
  rename(sigma =`sd_Country__year_orig`)

#plotting the distribution of the sigma from the Region hierarchical model.
Region_I_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye() + ggtitle("Sigma distribution attached to the Region hyper-parameter Intercept estimates")

Region_S_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye()+ ggtitle("Sigma distribution attached to the Region hyper-parameter Slope estimates")

#Sigma distribution for the Country parameter estimates
RegionC_I_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye() + ggtitle("Sigma distribution attached to the Intercept parameter for Region hierarchical model")

RegionC_S_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye()+ ggtitle("Sigma distribution attached to the Slope parameter for Region hierarchical model")
```

#### Sigma estimates from the Income hierarchical model

```{r}
#get_variables(Income_BRMSModel)

#pulling the sigma estimates from the model iterations for the Income_BRMSModel.
#The hierarchical structure
#Intercept
Income_I_sigma <- spread_draws(Income_BRMSModel, sd_Income__Intercept) |>
  rename(sigma =`sd_Income__Intercept`)

#Slope
Income_S_sigma <- spread_draws(Income_BRMSModel, sd_Income__year_orig) |>
  rename(sigma =`sd_Income__year_orig`)

#The country  variations
#Intercept
IncomeC_I_sigma <- spread_draws(Income_BRMSModel, sd_Country__Intercept) |>
  rename(sigma =`sd_Country__Intercept`)

#Slope
IncomeC_S_sigma <- spread_draws(Income_BRMSModel, sd_Country__year_orig) |>
  rename(sigma =`sd_Country__year_orig`)

#plotting the distribution of the sigma from the Income hierarchical model.
Income_I_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye() + ggtitle("Sigma distribution attached to the Income hyper-parameter Intercept estimates")

Income_S_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye()+ ggtitle("Sigma distribution attached to the Income hyper-parameter Slope estimates")

#Sigma distribution for the Country parameter estimates
IncomeC_I_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye() + ggtitle("Sigma distribution attached to the Intercept parameter for Income hierarchical model")

IncomeC_S_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye()+ ggtitle("Sigma distribution attached to the Slope parameter for Income hierarchical model")
```


#### Sigma estimates from the Income-Region hierarchical model

```{r}
#get_variables(IncomeRegion_BRMSModel)

#pulling the sigma estimates from the model iterations for the  Income-Region_BRMSModel.
#The hierarchical structure
#Intercept
IncomeRegion_I_sigma <- spread_draws(IncomeRegion_BRMSModel, sd_Income_Region__Intercept) |>
  rename(sigma =`sd_Income_Region__Intercept`)

#Slope
IncomeRegion_S_sigma <- spread_draws(IncomeRegion_BRMSModel, sd_Income_Region__year_orig) |>
  rename(sigma =`sd_Income_Region__year_orig`)

#The country  variations
#Intercept
IRC_I_sigma <- spread_draws(IncomeRegion_BRMSModel, sd_Country__Intercept) |>
  rename(sigma =`sd_Country__Intercept`)

#Slope
IRC_S_sigma <- spread_draws(IncomeRegion_BRMSModel, sd_Country__year_orig) |>
  rename(sigma =`sd_Country__year_orig`)

#plotting the distribution of the sigma from the Income-Region hierarchical model.
IncomeRegion_I_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye() + ggtitle("Sigma distribution attached to the Income-Region hyper-parameter Intercept estimates")

IncomeRegion_S_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye()+ ggtitle("Sigma distribution attached to the Income-Region hyper-parameter Slope estimates")

#Sigma distribution for the Country parameter estimates
IRC_I_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye() + ggtitle("Sigma distribution attached to the Intercept parameter for Income-Region hierarchical model")

IRC_S_sigma |>
  ggplot(aes(x = sigma)) +
  stat_halfeye()+ ggtitle("Sigma distribution attached to the Slope parameter for Income-Region hierarchical model")
```