---
title: "Model predictions from BRMS Model"
author: "Oluwayomi Akinfenwa"
date: "27/06/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Sourcing the indexing file containing the data and the country, region, income, income-region names and indexing.

```{r, data, include = FALSE}
sys.source("01_BRMS_PISA_Analysis_Data.R", envir = knitr::knit_global())
```

Creating a folder to store all the plots

```{r, libraries, include = FALSE}
if (!dir.exists(here::here("Saved_Plots/Pred_differences")))
  dir.create(here::here("Saved_Plots/Pred_differences"))
```

## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```

### Pulling the posterior draws estimates for the year 2022.

#### ytilde estimates from all the models

```{r}
#Independent model fit
CountryInd_model_pred <- SPred_grid|>
add_predicted_rvars(CountryInd_BRMSModel) |>
rename(pred = .prediction)

#Country_specific model
Country_model_pred <- Pred_grid|>
  add_predicted_rvars(Country_BRMSModel) |>
  rename(pred = .prediction)

#Region hierarchical model
Region_model_pred <- Pred_grid|>
  add_predicted_rvars(Region_BRMSModel) |>
  rename(pred = .prediction)

#Income hierarchical model                         
Income_model_pred <- Pred_grid|>
  add_predicted_rvars(Income_BRMSModel) |>
  rename(pred = .prediction)

#Income_Region hierarchical model
IR_model_pred <- Pred_grid|>
  add_predicted_rvars(IncomeRegion_BRMSModel) |>
  rename(pred = .prediction)
```

### Based on the recommendations from our last meeting, we want to calculate the
### probability of the posterior prediction less than the observed PISA scores for year 2022.

```{r}
#the observed values for 2022
yobserved <- Pisa_Europe_Data |>
  filter(year == "2022")

#Independent model fit
IndCountry_Pred <- CountryInd_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math)) |>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Country_specific model
Country_Pred <- Country_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Region hierarchical model
Region_Pred <- Region_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Income hierarchical model
Income_Pred <- Income_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Income-Region hierarchical model
IR_Pred <- IR_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 
```

### 27/06/2024 - New plot of the differences facet by region.

### Based on the recommendations from our last meeting, we want to plot the differences between predicted and observed PISA scores for 2022

##### Creating grid to color the plot

```{r}
# Creating a grid for the color
Names <- Country_Pred |>
  select(Country, Region)

Region_color <- c("Eastern Europe" = "lightsteelblue2",
                  "Northern Europe"="lavenderblush2", 
                  "Southern Europe"= "bisque2",
                  "Western Europe"="#ACE1AF")

Colors <- Names |>
  mutate(color_region = Region_color[Region]) |>
  as.data.frame()
```

#####Independent linear model

```{r}
# The plot
P_Ind <- ggplot(data = IndCountry_Pred,
       aes(x= math0, y= Country)) +
        geom_point(shape=23, fill="blue", color="darkred", size=2.8) +
  facet_grid(Region ~ ., scales = "free_y", switch = "y") + 
  labs(x = "Differences between predicted and observed PISA2022", y = " ") +
  theme_bw() +
  theme(strip.text = element_text(size = 10.5, face = "bold"),
        axis.text.y = element_text(size = 11.5))

pdf("Saved_Plots/Pred_differences/Diff_IndM.pdf")
#creating the grid color
g1 <- ggplotGrob(P_Ind) # for other ggplots

stripl <- which(grepl('strip-l', g1$layout$name))  #the y axis names has been switch to the left, hence the reason for the strip-l

for (i in stripl){
  j <- which(grepl('rect', g1$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g1$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g1$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, Colors$Region)
  if (!is.na(st)){
    g1$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
  }
}

grid.draw(g1)
dev.off()
```

#### Country Model

```{r}
# The plot
P_Country <- ggplot(data = Country_Pred,
       aes(x= math0, y= Country)) +
        geom_point(shape=23, fill="blue", color="darkred", size=2.8) +
  facet_grid(Region ~ ., scales = "free_y", switch = "y") + 
  labs(x = "Differences between predicted and observed PISA2022", y = " ") +
  theme_bw() +
  theme(strip.text = element_text(size = 10.5, face = "bold"),
        axis.text.y = element_text(size = 11.5))

pdf("Saved_Plots/Pred_differences/Diff_CM.pdf")
#creating the grid color
g2 <- ggplotGrob(P_Country) # for other ggplots

stripl <- which(grepl('strip-l', g2$layout$name))  #the y axis names has been switch to the left, hence the reason for the strip-l

for (i in stripl){
  j <- which(grepl('rect', g2$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g2$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g2$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, Colors$Region)
  if (!is.na(st)){
    g2$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
  }
}

grid.draw(g2)
dev.off()
```

#### Region Model

```{r}
# The plot
P_Region <- ggplot(data = Region_Pred,
       aes(x= math0, y= Country)) +
        geom_point(shape=23, fill="blue", color="darkred", size=2.8) +
  facet_grid(Region ~ ., scales = "free_y", switch = "y") + 
  labs(x = "Differences between predicted and observed PISA2022", y = " ") +
  theme_bw() +
  theme(strip.text = element_text(size = 10.5, face = "bold"),
        axis.text.y = element_text(size = 11.5))

pdf("Saved_Plots/Pred_differences/Diff_RegionM.pdf")
#creating the grid color
g3 <- ggplotGrob(P_Region) # for other ggplots

stripl <- which(grepl('strip-l', g3$layout$name))  #the y axis names has been switch to the left, hence the reason for the strip-l

for (i in stripl){
  j <- which(grepl('rect', g3$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g3$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g3$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, Colors$Region)
  if (!is.na(st)){
    g3$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
  }
}

grid.draw(g3)
dev.off()
```

#### Income model

```{r}
# The plot
P_Income <- ggplot(data = Income_Pred,
       aes(x= math0, y= Country)) +
        geom_point(shape=23, fill="blue", color="darkred", size=2.8) +
  facet_grid(Region ~ ., scales = "free_y", switch = "y") + 
  labs(x = "Differences between predicted and observed PISA2022", y = " ") +
  theme_bw() +
  theme(strip.text = element_text(size = 10.5, face = "bold"),
        axis.text.y = element_text(size = 11.5))

pdf("Saved_Plots/Pred_differences/Diff_IncomeM.pdf")
#creating the grid color
g4 <- ggplotGrob(P_Income) # for other ggplots

stripl <- which(grepl('strip-l', g4$layout$name))  #the y axis names has been switch to the left, hence the reason for the strip-l

for (i in stripl){
  j <- which(grepl('rect', g4$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g4$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g4$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, Colors$Region)
  if (!is.na(st)){
    g4$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
  }
}

grid.draw(g4)
dev.off()
```

#### Income-Region model
```{r}
# The plot
P_IR <- ggplot(data = IR_Pred,
       aes(x= math0, y= Country)) +
        geom_point(shape=23, fill="blue", color="darkred", size=2.8) +
  facet_grid(Region ~ ., scales = "free_y", switch = "y") + 
  labs(x = "Differences between predicted and observed PISA2022", y = " ") +
  theme_bw() +
  theme(strip.text = element_text(size = 10.5, face = "bold"),
        axis.text.y = element_text(size = 11.5))

pdf("Saved_Plots/Pred_differences/Diff_IRM.pdf")
#creating the grid color
g5 <- ggplotGrob(P_IR) # for other ggplots

stripl <- which(grepl('strip-l', g5$layout$name))  #the y axis names has been switch to the left, hence the reason for the strip-l

for (i in stripl){
  j <- which(grepl('rect', g5$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g5$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g5$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, Colors$Region)
  if (!is.na(st)){
    g5$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
  }
}

grid.draw(g5)
dev.off()
```