---
title: "The Bayesian hierarchical models for Region, Income and Income-Region"
author: "Oluwayomi Akinfenwa"
date: "30/08/2023"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
```

Loading the two Rdata containing the learningtower data set and the processed data with Region and Income classification.

```{r loading the data}
load(here::here("SavedData", "pisam.Rdata"))
```

**We have 406 observations and for this analysis, we decided to examine European countries**

### Filtering European countries alone

```{r Europe}
Pisa_Europe_Data <- Pisa_Data |> filter(Continent == "Europe") |> arrange(Country)
```

**For the European countries, we have 230 observations from 40 countries.**

### Visualising the data

```{r}
# Joining the Income and Region together to form one new column
Pisa_Europe_Data <- unite(Pisa_Europe_Data, col = "Income_Region", c("Income", "Region"), 
                          sep = "_", remove = FALSE)

#Creating the grid for the prediction
country_names <- levels(factor(Pisa_Europe_Data$Country))
region_names <- levels(factor(Pisa_Europe_Data$Region))
income_names <- levels(factor(Pisa_Europe_Data$Income))
incomeregion_names <- levels(factor(Pisa_Europe_Data$Income_Region))

## Obtaining the index for the data
mu_index <- 1:nrow(Pisa_Europe_Data)

## Obtaining the region indexes

country_region <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         
INCOME_REGION <- country_incomeregion |> select(Country, Income_Region)

pred_grid <- Pisa_Europe_Data |> 
  modelr::data_grid(Country, year_orig) |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region)))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> left_join(INCOME_REGION, join_by(Country))
```

### Loading the hierarchical models from the saved R.Data file

```{r}
#Country specific model
load(here::here("Manuscript_Models", "Country_Model.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_Model.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_Model.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_Model.Rdata"))

```

## Results

### Estimates from the country-specific model

```{r}
Country_ModelSample <- C_Model$BUGSoutput$sims.matrix

CountryI <- spread_rvars(Country_ModelSample , alpha.j[Country_index]) |>
  mutate(Country = country_names[Country_index], term="Intercept") |>
  select(Country, term,rvar=alpha.j)


CountryS <- spread_rvars(Country_ModelSample , beta.j[Country_index]) |>
  mutate(Country = country_names[Country_index], term="year_orig") |>
  select(Country, term,rvar=beta.j)

CountryIS <- rbind(CountryI, CountryS)


Country_IS_Est <- CountryIS |> mutate(coef=median(rvar))|> 
  select(-rvar, Country)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
Country_Int_Est <- CountryI |> median_qi(rvar) |>
  mutate(Model = "Country")|>
  select(c(Country, Model,rvar, .lower, .upper))
## Slope Estimates
Country_Slop_Est <- CountryS |> median_qi(rvar) |>
  mutate(Model = "Country")|>
  select(c(Country, Model,rvar, .lower, .upper))
```

#### The country-specific plot

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point(color = "blue3")+ facet_wrap(~Country, nrow = 5) +
  geom_abline(data=Country_IS_Est, aes(slope=year_orig, intercept= Intercept), color="black")+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+ xlab("year")+
   ylab("Average maths score") +theme_bw()+
  theme(legend.position = "bottom",
        plot.subtitle = element_text(family = "Serif"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

### Estimates from the region hierarchical model

```{r}
Region_ModelSamples <- Region_Model$BUGSoutput$sims.matrix
# get_variables(Region_ModelSamples)


Region_I <- spread_rvars(Region_ModelSamples , mu_alpha.r[region_num]) |>
  mutate(Region = region_names[region_num], term = "Intercept") |>
  rename(rvar =mu_alpha.r) |>
  select(Region, term,rvar)

Region_S <- spread_rvars(Region_ModelSamples , mu_beta.r[region_num]) |>
  mutate(Region = region_names[region_num], term = "year_orig") |>
  rename(rvar =mu_beta.r) |>
  select(Region, term,rvar)

Region_IS <- rbind(Region_I, Region_S)


## The region country estimates
Rcountry_I <- spread_rvars(Region_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(Country_region, by = join_by(Country==Country))|>
  rename(rvar =alpha.j,Country = Country) |>
  select(Country, Region,Income, term,rvar)


Rcountry_S <- spread_rvars(Region_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(Country_region, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country = Country) |>
  select(Country, Region,Income, term,rvar)

Rcountry_IS <- rbind(Rcountry_I, Rcountry_S) 
```

### Tidying the estimates from the Region hierarchical model

```{r, fig.width=10, fig.height=8}
#median estimates
Region_IS_Est <- Region_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

Rcountry_IS_Est <- Rcountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
Region_int_est <- Region_I |> median_qi(rvar) |>
  select(c(Region,rvar, .lower ,.upper))
#Country estimates
Region_Int_Est <- Rcountry_I |> median_qi(rvar) |>
  mutate(Model = "Region")|>
  select(c(Country, Model,rvar, .lower, .upper))
## Slope Estimates
#Hierarchy estimates
Region_slop_est <- Region_S |> median_qi(rvar) |>
  select(c(Region,rvar, .lower ,.upper))
#Country estimates
Region_Slop_Est <- Rcountry_S |> median_qi(rvar) |>
  mutate(Model = "Region")|>
  select(c(Country, Model,rvar, .lower, .upper))

### Creating a boxplot for both intercept and slope

ggplot(data = Rcountry_IS_Est)+
  geom_boxplot(aes(x= Region, y = Intercept))

```

### Estimates from the income hierarchical model

```{r}
Income_ModelSamples <- Income_Model$BUGSoutput$sims.matrix
# get_variables(Income_ModelSamples)
Income_I <- spread_rvars(Income_ModelSamples , mu_alpha.I[income_num]) |>
  mutate(Income = income_names[income_num], term = "Intercept") |>
  rename(rvar =mu_alpha.I) |>
  select(Income, term,rvar)

Income_S <- spread_rvars(Income_ModelSamples , mu_beta.I[income_num]) |>
  mutate(Income = income_names[income_num], term = "year_orig") |>
  rename(rvar =mu_beta.I) |>
  select(Income, term,rvar)

Income_IS <- rbind(Income_I, Income_S)

## The income country estimates
Icountry_I <- spread_rvars(Income_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(Country_income, by = join_by(Country==Country))|>
  rename(rvar =alpha.j, Country=Country) |>
  select(Country, Income,Region, term,rvar)


Icountry_S <- spread_rvars(Income_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(Country_income, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country=Country) |>
  select(Country, Income,Region, term,rvar)

Icountry_IS <- rbind(Icountry_I, Icountry_S) 
```

#### Tidying the estimates from the model

```{r, fig.width=10, fig.height=8}
INCOME_IS_EST <- Income_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

Income_IS_Est <- Icountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
Income_int_est <- Income_I |> median_qi(rvar) |>
  select(c(Income,rvar, .lower ,.upper))
#Country estimates
Income_Int_Est <- Icountry_I |> median_qi(rvar) |>
  mutate(Model = "Income")|>
  select(c(Country, Model,rvar, .lower, .upper))

## Slope Estimates
#Hierarchy estimates
Income_slop_est <- Income_S |> median_qi(rvar) |>
  select(c(Income,rvar, .lower ,.upper))
#Country estimates
Income_Slop_Est <- Icountry_S |> median_qi(rvar) |>
  mutate(Model = "Income")|>
  select(c(Country, Model,rvar, .lower, .upper))
```

### Estimates from the incomeregion hierarchical model

```{r}
IR_ModelSamples <- IR_Model$BUGSoutput$sims.matrix
# get_variables(IR_ModelSamples)
IncomeRegion_I <- spread_rvars(IR_ModelSamples , mu_alpha.IR[income_num]) |>
  mutate(Income = incomeregion_names[income_num], term = "Intercept") |>
  rename(rvar =mu_alpha.IR) |>
  select(Income, term,rvar)

IncomeRegion_S <- spread_rvars(IR_ModelSamples , mu_beta.IR[income_num]) |>
  mutate(Income = incomeregion_names[income_num], term = "year_orig") |>
  rename(rvar =mu_beta.IR) |>
  select(Income, term,rvar)

IncomeRegion_IS <- rbind(IncomeRegion_I, IncomeRegion_S)

## The income country estimates
IRcountry_I <- spread_rvars(IR_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(country_incomeregion, by = join_by(Country==Country))|>
  rename(rvar =alpha.j, Country=Country) |>
  select(Country, Income_Region, term,rvar)


IRcountry_S <- spread_rvars(IR_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(country_incomeregion, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country=Country) |>
  select(Country, Income_Region, term,rvar)

IRcountry_IS <- rbind(IRcountry_I, IRcountry_S) 
```

#### The median and credible interval estimates for the IncomeRegion model

```{r}
## Median
IR_IS_EST <- IncomeRegion_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

IncomeRegion_IS_Est <- IRcountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
IncomeRegion_int_est <- IncomeRegion_I |> median_qi(rvar) |>
  select(c(Income,rvar, .lower ,.upper))
#Country estimates
Income_Region_Int_Est <- IRcountry_I |> median_qi(rvar) |>
  mutate(Model = "Income_Region")|>
  select(c(Country, Model,rvar, .lower, .upper))
## Slope Estimates
#Hierarchy estimates
IncomeRegion_slop_est <- IncomeRegion_S |> median_qi(rvar) |>
  select(c(Income,rvar, .lower ,.upper))
#Country estimates
Income_Region_Slop_Est <- IRcountry_S |> median_qi(rvar) |>
  mutate(Model = "Income_Region")|>
  select(c(Country, Model,rvar, .lower, .upper))
```

### Recommendation 2 from our last meeting.

A plot showing the model estimates and error-bars, facet by country and connect the dots for the estimates from the 4 models.

```{r}
Combined_Estimates <- rbind(Country_Int_Est,Region_Int_Est,
                            Income_Int_Est,Income_Region_Int_Est) |>
  arrange(Country)
  
### The plot
ggplot(data= Combined_Estimates, aes(x = Model, y = rvar))+
  geom_point(aes(color = Model))+
  geom_errorbar(aes(ymin= .lower, ymax= .upper, color = Model), width= 0.34)+
  geom_line(aes(group = Country),linetype= "dashed")+
  facet_wrap(~Country, scales = "free_y", nrow = 8)+
  xlab(" ")+ ylab("Intercept model estimates")+
  theme(legend.position = "bottom")
```