---
title: "Pulling out the SD across the models"
author: "Oluwayomi Akinfenwa"
date: "25/11/2023"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```


```{r, libraries, include = FALSE}
library(lme4)
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
library(bayesplot)
library(patchwork)
library(ggragged)
library(geofacet)
```

Loading the two R.data containing the learning-tower data set and the processed data with Region and Income classification.

```{r loading the data}
load(here::here("SavedData", "pisam.Rdata"))
```

**We have 406 observations and for this analysis, we decided to examine European countries**

### Filtering European countries alone

```{r Europe}
Pisa_Europe_Data <- Pisa_Data |> filter(Continent == "Europe") |> arrange(Country)
```

**For the European countries, we have 230 observations from 40 countries.**

### Visualising the data

```{r}
# Joining the Income and Region together to form one new column
Pisa_Europe_Data <- unite(Pisa_Europe_Data, col = "Income_Region", c("Income", "Region"), sep = "_", remove = FALSE)

#Creating the grid for the prediction
country_names <- levels(factor(Pisa_Europe_Data$Country))
region_names <- levels(factor(Pisa_Europe_Data$Region))
income_names <- levels(factor(Pisa_Europe_Data$Income))
incomeregion_names <- levels(factor(Pisa_Europe_Data$Income_Region))

## Obtaining the index for the data
mu_index <- 1:nrow(Pisa_Europe_Data)

## Obtaining the region indexes

country_region <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         

pred_grid <- Pisa_Europe_Data |> 
  modelr::data_grid(Country, year_orig) |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region)))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> 
  left_join(REGION, join_by(Country))
```


## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "Ind_Country_Model.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_Model.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_Model.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_Model.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_Model.Rdata"))
```

### Pulling the SD for all the country estimates across all the hierarchical models to create a boxplot to visualise the uncertainties for each model. This will enable us to  know if the number of parameters have impact on the uncertainties.

### SD from Region Hierarchical model

```{r}
Region_ModelSamples <- Region_Model$BUGSoutput$sims.matrix
# get_variables(Region_ModelSamples)

RegionGlobal_SD <- spread_rvars(Region_ModelSamples , sigma[G])

Region_SD <- spread_rvars(Region_ModelSamples , sigma_alpha[country_num])

RegionC_SD <- Region_Model$BUGSoutput$sd

Region_alphaSD <- as_tibble(RegionC_SD$alpha.j) |>
  mutate(country_num = 1:40) |> rename(sd = value)|>
  mutate(Country = country_names[country_num], model = "Region") |>
  select(Country,model, sd)

Region_betaSD <- as_tibble(RegionC_SD$beta.j) |>
  mutate(country_num = 1:40) |> rename(sd = value)|>
  mutate(Country = country_names[country_num], model = "Region") |>
  select(Country,model, sd)

```


### SD from Income Hierarchical model

```{r}
Income_ModelSamples <- Income_Model$BUGSoutput$sims.matrix
# get_variables(Income_ModelSamples)

IncomeGlobal_SD <- spread_rvars(Income_ModelSamples , sigma[G])

Income_SD <- spread_rvars(Income_ModelSamples , sigma_alpha[country_num])

IncomeC_SD <- Income_Model$BUGSoutput$sd

Income_alphaSD <- as_tibble(IncomeC_SD$alpha.j) |>
  mutate(country_num = 1:40) |> rename(sd = value)|>
  mutate(Country = country_names[country_num], model = "Income") |>
select(Country,model, sd)

Income_betaSD <- as_tibble(IncomeC_SD$beta.j) |>
  mutate(country_num = 1:40) |> rename(sd = value)|>
  mutate(Country = country_names[country_num], model = "Income") |>
  select(Country,model, sd)

```


### SD from IncomeRegion Hierarchical model

```{r}
IR_ModelSamples <- IR_Model$BUGSoutput$sims.matrix
# get_variables(IR_ModelSamples)

IRGlobal_SD <- spread_rvars(IR_ModelSamples , sigma[G])

IR_SD <- spread_rvars(IR_ModelSamples , sigma_alpha[country_num])

IRC_SD <- IR_Model$BUGSoutput$sd

IR_alphaSD <- as_tibble(IRC_SD$alpha.j) |>
  mutate(country_num = 1:40) |> rename(sd = value)|>
  mutate(Country = country_names[country_num], model = "IncomeRegion") |>
  select(Country,model, sd)

IR_betaSD <- as_tibble(IRC_SD$beta.j) |>
  mutate(country_num = 1:40) |> rename(sd = value)|>
  mutate(Country = country_names[country_num], model = "IncomeRegion")  |>
   select(Country,model, sd)

```


Tidying the sd estimates from the hierarchical models

```{r}
### ALPHA
alpha_sd <- rbind(Region_alphaSD, Income_alphaSD, IR_alphaSD) |>
  arrange(Country)

alpha_sd$model = factor(alpha_sd$model,
                       levels= c("Region", "Income", "IncomeRegion"))

#### BETA
beta_sd <- rbind(Region_betaSD, Income_betaSD, IR_betaSD) |>
  arrange(Country)

beta_sd$model = factor(beta_sd$model,
                       levels= c("Region", "Income", "IncomeRegion"))
```

Creating a boxplot

```{r}
ggplot(data = alpha_sd, 
       aes(x = model, y = sd))+
  geom_boxplot()+ ylim(0,20) +
  ggtitle("Visualising the Alpha uncertainties")

ggplot(data = beta_sd, 
       aes(x = model, y = sd))+
  geom_boxplot()+
  ggtitle("Visualising the Beta uncertainties")
```

Another visual to represent the sds

```{r}
ggplot(dat = alpha_sd,
       aes(x = sd, y = reorder(Country,sd), color = model))+
  geom_point()+ ylab("Country") + xlim(0,20)+
  ggtitle("Visualising the Alpha uncertainties")

ggplot(dat = beta_sd,
       aes(x = sd, y = reorder(Country,sd), color = model))+
  geom_point()+ ylab("Country") +
  ggtitle("Visualising the Beta uncertainties")
```


This results reveal that the variation across model with more parameters is lesser than the model with less parameters. Hence, the sd reduces as the number of parameter increases.


### Recommendation 3

#### Pull out the country estimates from the model.

```{r}

```


```{r}
IR_ModelSamples <- IR_Model$BUGSoutput$sims.matrix
# get_variables(IR_ModelSamples)
IncomeRegion_I <- spread_rvars(IR_ModelSamples , mu_alpha.IR[income_num]) |>
  mutate(Income_Region = incomeregion_names[income_num], term = "Intercept") |>
  right_join(Country_incomeregion, by = join_by(Income_Region ==Income_Region ))|>
  rename(rvar =mu_alpha.IR) |>
  select(Country,Region, Income_Region,term,rvar)

IncomeRegion_S <- spread_rvars(IR_ModelSamples , mu_beta.IR[income_num]) |>
  mutate(Income_Region  = incomeregion_names[income_num], term = "year_orig") |>
  right_join(Country_incomeregion, by = join_by(Income_Region ==Income_Region ))|>
  rename(rvar =mu_beta.IR) |>
  select(Country,Region,Income_Region,term,rvar)

IncomeRegion_IS <- rbind(IncomeRegion_I, IncomeRegion_S)

## The income country estimates
IRcountry_I <- spread_rvars(IR_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(Country_incomeregion, by = join_by(Country==Country))|>
  rename(rvar =alpha.j, Country=Country) |>
  select(Country,Region, Income_Region, term,rvar)


IRcountry_S <- spread_rvars(IR_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(Country_incomeregion, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country=Country) |>
  select(Country,Region, Income_Region, term,rvar)

IRcountry_IS <- rbind(IRcountry_I, IRcountry_S) 
```

#### The median and credible interval estimates for the IncomeRegion model

```{r}
## Median
IR_IS_EST <- IncomeRegion_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

IncomeRegion_IS_Est <- IRcountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
IncomeRegion_int_est <- IncomeRegion_I |> median_qi(rvar) |>
  mutate(Model = "Income-Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower ,.upper))
#Country estimates
Income_Region_Int_Est <- IRcountry_I |> median_qi(rvar) |>
  mutate(Model = "Income-Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))
## Slope Estimates
#Hierarchy estimates
IncomeRegion_slop_est <- IncomeRegion_S |> median_qi(rvar) |>
  mutate(Model = "Income-Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower ,.upper))
#Country estimates
Income_Region_Slop_Est <- IRcountry_S |> median_qi(rvar) |>
  mutate(Model = "Income-Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))
```


### Plotting the model fit on the data

#### Independent country model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  facet_wrap(~Country, nrow = 5)+
  geom_abline(data= Ind_CountryIS_Est, aes(slope=year_orig, intercept= Intercept), color="green")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Independent country model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

#### Country model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  facet_wrap(~Country, nrow = 5)+
  geom_abline(data=Country_IS_Est, aes(slope=year_orig, intercept= Intercept), color="magenta3")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Country-specific model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

#### Region model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_nested_wrap(vars(Region, Country), nrow = 5)+
  geom_abline(data=Rcountry_IS_Est, aes(slope=year_orig, intercept= Intercept), color="blue3")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Region hierarchical model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```
geom_abline(data=Rcountry_IS_Est, aes(slope=year_orig, intercept= Intercept), color="blue3")+
geom_abline(data=Income_IS_Est, aes(slope=year_orig, intercept= Intercept), color="red3")+
 geom_abline(data=IncomeRegion_IS_Est, aes(slope=year_orig, intercept= Intercept), color="red3")
#### Income model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_nested_wrap(vars(Income, Country), nrow = 5)+
  geom_abline(data=Income_IS_Est, aes(slope=year_orig, intercept= Intercept), color="red3")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Income hierarchical model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

#### IncomeRegion model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_nested_wrap(vars(Income_Region, Country), nrow = 5)+
  geom_abline(data=IncomeRegion_IS_Est, aes(slope=year_orig, intercept= Intercept), color="red3")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Income-Region hierarchical model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```