---
title: "The Bayesian hierarchical models for Region, Income and Income-Region"
author: "Oluwayomi Akinfenwa"
date: "30/08/2023"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
```

Loading the two Rdata containing the learningtower data set and the processed data with Region and Income classification.

```{r loading the data}
load(here::here("SavedData", "pisam.Rdata"))
```

**We have 406 observations and for this analysis, we decided to examine European countries**

### Filtering European countries alone

```{r Europe}
Pisa_Europe_Data <- Pisa_Data |> filter(Continent == "Europe") |> arrange(Country)
```

**For the European countries, we have 230 observations from 40 countries.**

### Visualising the data

```{r}
# Joining the Income and Region together to form one new column
Pisa_Europe_Data <- unite(Pisa_Europe_Data, col = "Income_Region", c("Income", "Region"), 
                          sep = "_", remove = FALSE)

#Creating the grid for the prediction
country_names <- levels(factor(Pisa_Europe_Data$Country))
region_names <- levels(factor(Pisa_Europe_Data$Region))
income_names <- levels(factor(Pisa_Europe_Data$Income))
incomeregion_names <- levels(factor(Pisa_Europe_Data$Income_Region))

## Obtaining the index for the data
mu_index <- 1:nrow(Pisa_Europe_Data)

## Obtaining the region indexes

country_region <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         
INCOME_REGION <- country_incomeregion |> select(Country, Income_Region)

pred_grid <- Pisa_Europe_Data |> 
  modelr::data_grid(Country, year_orig) |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region)))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> left_join(INCOME_REGION, join_by(Country))
```

## Setting the model parameter specification for JAGS

### Writing JAGS model for country-level specifications

```{r Countrymodel}
if (!dir.exists(here::here("Manuscript_Models")))
  dir.create(here::here("Manuscript_Models"))

if(file.exists(here::here("Manuscript_Models",
                          "Country_Model.Rdata"))){
  load(here::here("Manuscript_Models",
                          "Country_Model.Rdata"))
  countryJags <- FALSE
} else countryJags <- TRUE
```

```{r, eval = countryJags}
C_JAGS_Model = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i])
}

# Prior on country alphas

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha, sigma_alpha^-2)
beta.j[j] ~ dnorm(mu_beta, sigma_beta^-2)
}

# Prior on sigma, model variation
sigma ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution
mu_alpha ~ dnorm(500, 100^-2)
mu_beta ~ dnorm(0, 5^-2)
sigma_alpha ~ dt(0, 5^-2,1)T(0,) # Truncated t-distribution
sigma_beta ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution 


# Setting up the posterior
for(m in 1:n_pred){
ytilde[m] ~ dnorm(mu_pred.m[m], sigma^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]] *(xpred.m[m])
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma^-2)
}
}
"

## JAGS Model
C_Jags.data <- list(y.i = Pisa_Europe_Data$math,
                    x.i = Pisa_Europe_Data$year_orig,
                    n = nrow(Pisa_Europe_Data),
                    n_C = Pisa_Europe_Data$Country |> unique() |> length(),
                    C = as.numeric(factor(Pisa_Europe_Data$Country)),
                    n_pred = nrow(pred_grid),
                    C_pred = pred_grid$Country_num,
                    xpred.m = pred_grid$year_orig)

C_Parnames <- c("alpha.j","beta.j", "mu_alpha", "mu_beta","sigma","sigma_alpha",
                 "sigma_beta","ytilde", "yrep","mu_pred.m","mu.i")

# model
C_Model <- jags(data = C_Jags.data,
              parameters.to.save = C_Parnames,
              model.file = textConnection(C_JAGS_Model),
              n.iter = 10000,
              n.burnin = 2000,
              n.chains = 4,
              n.thin = 4)

save(C_Model, file=here::here("Manuscript_Models", "Country_Model.Rdata"))
```

**This C_MODEL fits a separate linear regression for each country, giving each country its distinct parameter estimates.**

# Hierarchical Model

## Region-based Country specific intercept and slope

### Region as a hierarchical structure.

```{r Regionmodel}
if (!dir.exists(here::here("Manuscript_Models")))
  dir.create(here::here("Manuscript_Models"))

if(file.exists(here::here("Manuscript_Models",
                          "Region_Model.Rdata"))){
  load(here::here("Manuscript_Models",
                          "Region_Model.Rdata"))
  regionJags <- FALSE
} else regionJags <- TRUE
```

```{r, eval = regionJags}
hmregion = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i] )
}

# Prior on alphas to vary by region

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha.r[R[j]], sigma_alpha[R[j]]^-2)
beta.j[j] ~ dnorm(mu_beta.r[R[j]], sigma_beta^-2)
}

for (r in 1:n_R){
mu_alpha.r[r] ~ dnorm(mu_alpha_eur, sigma_alpha.r^-2)
mu_beta.r[r] ~ dnorm(mu_beta_eur, sigma_beta.r^-2)
sigma_alpha[r] ~ dt( 0, 1^-2,1)T(0,) # Truncated t-distribution
}

# Prior on sigma, model variation
sigma ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on alpha hyper-parameters
mu_alpha_eur ~ dnorm(500, 100^-2)
sigma_alpha.r ~ dt( 0, 5^-2,1)T(0,) # Truncated t-distribution

# Prior on beta hyper-parameters
mu_beta_eur ~ dnorm(0, 5^-2)
sigma_beta ~ dt( 30, 10^-2,1)T(0,) # Truncated t-distribution 
sigma_beta.r ~ dt( 0, 3^-2,1)T(0,) # Truncated t-distribution


for(m in 1:n_pred){
ytilde[m] ~ dnorm(mu_pred.m[m], sigma^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]] *(xpred.m[m])
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma^-2)
}
}
"

## JAGS Model

R_Jags.data <- list(y.i = Pisa_Europe_Data$math,
                  x.i = Pisa_Europe_Data$year_orig,
                  n = nrow(Pisa_Europe_Data),
                  n_C = Pisa_Europe_Data$Country %>% unique() %>% length(),
                  C = as.numeric(factor(Pisa_Europe_Data$Country)),
                  R = country_region$region_num,
                  n_pred = nrow(pred_grid),
                  C_pred = pred_grid$Country_num,
                  xpred.m = pred_grid$year_orig,
                  n_R = Pisa_Europe_Data$Region %>% unique() %>% length())

R_Parnames <- c( "alpha.j","beta.j","sigma","sigma_alpha","sigma_beta","mu_alpha.r", 
               "mu_beta.r","mu_alpha_eur","mu_beta_eur", "ytilde", "yrep", "mu_pred.m", 
               "mu.i" ,"sigma_alpha.r", "sigma_beta.r")

# model
Region_Model <- jags(data = R_Jags.data,
              parameters.to.save = R_Parnames,
              model.file = textConnection(hmregion),
              n.iter = 10000,
              n.burnin = 2000,
              n.chains = 4,
              n.thin = 4)

save(Region_Model, file=here::here("Manuscript_Models", "Region_Model.Rdata"))
```

**R_Model fits a hierarchical model on the Pisa_Europe_Data by estimating the model parameters based on the estimates from its different level of hierarchy (geographical region)**

### Income as a hierarchical structure.

```{r Incomemodel}
if (!dir.exists(here::here("Manuscript_Models")))
  dir.create(here::here("Manuscript_Models"))

if(file.exists(here::here("Manuscript_Models",
                          "Income_Model.Rdata"))){
  load(here::here("Manuscript_Models",
                          "Income_Model.Rdata"))
  incomeJags <- FALSE
} else incomeJags <- TRUE
```

```{r, eval = incomeJags}
hmincome = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i])
}

# Prior on alphas to vary by income

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha.I[I[j]], sigma_alpha[I[j]]^-2)
beta.j[j] ~ dnorm(mu_beta.I[I[j]], sigma_beta^-2)
}

for (r in 1:n_I){
mu_alpha.I[r] ~ dnorm(mu_alpha_inc, sigma_alpha.inc^-2)
mu_beta.I[r] ~ dnorm(mu_beta_inc, sigma_beta.inc^-2)
sigma_alpha[r] ~ dt( 0, 5^-2,1)T(0,) # Truncated t-distribution
}

# Prior on sigma, model variation
sigma ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on alpha hyper-parameters
mu_alpha_inc ~ dnorm(500, 100^-2)
sigma_alpha.inc ~ dt( 30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on beta hyper-parameters
mu_beta_inc ~ dnorm(0, 5^-2)
sigma_beta ~ dt( 30, 10^-2,1)T(0,) # Truncated t-distribution
sigma_beta.inc ~ dt( 30, 10^-2,1)T(0,) # Truncated t-distribution


for(m in 1:n_pred){
ytilde[m] ~ dnorm(mu_pred.m[m], sigma^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]] *(xpred.m[m] - mean(xpred.m))
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma^-2)
}
}
"

## JAGS Model

I_Jags.data <- list(y.i = Pisa_Europe_Data$math,
                    x.i = Pisa_Europe_Data$year_orig,
                    n = nrow(Pisa_Europe_Data),
                    n_C = Pisa_Europe_Data$Country %>% unique() %>% length(),
                    C = as.numeric(factor(Pisa_Europe_Data$Country)),
                    I = country_income$income_num,
                    n_pred = nrow(pred_grid),
                    C_pred = pred_grid$Country_num,
                    xpred.m = pred_grid$year_orig,
                    n_I = Pisa_Europe_Data$Income %>% unique() %>% length())

I_Parnames <- c( "alpha.j","beta.j","sigma","sigma_alpha","sigma_beta","mu_alpha.I", 
                 "mu_beta.I","mu_alpha_inc","mu_beta_inc", "ytilde", "yrep", "mu_pred.m", 
                 "mu.i" ,"sigma_alpha.inc", "sigma_beta.inc")

# model
Income_Model <- jags(data = I_Jags.data,
                parameters.to.save = I_Parnames,
                model.file = textConnection(hmincome),
                n.iter = 10000,
                n.burnin = 2000,
                n.chains = 4,
                n.thin = 4)

save(Income_Model, file=here::here("Manuscript_Models", "Income_Model.Rdata"))
```

**I_Model fits a hierarchical model on the Pisa_Europe_Data by estimating the model parameters based on the estimates from its different level of hierarchy (income classification)**

### Income_Region as a hierarchical structure.

```{r IncomeRegionmodel}
if (!dir.exists(here::here("Manuscript_Models")))
  dir.create(here::here("Manuscript_Models"))

if(file.exists(here::here("Manuscript_Models",
                          "IncomeRegion_Model.Rdata"))){
  load(here::here("Manuscript_Models",
                          "IncomeRegion_Model.Rdata"))
  incomeregionJags <- FALSE
} else incomeregionJags <- TRUE
```

```{r, eval=incomeregionJags}
hmincome_region = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i] - mean(x.i))
}

# Prior on alphas to vary by income

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha.IR[IR[j]], sigma_alpha[IR[j]]^-2)
beta.j[j] ~ dnorm(mu_beta.IR[IR[j]], sigma_beta^-2)
}

for (r in 1:n_IR){
mu_alpha.IR[r] ~ dnorm(mu_alpha_inre, sigma_alpha.inre^-2)
mu_beta.IR[r] ~ dnorm(mu_beta_inre, sigma_beta.inre^-2)
sigma_alpha[r] ~ dt( 0, 5^-2,1)T(0,) # Truncated t-distribution
}

# Prior on sigma, model variation
sigma ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on alpha hyper-parameters
mu_alpha_inre ~ dnorm(500, 100^-2)
sigma_alpha.inre ~ dt( 30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on beta hyper-parameters
mu_beta_inre ~ dnorm(0, 5^-2)
sigma_beta ~ dt( 30, 10^-2,1)T(0,) # Truncated t-distribution
sigma_beta.inre ~ dt( 30, 10^-2,1)T(0,) # Truncated t-distribution


for(m in 1:n_pred){
ytilde[m] ~ dnorm(mu_pred.m[m], sigma^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]] *(xpred.m[m] - mean(xpred.m))
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma^-2)
}
}
"
IR_Jags.data <- list(y.i = Pisa_Europe_Data$math,
                    x.i = Pisa_Europe_Data$year_orig,
                    n = nrow(Pisa_Europe_Data),
                    n_C = Pisa_Europe_Data$Country %>% unique() %>% length(),
                    C = as.numeric(factor(Pisa_Europe_Data$Country)),
                    IR = country_incomeregion$incomeregion_num,
                    n_pred = nrow(pred_grid),
                    C_pred = pred_grid$Country_num,
                    xpred.m = pred_grid$year_orig,
                    n_IR = Pisa_Europe_Data$Income_Region %>% unique() %>% length())

IR_Parnames <- c( "alpha.j","beta.j","sigma","sigma_alpha","sigma_beta","mu_alpha.IR", 
                 "mu_beta.IR","mu_alpha_inre","mu_beta_inre", "ytilde", "yrep", "mu_pred.m", 
                 "mu.i" ,"sigma_alpha.inre", "sigma_beta.inre")
# model
IR_Model <- jags(data = IR_Jags.data,
                parameters.to.save = IR_Parnames,
                model.file = textConnection(hmincome_region),
                n.iter = 10000,
                n.burnin = 2000,
                n.chains = 4,
                n.thin = 4)

save(IR_Model, file=here::here("Manuscript_Models", "IncomeRegion_Model.Rdata"))
```

