---
title: "OECD Raw Data"
author: "Oluwayomi Akinfenwa"
date: "11/12/2023"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r}
library(haven)
library(intsvy)
library(tidyverse)
```

#### Creating directory to strore the raw data and the dictionary explaining the variables in the data.

```{r}
 dir.create(here::here("Saved_PISA_Data"))

pisaFile <- here::here("SavedData", "pisa.Rdata")
if (file.exists(pisaFile)){
  load(pisaFile)
}else {
  dir.create(here::here("SavedData"))
  pisa <- learningtower::load_student("all")
  save( pisa, file=pisaFile)
}

```


### Loading the raw 2022 PISA Data

**I renamed the raw data to STU_2022.sav**

```{r}
pisa22 <- here::here("Saved_PISA_Data", "pisa22.Rdata")
student22 <- haven::read_spss("STU_2022.sav") 
dictstudent22 <- labelled::generate_dictionary(student22)

save(student22, dictstudent22,file= pisa22)
```

### Loading the raw 2018 PISA Data

**I renamed the raw data to STU_2018.sav**

```{r}
pisa18 <- here::here("Saved_PISA_Data", "pisa18.Rdata")
student18 <- haven::read_spss("STU_2018.sav") 
dictstudent18 <- labelled::generate_dictionary(student18)

save(student18, dictstudent18,file= pisa18)
```

### Loading the raw 2015 PISA Data

**I renamed the raw data to STU_2015.sav**

```{r}
pisa15 <- here::here("Saved_PISA_Data", "pisa15.Rdata")
student15 <- haven::read_spss("STU_2015.sav") 
dictstudent15 <- labelled::generate_dictionary(student15)

save(student15, dictstudent15,file= pisa15)
```


*At the inception of PISA, the data were stored as text.file*

*There is a R package called pbiecek which contains the raw data for 2000 to 2012*. 

### Loading the raw PISA Data from 2012 through to 2003.

```{r}
### 2012
# pisa12 <- here::here("Saved_PISA_Data", "pisa12.Rdata")
# library(PISA2012lite)
# student12 <- student2012
# dictstudent12 <- student2012dict
# save(student12, dictstudent12,file= pisa12)
# 
# ### 2009
# pisa09 <- here::here("Saved_PISA_Data", "pisa09.Rdata")
# library(PISA2009lite)
# student09 <- student2009
# dictstudent09 <- student2009dict
# save(student09, dictstudent09,file= pisa09)
# 
# ### 2006
# pisa06 <- here::here("Saved_PISA_Data", "pisa06.Rdata")
# library(PISA2006lite)
# student06 <- student2006
# dictstudent06 <- student2006dict
# save(student06, dictstudent06,file= pisa06)
# 
# ### 2003
# pisa03 <- here::here("Saved_PISA_Data", "pisa03.Rdata")
# library(PISA2003lite)
# student03 <- student2003
# dictstudent03 <- student2003dict
# save(student03, dictstudent03,file= pisa03)
```

**The intsvy R package provides analysis and visualisation tools that considers the complex sample design (such as the replicate weights) in the calculation. Hence, I will use the package to calculate the mean of the raw data**

#### Loading all the raw data

```{r loading the data}
load(here::here("Saved_PISA_Data", "pisa22.Rdata"))

load(here::here("Saved_PISA_Data", "pisa18.Rdata"))

load(here::here("Saved_PISA_Data", "pisa15.Rdata"))

load(here::here("Saved_PISA_Data", "pisa12.Rdata"))

load(here::here("Saved_PISA_Data", "pisa09.Rdata"))

load(here::here("Saved_PISA_Data", "pisa06.Rdata"))

load(here::here("Saved_PISA_Data", "pisa03.Rdata"))
```

#### Averaging the data

**2022 data**

```{r averaging the 2022 data}
Student_2022 <- student22 |> select(c("CNT", starts_with("PV") & ends_with("MATH")))

DATA_2022 <-intsvy.mean.pv(pvnames = paste0("PV", 1:10, "MATH"), by = "CNT",
               data = student22, config = pisa_conf)

## Selecting the mean and country ISO code, renaming mean to math and creating a new column with year.

Math_2022 <- DATA_2022 |> 
  select(c("CNT", "Mean")) |>
  mutate(year = 2022) |>
  rename(math = Mean) |>
  as_tibble()
```

**2018 data **

```{r averaging the 2018 data}
Student_2018 <- student18 |> select(c("CNT", starts_with("PV") & ends_with("MATH")))

DATA_2018 <-intsvy.mean.pv(pvnames = paste0("PV", 1:10, "MATH"), by = "CNT",
               data = student18, config = pisa_conf)

## Selecting the mean and country ISO code, renaming mean to math and creating a new column with year.

Math_2018 <- DATA_2018 |> 
  select(c("CNT", "Mean")) |>
  mutate(year = 2018) |>
  rename(math = Mean) |>
  as_tibble()
```

**2015 data **

```{r averaging the 2015 data}
Student_2015 <- student15 |> select(c("CNT", starts_with("PV") & ends_with("MATH")))


DATA_2015 <-intsvy.mean.pv(pvnames = paste0("PV", 1:10, "MATH"), by = "CNT",
               data = student15, config = pisa_conf)

## Selecting the mean and country ISO code, renaming mean to math and creating a new column with year.

Math_2015 <- DATA_2015 |> 
  select(c("CNT", "Mean")) |>
  mutate(year = 2015) |>
  rename(math = Mean) |>
  as_tibble()
```

**2012 data **

```{r averaging the 2012 data}
#From the data W_FSTUWT is the final student weight -"FINAL STUDENT WEIGHT" 
Student_2012 <- student12 |> select(c("CNT", starts_with("PV") & ends_with("MATH"), "W_FSTUWT"))
data <-Student_2012 |>
   group_by(CNT) |>
   mutate(Average =(PV1MATH+PV2MATH+PV3MATH+PV4MATH+PV5MATH)/5) |>
  select(CNT, W_FSTUWT, Average)

Data_2012 <- data |> group_by(CNT) |>
  summarise(Mean = weighted.mean(Average, W_FSTUWT))

## I realised that some names are not the same in the data_2012 and WDI
# The WDI data does not have ISO code for Hong Kong, Korea, Shanghai, Chinese Taipei, 
# Turkey, United State of America
Data_2012 <- Data_2012 |>
  mutate(CNT = recode_factor(CNT,
                                "Hong Kong-China" = "Hong Kong SAR, China",
                                 "Turkey" = "Turkiye",
                                 "Korea" = "Korea, Rep.",
                                 "Kyrgyzstan" = "Kyrgyz Republic",
                                 "Republic of Moldova" = "Moldova",
                                 "Macao-China" = "Macao SAR, China",
                                 "China-Shanghai" = "China",
                                 "Tamil Nadu-India" = "India",
                                 "Chinese Taipei" = "Taiwan, China",
                                  "Miranda-Venezuela" = "Venezuela, RB",
                                  "Perm(Russian Federation)" = "Russian Federation",
                                  "Russian Federation" = "Russian federation", #in the data, Russian appeared twice and checking with Catherine's version, the second one is the right one. hence the need to drop this.
                                 "United States of America" = "United States"))

#The code below didn't work for me.
#DATA_2012 <-intsvy.mean.pv(pvnames = paste0("PV", 1:5, "MATH"), by = "CNT",
 #              data = student12, config = pisa_conf)

#It will interest us to know that the CNT column contains the country name instead of the ISO code
# every other year except 2009 and 2012 has the CNT has the ISO code, for uniformity it is advisable to 
# also include the ISO code to the data.

# A R package called countrycode contains the country name with its ISO code
#data(countrycode).
#I tried that package and realised that some of the countries does not have ISO code in that library.
# I decided to use the WDI data.
library(WDI)
WDI <- WDI_data$country
Countrycode <- WDI |>
  select(iso3c, country)

DATA_2012 <- Data_2012 |>
  left_join(Countrycode, join_by("CNT" =="country"))

## Selecting the mean and country ISO code, renaming mean to math and creating a new column with year.

Math_2012 <- DATA_2012 |> 
  select(c("iso3c", "Mean")) |>
  mutate(year = 2012) |>
  rename(math = Mean, CNT = iso3c) |>
  as_tibble()
```

**2009 data **

```{r averaging the 2009 data}
Student_2009 <- student09 |> select(c("CNT", starts_with("PV") & ends_with("MATH")))


Data_2009 <-intsvy.mean.pv(pvnames = paste0("PV", 1:5, "MATH"), by = "CNT",
               data = student09, config = pisa_conf)

Data_2009 <- Data_2009 |>
  mutate(CNT = recode_factor(CNT,
                                "Hong Kong-China" = "Hong Kong SAR, China",
                                 "Turkey" = "Turkiye",
                                 "Korea" = "Korea, Rep.",
                                 "Kyrgyzstan" = "Kyrgyz Republic",
                                 "Republic of Moldova" = "Moldova",
                                 "Macao-China" = "Macao SAR, China",
                                 "Shanghai-China" = "China",
                                 "Tamil Nadu-India" = "India",
                                 "Chinese Taipei" = "Taiwan, China",
                                  "Miranda-Venezuela" = "Venezuela, RB",
                                 "United State of America" = "United States"))

#It will interest us to know that the CNT column contains the country name instead of the ISO code
# every other year except 2009 and 2012 has the CNT has the ISO code, for uniformity it is advisable to 
# also include the ISO code to the data.

DATA_2009 <- Data_2009 |>
  left_join(Countrycode, join_by("CNT" =="country"))
## Selecting the mean and country ISO code, renaming mean to math and creating a new column with year.

Math_2009 <- DATA_2009 |> 
  select(c("iso3c", "Mean")) |>
  mutate(year = 2009) |>
  rename(math = Mean, CNT = iso3c) |>
  as_tibble()
```

*A report of 2009 data. I manually re-coded the names in the Data_2009, that has different name arrangement in the WDI data. Still, we have one country - Himachal Pradesh-India that has no corresponse. India appeared twice in mine and Catherine's version too*

**2006 data **

```{r averaging the 2006 data}
Student_2006 <- student06 |> select(c("CNT", starts_with("PV") & ends_with("MATH")))


DATA_2006 <-intsvy.mean.pv(pvnames = paste0("PV", 1:5, "MATH"), by = "CNT",
               data = student06, config = pisa_conf)

## Selecting the mean and country ISO code, renaming mean to math and creating a new column with year.

Math_2006 <- DATA_2006 |> 
  select(c("CNT", "Mean")) |>
  mutate(year = 2006) |>
  rename(math = Mean) |>
  as_tibble()
```

**2003 data **

```{r averaging the 2003 data}
Student_2003 <- student03 |> select(c("CNT", starts_with("PV") & ends_with("MATH")))


DATA_2003 <-intsvy.mean.pv(pvnames = paste0("PV", 1:5, "MATH"), by = "CNT",
               data = student03, config = pisa_conf)

## Selecting the mean and country ISO code, renaming mean to math and creating a new column with year.

Math_2003 <- DATA_2003 |> 
  select(c("CNT", "Mean")) |>
  mutate(year = 2003) |>
  rename(math = Mean) |>
  as_tibble()
```

**Row binding the entire data set**

```{r}
Pisa_Data <- rbind(Math_2003, Math_2006, Math_2009, Math_2012, Math_2015, Math_2018, Math_2022) |>
  drop_na() |>
  arrange(CNT)
```

**Joining the data together, we have 462 observations from 107 countries.**

**I manually checked these estimates with what Catherine has in 'mathmean.Rdata' and they are the same. mathmean.Rdata has 109 data because RUS appeared twice with the same values and IND appeared twice with different values. I experienced the same IND names in Data_2009, but in WDI package, it only has one ISO code for India, hence the reason why we dropped the other.**

**In conclusion, the values are the same with what Catherine calculated.**

### Loading the UNSD data for geographical classification of countries.

```{r regions}
UNSD <- read.csv(here::here("UNSD — Methodology.csv"))

Regions <- UNSD |> select(c("ISO.alpha3.Code","Region.Name", 
                               "Sub.region.Name"))

# We are interested in obtaining the region classification for countries that are present in our data.
#Therew are 103 countries in the Pisa_Data set.
Pisa_Country <- Pisa_Data |>
  select(CNT) |> unique()

# left joining the UNSD with the Pisa_Country
# Pisa_Country contains 103 countries, hence I will extract the region information for these countries.
country_reg <- Pisa_Country |>
  left_join(Regions, join_by(CNT == ISO.alpha3.Code))

# Renaming the variables
names(country_reg)[2] <- 'Continent'
names(country_reg)[3] <- 'Region'
```

*The UNSD csv file has 249 countries and the PISA data has 107 countries. Hence, we still have a total of 107 countries. We also did not lose any data*.

### Loading the income classification from the WDI package.

```{r}
library(WDI)
WDI <- WDI_data$country

WDI_Data <- WDI |> 
  select(c("iso3c","country", "income")) |>
  mutate(income = recode_factor(income,
        "Lower middle income" = "Middle Income",
        "Upper middle income" = "Middle Income",
        "High income" = "High Income"))

names(WDI_Data)[3] <- "Income"

# Joining the WDI data with the countrycode data.

countrycode_reg_inc <- country_reg |>
  left_join(WDI_Data, join_by(CNT == iso3c))
```

Hence, we proceed to joining the pisa_data with the country, region, and income information(countrycode_reg_inc).

```{r pisa_data}
pisaFileMaths <- here::here("Saved_PISA_Data", "pisamaths.Rdata")

PISA_Data <- Pisa_Data |>
  left_join(countrycode_reg_inc, join_by(CNT)) |>
  na.omit()

PISA_Data <- PISA_Data |> 
  select(-CNT)

save(PISA_Data, file =pisaFileMaths)
```

*The original pisa data set has 462 observations, By merging the two data set, we have 439 observations, 91 countries in total with 7 variables - year, math score, year_orig, country, continent, region, and income. Some ISO code does not have a valid name in the WDI package we used to give the country names.*







