---
title: "Visuals to compare the model estimates"
author: "Oluwayomi Akinfenwa"
date: "09/10/2023"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(lme4)
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
library(bayesplot)
library(patchwork)
library(ggragged)
library(geofacet)
```

Loading the two R.data containing the learning-tower data set and the processed data with Region and Income classification.

```{r loading the data}
load(here::here("SavedData", "pisam.Rdata"))
```

**We have 406 observations and for this analysis, we decided to examine European countries**

### Filtering European countries alone

```{r Europe}
Pisa_Europe_Data <- Pisa_Data |> filter(Continent == "Europe") |> arrange(Country)
```

**For the European countries, we have 230 observations from 40 countries.**

### Visualising the data

```{r}
# Joining the Income and Region together to form one new column
Pisa_Europe_Data <- unite(Pisa_Europe_Data, col = "Income_Region", c("Income", "Region"), sep = "_", remove = FALSE)

#Creating the grid for the prediction
country_names <- levels(factor(Pisa_Europe_Data$Country))
region_names <- levels(factor(Pisa_Europe_Data$Region))
income_names <- levels(factor(Pisa_Europe_Data$Income))
incomeregion_names <- levels(factor(Pisa_Europe_Data$Income_Region))

## Obtaining the index for the data
mu_index <- 1:nrow(Pisa_Europe_Data)

## Obtaining the region indexes

country_region <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         

pred_grid <- Pisa_Europe_Data |> 
  modelr::data_grid(Country, year_orig) |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region)))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> 
  left_join(REGION, join_by(Country))

```

### Exploratory data analysis

Question

Can we fit a linear regression model using lm fit and use the estimates to create this plot.

### An independent linear regression fit

The same slope

```{r}
Ind_Country_model <- lmer(math~ year_orig+(1|Country), data = Pisa_Europe_Data)

Ind_Country_Model <- coef(Ind_Country_model)$Country
Ind_Country_Model$Country <- rownames(Ind_Country_Model)
Ind_Country_Model <- Ind_Country_Model |>
  left_join(Country_region, join_by(Country)) |>
  select(-c(Country_num, region_num))
```

Varying slope

```{r}
Country_model <- lmer(math~ year_orig+(1+year_orig|Country), data = Pisa_Europe_Data)

Country_Model_IS <- coef(Country_model)$Country
Country_Model_IS$Country <- rownames(Country_Model_IS)
Country_Model_IS <- Country_Model_IS |>
  rename("slope" = "year_orig") |>
  mutate(slopesign = sign(slope)) |>
  left_join(Country_region, join_by(Country)) |>
  select(-c(Country_num, region_num)) |>
  arrange(slope)
```

## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "Ind_Country_Model.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_Model.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_Model.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_Model.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_Model.Rdata"))
```

### Results

#### Estimates from the independent-country-specific model

```{r}
Ind_Country_ModelSample <- Ind_C_Model$BUGSoutput$sims.matrix

Ind_CountryI <- spread_rvars(Ind_Country_ModelSample , alpha.j[Country_index]) |>
  mutate(Country = country_names[Country_index], term="Intercept") |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region,Income, term,rvar=alpha.j)

Global_slop <- spread_rvars(Ind_Country_ModelSample , beta.j)|> median_qi(beta.j)

## Credible interval
## Intercept Estimates
Ind_Country_Int_Est <- Ind_CountryI |> median_qi(rvar) |>
  mutate(Model = "Indepedent \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))

# Slope Estimates
Ind_Country_Slop_Est <- Global_slop[rep(seq_len(nrow(Global_slop)), 
                each = 40), ] |>
  mutate(Country_index = 1:40) |>
  mutate(Country = country_names[Country_index], 
         Model = "Indepedent \n Model") |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region,Model,rvar=beta.j, .lower, .upper)

```

#### Estimates from the country-specific model

```{r}
Country_ModelSample <- C_Model$BUGSoutput$sims.matrix

CountryI <- spread_rvars(Country_ModelSample , alpha.j[Country_index]) |>
  mutate(Country = country_names[Country_index], term="Intercept") |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region,Income, term,rvar=alpha.j)


CountryS <- spread_rvars(Country_ModelSample , beta.j[Country_index]) |>
  mutate(Country = country_names[Country_index], term="year_orig") |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region,Income, term,rvar=beta.j)

CountryIS <- rbind(CountryI, CountryS)


Country_IS_Est <- CountryIS |> mutate(coef=median(rvar))|> 
  select(-rvar, Country)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
Country_Int_Est <- CountryI |> median_qi(rvar) |>
  mutate(Model = "Country \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))
## Slope Estimates
Country_Slop_Est <- CountryS |> median_qi(rvar) |>
  mutate(Model = "Country \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))
```

### Estimates from the region hierarchical model

```{r}
Region_ModelSamples <- Region_Model$BUGSoutput$sims.matrix
# get_variables(Region_ModelSamples)

Region_I <- spread_rvars(Region_ModelSamples , mu_alpha.r[region_num]) |>
  mutate(Region = region_names[region_num], term = "Intercept") |>
  right_join(Country_region, by = join_by(Region==Region))|>
  rename(rvar =mu_alpha.r) |>
  select(Country,Region, term,rvar)

Region_S <- spread_rvars(Region_ModelSamples , mu_beta.r[region_num]) |>
  mutate(Region = region_names[region_num], term = "year_orig") |>
  right_join(Country_region, by = join_by(Region==Region))|>
  rename(rvar =mu_beta.r) |>
  select(Country,Region, term,rvar)

Region_IS <- rbind(Region_I, Region_S)

## The region country estimates
Rcountry_I <- spread_rvars(Region_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(Country_region, by = join_by(Country==Country))|>
  rename(rvar =alpha.j,Country = Country) |>
  select(Country, Region,Income, term,rvar)


Rcountry_S <- spread_rvars(Region_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(Country_region, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country = Country) |>
  select(Country, Region,Income, term,rvar)

Rcountry_IS <- rbind(Rcountry_I, Rcountry_S) 
```

### Tidying the estimates from the Region hierarchical model

```{r, fig.width=10, fig.height=8}
#median estimates
Region_IS_Est <- Region_IS |> mutate(coef=median(rvar))|> 
  pivot_wider(values_from=coef, names_from=term)

Rcountry_IS_Est <- Rcountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
Region_int_est <- Region_I |> median_qi(rvar) |>
  mutate(Model = "Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower ,.upper))
#Country estimates
Region_Int_Est <- Rcountry_I |> median_qi(rvar) |>
  mutate(Model = "Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))
## Slope Estimates
#Hierarchy estimates
Region_slop_est <- Region_S |> median_qi(rvar) |>
  mutate(Model = "Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower ,.upper))
#Country estimates
Region_Slop_Est <- Rcountry_S |> median_qi(rvar) |>
  mutate(Model = "Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))
```

### Estimates from the income hierarchical model

```{r}
Income_ModelSamples <- Income_Model$BUGSoutput$sims.matrix
# get_variables(Income_ModelSamples)
Income_I <- spread_rvars(Income_ModelSamples , mu_alpha.I[income_num]) |>
  mutate(Income = income_names[income_num], term = "Intercept") |>
  right_join(Country_income, by = join_by(Income==Income))|>
  rename(rvar =mu_alpha.I) |>
  select(Country,Region, Income, term,rvar)

Income_S <- spread_rvars(Income_ModelSamples , mu_beta.I[income_num]) |>
  mutate(Income = income_names[income_num], term = "year_orig") |>
  right_join(Country_income, by = join_by(Income==Income))|>
  rename(rvar =mu_beta.I) |>
  select(Country,Region, Income, term,rvar)

Income_IS <- rbind(Income_I, Income_S)

## The income country estimates
Icountry_I <- spread_rvars(Income_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(Country_income, by = join_by(Country==Country))|>
  rename(rvar =alpha.j, Country=Country) |>
  select(Country,Region, Income,Region, term,rvar)


Icountry_S <- spread_rvars(Income_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(Country_income, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country=Country) |>
  select(Country,Region, Income,Region, term,rvar)

Icountry_IS <- rbind(Icountry_I, Icountry_S) 
```

#### Tidying the estimates from the model

```{r, fig.width=10, fig.height=8}
INCOME_IS_EST <- Income_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

Income_IS_Est <- Icountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
Income_int_est <- Income_I |> median_qi(rvar) |>
  mutate(Model = "Income \n Model")|>
  select(c(Country,Region, Model,rvar, .lower ,.upper))
#Country estimates
Income_Int_Est <- Icountry_I |> median_qi(rvar) |>
  mutate(Model = "Income \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))

## Slope Estimates
#Hierarchy estimates
Income_slop_est <- Income_S |> median_qi(rvar) |>
  mutate(Model = "Income \n Model")|>
  select(c(Country,Region, Model,rvar, .lower ,.upper))
#Country estimates
Income_Slop_Est <- Icountry_S |> median_qi(rvar) |>
  mutate(Model = "Income \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))
```

### Estimates from the incomeregion hierarchical model

```{r}
IR_ModelSamples <- IR_Model$BUGSoutput$sims.matrix
# get_variables(IR_ModelSamples)
IncomeRegion_I <- spread_rvars(IR_ModelSamples , mu_alpha.IR[income_num]) |>
  mutate(Income_Region = incomeregion_names[income_num], term = "Intercept") |>
  right_join(Country_incomeregion, by = join_by(Income_Region ==Income_Region ))|>
  rename(rvar =mu_alpha.IR) |>
  select(Country,Region, Income_Region,term,rvar)

IncomeRegion_S <- spread_rvars(IR_ModelSamples , mu_beta.IR[income_num]) |>
  mutate(Income_Region  = incomeregion_names[income_num], term = "year_orig") |>
  right_join(Country_incomeregion, by = join_by(Income_Region ==Income_Region ))|>
  rename(rvar =mu_beta.IR) |>
  select(Country,Region,Income_Region,term,rvar)

IncomeRegion_IS <- rbind(IncomeRegion_I, IncomeRegion_S)

## The income country estimates
IRcountry_I <- spread_rvars(IR_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(Country_incomeregion, by = join_by(Country==Country))|>
  rename(rvar =alpha.j, Country=Country) |>
  select(Country,Region, Income_Region, term,rvar)


IRcountry_S <- spread_rvars(IR_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(Country_incomeregion, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country=Country) |>
  select(Country,Region, Income_Region, term,rvar)

IRcountry_IS <- rbind(IRcountry_I, IRcountry_S) 
```

#### The median and credible interval estimates for the IncomeRegion model

```{r}
## Median
IR_IS_EST <- IncomeRegion_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

IncomeRegion_IS_Est <- IRcountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
IncomeRegion_int_est <- IncomeRegion_I |> median_qi(rvar) |>
  mutate(Model = "Income-Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower ,.upper))
#Country estimates
Income_Region_Int_Est <- IRcountry_I |> median_qi(rvar) |>
  mutate(Model = "Income-Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))
## Slope Estimates
#Hierarchy estimates
IncomeRegion_slop_est <- IncomeRegion_S |> median_qi(rvar) |>
  mutate(Model = "Income-Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower ,.upper))
#Country estimates
Income_Region_Slop_Est <- IRcountry_S |> median_qi(rvar) |>
  mutate(Model = "Income-Region \n Model")|>
  select(c(Country,Region, Model,rvar, .lower, .upper))
```

A plot showing the model estimates and error-bars, facet by country and connect the dots for the estimates from the 4 models (An independent lm fits, Country-specific model and the three hierarchical models).

```{r}
## Hierarchical estimates
##Intercepts
Combined_int_estimates <- rbind(Region_int_est, Income_int_est,
                              IncomeRegion_int_est) |>
  arrange(Country)

Combined_slop_estimates <- rbind(Region_slop_est, Income_slop_est,
                              IncomeRegion_slop_est)|>
  arrange(Country)

Combined_int_estimates$Model <- factor(Combined_int_estimates$Model, 
                  levels = c("Region \n Model", "Income \n Model", "Income-Region \n Model"))

Combined_slop_estimates$Model <- factor(Combined_slop_estimates$Model, 
                  levels = c("Region \n Model", "Income \n Model", "Income-Region \n Model"))

## Countries estimates
Combined_Int_Estimates <- rbind(Ind_Country_Int_Est,
                            Country_Int_Est,Region_Int_Est,
                            Income_Int_Est,Income_Region_Int_Est) |>
  arrange(Country)

Combined_Slop_Estimates <- rbind(Ind_Country_Slop_Est,
                            Country_Slop_Est,Region_Slop_Est,
                            Income_Slop_Est,Income_Region_Slop_Est) |>
  arrange(Country)

Combined_Int_Estimates <- Combined_Int_Estimates |>
  left_join(country_incomeregion, join_by(Country))
Combined_Int_Estimates$Model <- factor(Combined_Int_Estimates$Model, 
                  levels = c("Indepedent \n Model","Country \n Model",
                             "Region \n Model", "Income \n Model",
                             "Income-Region \n Model"))

Combined_Slop_Estimates$Model <- factor(Combined_Slop_Estimates$Model, 
                  levels = c("Indepedent \n Model","Country \n Model",
                             "Region \n Model", "Income \n Model",
                             "Income-Region \n Model"))
```

### The plots

```{r}
## Comparing the model estimates
Region_color_flag <- c("Eastern Europe" = "lightseagreen",
                      "Northern Europe"="darkolivegreen3", 
                      "Southern Europe"="indianred", 
                      "Western Europe"="cyan1")

color_flag <- c("Indepedent \n Model" ="darkolivegreen4" ,
                "Country \n Model" ="purple2",
                "Region \n Model" = "blue3",
                "Income \n Model" = "brown4",
                "Income-Region \n Model"= "darkgoldenrod3")

strip <- ggh4x::strip_themed(background_x = ggh4x::elem_list_rect(fill = Region_color_flag))

## Intercept
pdf("Comparison_Int2.pdf",
    width = 12, height = 8)

ggplot(data = Combined_Int_Estimates)+
  geom_point(aes(x = Model, y = rvar,color = Model))+
  geom_line(aes(x = Model, y = rvar,group = Country), linetype = "dashed")+
  geom_errorbar(aes(x = Model,ymin= .lower, ymax= .upper,
                    color = Model), width= 0.1)+
  geom_point(data = Combined_int_estimates,
             aes(x = Model, y = rvar, color = Model),alpha = 0.45,
             position=position_nudge(x = 0.15))+
  geom_errorbar(data = Combined_int_estimates,
                aes(x = Model, ymin= .lower, ymax= .upper,
                    color = Model), width = 0.1, alpha = 0.45,
                position=position_nudge(x = 0.15))+
  scale_color_manual(values = color_flag)+
  ggh4x::facet_wrap2(~Country, strip= strip, scales = "free_y", nrow = 8)+
  xlab(" ")+ ylab("Intercept estimates")+
  theme(axis.line = element_line(color = "black"),
        axis.text.x = element_text(angle = 20,vjust = 0.75, 
      hjust = 0.60, face = "bold"))+theme_bw()+
  labs(x = " ", y= "Intercept estimates", color = "Model")+
  theme(axis.text.x = element_blank(),
      legend.position = "bottom")
dev.off()
```

#### Slope

```{r}
pdf("Comparison_Slope2.pdf",
    width = 12, height = 8)## Slope

ggplot(data = Combined_Slop_Estimates)+
  geom_point(aes(x = Model, y = rvar,color = Model))+
  geom_line(aes(x = Model, y = rvar,group = Country), linetype = "dashed")+
  geom_errorbar(aes(x = Model,ymin= .lower, ymax= .upper,
                    color = Model), width= 0.1)+
  geom_point(data = Combined_slop_estimates,
             aes(x = Model, y = rvar, color = Model),alpha = 0.45,
             position=position_nudge(x = 0.15))+
  geom_errorbar(data = Combined_slop_estimates,
                aes(x = Model, ymin= .lower, ymax= .upper,
                    color = Model), width = 0.1, alpha = 0.45,
                position=position_nudge(x = 0.15))+
  scale_color_manual(values = color_flag)+
  ggh4x::facet_wrap2(~Country, strip= strip, scales = "free_y", nrow = 8)+
  xlab(" ")+ ylab("Slope estimates")+
  theme(axis.line = element_line(color = "black"),
        axis.text.x = element_text(angle = 20,vjust = 0.75, 
      hjust = 0.60, face = "bold"))+theme_bw()+
  labs(x = " ", y= "Slope estimates", color = "Model")+
  theme(axis.text.x = element_blank(),
      legend.position = "bottom")
dev.off()
```

#### Comparing the country estimates

```{r}
## Comparing the country estimates
## Intercept
pdf("Comparison_Int1.pdf",
    width = 12, height = 8)

ggplot(data = Combined_Int_Estimates)+
  geom_point(aes(x = Model, y = rvar,color = Model))+
  geom_line(aes(x = Model, y = rvar,group = Country), linetype = "dashed")+
  geom_errorbar(aes(x = Model,ymin= .lower, ymax= .upper,
                    color = Model), width= 0.1)+
  geom_point(data = Combined_int_estimates,
             aes(x = Model, y = rvar, color = Model),alpha = 0.45,
             position=position_nudge(x = 0.15))+
  geom_errorbar(data = Combined_int_estimates,
                aes(x = Model, ymin= .lower, ymax= .upper,
                    color = Model), width = 0.1, alpha = 0.45,
                position=position_nudge(x = 0.15))+
  scale_color_manual(values = color_flag)+
  ggh4x::facet_wrap2(~Country, strip= strip, nrow = 8)+
  xlab(" ")+ ylab("Intercept estimates")+
  theme(axis.line = element_line(color = "black"),
        axis.text.x = element_text(angle = 20,vjust = 0.75, 
      hjust = 0.60, face = "bold"))+theme_bw()+
  labs(x = " ", y= "Intercept estimates", color = "Model")+
  theme(axis.text.x = element_blank(),
      legend.position = "bottom")
dev.off()
```

#### Slope

```{r}
## Slope
pdf("Comparison_slope1.pdf",
    width = 12, height = 8)
ggplot(data = Combined_Slop_Estimates)+
  geom_point(aes(x = Model, y = rvar,color = Model))+
  geom_line(aes(x = Model, y = rvar,group = Country), linetype = "dashed")+
  geom_errorbar(aes(x = Model,ymin= .lower, ymax= .upper,
                    color = Model), width= 0.1)+
  geom_point(data = Combined_slop_estimates,
             aes(x = Model, y = rvar, color = Model),alpha = 0.45,
             position=position_nudge(x = 0.15))+
  geom_errorbar(data = Combined_slop_estimates,
                aes(x = Model, ymin= .lower, ymax= .upper,
                    color = Model), width = 0.1,alpha = 0.45,
                position=position_nudge(x = 0.15))+
  scale_color_manual(values = color_flag)+
  ggh4x::facet_wrap2(~Country, strip= strip, nrow = 8)+
  xlab(" ")+ ylab("Slope estimates")+
  theme(axis.line = element_line(color = "black"),
        axis.text.x = element_text(angle = 20,vjust = 0.75, 
      hjust = 0.60, face = "bold"))+theme_bw()+
  labs(x = " ", y= "Slope estimates", color = "Model")+
  theme(axis.text.x = element_blank(),
      legend.position = "bottom")
dev.off()
```

#### Trying the geo_facet to group the countries according to its geo-political zones.

```{r}
load(here::here("SavedData", "Region_grouping.Rdata"))
C_codes <- country_reg |> filter(Continent == "Europe") |>
  select(name =Country, code = country) |> arrange(name)


row<-c(7,4,3,3,5,6,6,3,2,2,1,5,3,7,4,1,2,6,2,4,
       2,4,6,7,4,6,2,1,2,6,4,1,5,3,5,6,1,5,4,2)

col<-c(6,4,8,3,6,8,5,5,4,8,6,2,4,8,5,1,1,4,7,3,
       6,2,7,4,7,6,3,4,5,1,6,8,7,6,5,2,5,3,8,2)

geo_grid <- cbind(row,col,C_codes) 


## Comparing the model estimates
## Intercept
pdf("Comparison_Int.pdf",
    width = 12, height = 8)

ggplot(data = Combined_Int_Estimates)+
  geom_point(aes(x = Model, y = rvar,color = Model))+
  geom_line(aes(x = Model, y = rvar,group = Country), linetype = "dashed")+
  geom_errorbar(aes(x = Model,ymin= .lower, ymax= .upper,
                    color = Model), width= 0.1)+
  geom_point(data = Combined_int_estimates,
             aes(x = Model, y = rvar, color = Model),alpha = 0.45,
             position=position_nudge(x = 0.15))+
  geom_errorbar(data = Combined_int_estimates,
                aes(x = Model, ymin= .lower, ymax= .upper,
                    color = Model), width = 0.1, alpha = 0.45,
                position=position_nudge(x = 0.15))+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid, scales= "free_y")+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(),
      legend.position = "bottom")

dev.off()
  
###Slope
pdf("Comparison_slop.pdf",
    width = 12, height = 8)

ggplot(data = Combined_Slop_Estimates)+
  geom_point(aes(x = Model, y = rvar,color = Model))+
  geom_line(aes(x = Model, y = rvar,group = Country), linetype = "dashed")+
  geom_errorbar(aes(x = Model,ymin= .lower, ymax= .upper,
                    color = Model), width= 0.1)+
  geom_point(data = Combined_slop_estimates,
             aes(x = Model, y = rvar, color = Model),alpha = 0.45,
             position=position_nudge(x = 0.15))+
  geom_errorbar(data = Combined_slop_estimates,
                aes(x = Model, ymin= .lower, ymax= .upper,
                    color = Model), width = 0.1, alpha = 0.45,
                position=position_nudge(x = 0.15))+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid, scales= "free_y")+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(),
      legend.position = "bottom")
dev.off()
```



```{r}
## Comparing the country estimates

## To specify separate color for each region
# Can we create a dataframe with colors and country names?
#It didn't work.

P <- ggplot(data = Combined_Int_Estimates)+
  geom_point(aes(x = Model, y = rvar,color = Model))+
  geom_line(aes(x = Model, y = rvar,group = Country), linetype = "dashed")+
  geom_errorbar(aes(x = Model,ymin= .lower, ymax= .upper,
                    color = Model), width= 0.1)+
  geom_point(data = Combined_int_estimates,
             aes(x = Model, y = rvar, color = Model),alpha = 0.45,
             position=position_nudge(x = 0.15))+
  geom_errorbar(data = Combined_int_estimates,
                aes(x = Model, ymin= .lower, ymax= .upper,
                    color = Model), width = 0.1, alpha = 0.45,
                position=position_nudge(x = 0.15))+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid)+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()

fill_colors <- unique(ggplot_build(P)$data[[1]]$fill)

## Intercept
ggplot(data = Combined_Int_Estimates)+
  geom_point(aes(x = Model, y = rvar,color = Model))+
  geom_line(aes(x = Model, y = rvar,group = Country), linetype = "dashed")+
  geom_errorbar(aes(x = Model,ymin= .lower, ymax= .upper,
                    color = Model), width= 0.1)+
  geom_point(data = Combined_int_estimates,
             aes(x = Model, y = rvar, color = Model),alpha = 0.45,
             position=position_nudge(x = 0.15))+
  geom_errorbar(data = Combined_int_estimates,
                aes(x = Model, ymin= .lower, ymax= .upper,
                    color = Model), width = 0.1, alpha = 0.45,
                position=position_nudge(x = 0.15))+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid)+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(),strip.background = element_rect(fill = Combined_Int_Estimates$Region),
      legend.position = "bottom")
  
  
###Slope
ggplot(data = Combined_Slop_Estimates)+
  geom_point(aes(x = Model, y = rvar,color = Model))+
  geom_line(aes(x = Model, y = rvar,group = Country), linetype = "dashed")+
  geom_errorbar(aes(x = Model,ymin= .lower, ymax= .upper,
                    color = Model), width= 0.1)+
  geom_point(data = Combined_slop_estimates,
             aes(x = Model, y = rvar, color = Model),alpha = 0.45,
             position=position_nudge(x = 0.15))+
  geom_errorbar(data = Combined_slop_estimates,
                aes(x = Model, ymin= .lower, ymax= .upper,
                    color = Model), width = 0.1, alpha = 0.45,
                position=position_nudge(x = 0.15))+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid)+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(),strip.background = element_rect(fill =c ("red", "blue", "green", "orange4")),
      legend.position = "bottom")
```

