---
title: "Pre-Covid Analysis"
author: "Oluwayomi Akinfenwa"
date: "15/01/2024"
output:
  pdf_document:
    toc: yes
    toc_depth: '4'
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(lme4)
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
library(bayesplot)
library(patchwork)
library(ggragged)
```

Loading the PISA data for the European countries - Europe_Pisamaths.Rdata and filtering out data points for the year 2022.

```{r loading the data}
load(here::here("Saved_PISA_Data", "Europe_Pisamaths.Rdata"))

Pisa2_Europe_Data <- Pisa_Europe_Data |> filter(year != 2022)
```

### Creating the grid for the prediction

```{r}
country_names <- levels(factor(Pisa_Europe_Data$Country))
region_names <- levels(factor(Pisa_Europe_Data$Region))
income_names <- levels(factor(Pisa_Europe_Data$Income))
incomeregion_names <- levels(factor(Pisa_Europe_Data$Income_Region))

## Obtaining the index for the data
mu_index <- 1:nrow(Pisa_Europe_Data)

## Obtaining the region indexes
country_region <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes
country_income <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes
country_incomeregion <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         

pred_grid2 <- Pisa2_Europe_Data |> 
  modelr::data_grid(Country, year_orig) |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region)))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
```

### Exploratory data analysis

**Fitting a linear regression model on pre-covid data set**

```{r}
library(broom)
## The function reframe- creates a new data-frame by applying functions (in the previous line of code) to columns of an existing data frame.

#Weighted least squares. The weight is the reciprocal of the square of the standard error.
Country2_Model <- Pisa2_Europe_Data |>
  nest_by(Country) |>
  mutate(mod = list(lm(math ~ year_orig, weights = sigma^-2, data = data))) |>
  reframe(tidy(mod))|>
   select(Country, term, estimate)

### Tidying the estimates
### We are interested in arranging the countries according to their increasing slope.
Country2_Model_IS <- Country2_Model  |>
   pivot_wider(values_from = estimate, names_from = term) |>
   rename("slope" = "year_orig") |>
  left_join(Country_region, join_by(Country)) |>
  select(-c(Country_num, region_num))
```

Comparing pre-covid and post-covid slopes

```{r}
pre_covid <- Country2_Model_IS |> select(Country,slope) |> rename("pre" = "slope")
post_covid <- Country_Model_IS |> select(Country,slope) |> rename("post" = "slope")

Covid_Slopes <- pre_covid |>
  left_join(post_covid, join_by(Country)) |>
  pivot_longer(c(pre,post), names_to = "Slope", values_to = "Estimates")

### Visualising the estimates

pdf("covid_impact1.pdf",
    width = 12,
    height = 9)
ggplot(data = Covid_Slopes,
       aes(x = Estimates, y = Country, color = Slope))+
  geom_point()
dev.off()

## Creating a box-plot representation of the model.

pdf("covid_impact2.pdf",
    width = 12,
    height = 9)
ggplot(data = Covid_Slopes,
       aes(x = Estimates, y =Slope))+
  geom_boxplot()
dev.off()
```


### Running the hierarchical models to see the impact of covid

### Region as a hierarchical structure.

```{r Regionmodel}

if(file.exists(here::here("Region_Model.Rdata"))){
  load(here::here( "Region_Model.Rdata"))
  regionJags <- FALSE
} else regionJags <- TRUE
```

```{r, eval = regionJags}
hmregion2 = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i] )
sigma_y[i] <- sqrt(sigma[i]^2 + sigma.m^2)
}

# Prior on alphas to vary by region

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha.r[R[j]], sigma_alpha[R[j]]^-2)
beta.j[j] ~ dnorm(mu_beta.r[R[j]], sigma_beta^-2)
}

for (r in 1:n_R){
mu_alpha.r[r] ~ dnorm(mu_alpha_eur, sigma_alpha.r^-2)
mu_beta.r[r] ~ dnorm(mu_beta_eur, sigma_beta.r^-2)
sigma_alpha[r] ~ dt( 0, 5^-2,1)T(0,) # Truncated t-distribution
}

# Prior on sigma, model variation
sigma.m ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on alpha hyper-parameters
mu_alpha_eur ~ dnorm(500, 100^-2)
sigma_alpha.r ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution

# Prior on beta hyper-parameters
mu_beta_eur ~ dnorm(0, 2^-2)
sigma_beta ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution 
sigma_beta.r ~ dt( 0, 1^-2,1)T(0,) # Truncated t-distribution


for(m in 1:n_pred){
ytilde[m] ~ dnorm(mu_pred.m[m], sigma.m^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]] *(xpred.m[m])
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)
}
}
"

## JAGS Model

R_Jags.data2 <- list(y.i = Pisa2_Europe_Data$math,
                  x.i = Pisa2_Europe_Data$year_orig,
                  sigma = Pisa2_Europe_Data$sigma,
                  n = nrow(Pisa2_Europe_Data),
                  n_C = Pisa2_Europe_Data$Country %>% unique() %>% length(),
                  C = as.numeric(factor(Pisa2_Europe_Data$Country)),
                  R = country_region$region_num,
                  n_pred = nrow(pred_grid2),
                  C_pred = pred_grid2$Country_num,
                  xpred.m = pred_grid2$year_orig,
                  n_R = Pisa2_Europe_Data$Region %>% unique() %>% length())

R_Parnames <- c( "alpha.j","beta.j","sigma_y","sigma.m","sigma_alpha","sigma_beta",
                 "mu_alpha.r","mu_beta.r","mu_alpha_eur","mu_beta_eur", "ytilde", 
                 "yrep","mu_pred.m", "mu.i" ,"sigma_alpha.r", "sigma_beta.r")

# model
Region_Model2 <- jags(data = R_Jags.data2,
              parameters.to.save = R_Parnames,
              model.file = textConnection(hmregion2),
              n.iter = 10000,
              n.burnin = 2000,
              n.chains = 4,
              n.thin = 4)

save(Region_Model2, file=here::here("Region_Model.Rdata"))
```

**R_Model fits a hierarchical model on the Pisa2_Europe_Data by estimating the model parameters based on the estimates from its different level of hierarchy (geographical region)**

### Income as a hierarchical structure.

```{r Incomemodel}
if(file.exists(here::here("Income_Model.Rdata"))){
  load(here::here("Income_Model.Rdata"))
  incomeJags <- FALSE
} else incomeJags <- TRUE
```

```{r, eval = incomeJags}
hmincome2 = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i])
sigma_y[i] <- sqrt(sigma[i]^2 + sigma.m^2)
}

# Prior on alphas to vary by income

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha.I[I[j]], sigma_alpha[I[j]]^-2)
beta.j[j] ~ dnorm(mu_beta.I[I[j]], sigma_beta^-2)
}

for (r in 1:n_I){
mu_alpha.I[r] ~ dnorm(mu_alpha_inc, sigma_alpha.inc^-2)
mu_beta.I[r] ~ dnorm(mu_beta_inc, sigma_beta.inc^-2)
sigma_alpha[r] ~ dt( 0, 5^-2,1)T(0,) # Truncated t-distribution
}

# Prior on sigma, model variation
sigma.m ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on alpha hyper-parameters
mu_alpha_inc ~ dnorm(500, 100^-2)
sigma_alpha.inc ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution

# Prior on beta hyper-parameters
mu_beta_inc ~ dnorm(0, 2^-2)
sigma_beta ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution
sigma_beta.inc ~ dt( 0, 1^-2,1)T(0,) # Truncated t-distribution


for(m in 1:n_pred){
ytilde[m] ~ dnorm(mu_pred.m[m], sigma.m^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]] *(xpred.m[m] - mean(xpred.m))
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)
}
}
"

## JAGS Model

I_Jags.data2 <- list(y.i = Pisa2_Europe_Data$math,
                    x.i = Pisa2_Europe_Data$year_orig,
                    sigma = Pisa2_Europe_Data$sigma,
                    n = nrow(Pisa2_Europe_Data),
                    n_C = Pisa2_Europe_Data$Country %>% unique() %>% length(),
                    C = as.numeric(factor(Pisa2_Europe_Data$Country)),
                    I = country_income$income_num,
                    n_pred = nrow(pred_grid2),
                    C_pred = pred_grid2$Country_num,
                    xpred.m = pred_grid2$year_orig,
                    n_I = Pisa2_Europe_Data$Income %>% unique() %>% length())

I_Parnames <- c("alpha.j","beta.j","sigma_y","sigma.m","sigma_alpha","sigma_beta",
                 "mu_alpha.I","mu_beta.I","mu_alpha_inc","mu_beta_inc", "ytilde", 
                "yrep","mu_pred.m", "mu.i" ,"sigma_alpha.inc", "sigma_beta.inc")
 
# model
Income_Model2 <- jags(data = I_Jags.data2,
                parameters.to.save = I_Parnames,
                model.file = textConnection(hmincome2),
                n.iter = 10000,
                n.burnin = 2000,
                n.chains = 4,
                n.thin = 4)

save(Income_Model2, file=here::here("Income_Model.Rdata"))
```

**I_Model fits a hierarchical model on the Pisa_Europe_Data by estimating the model parameters based on the estimates from its different level of hierarchy (income classification)**

### Income_Region as a hierarchical structure.

```{r IncomeRegionmodel}
if(file.exists(here::here("IncomeRegion_Model.Rdata"))){
  load(here::here("IncomeRegion_Model.Rdata"))
  incomeregionJags <- FALSE
} else incomeregionJags <- TRUE
```

```{r, eval=incomeregionJags}
hmincome_region2 = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i] - mean(x.i))
sigma_y[i] <- sqrt(sigma[i]^2 + sigma.m^2)
}

# Prior on alphas to vary by income

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha.IR[IR[j]], sigma_alpha[IR[j]]^-2)
beta.j[j] ~ dnorm(mu_beta.IR[IR[j]], sigma_beta^-2)
}

for (r in 1:n_IR){
mu_alpha.IR[r] ~ dnorm(mu_alpha_inre, sigma_alpha.inre^-2)
mu_beta.IR[r] ~ dnorm(mu_beta_inre, sigma_beta.inre^-2)
sigma_alpha[r] ~ dt( 0, 5^-2,1)T(0,) # Truncated t-distribution
}

# Prior on sigma, model variation
sigma.m ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on alpha hyper-parameters
mu_alpha_inre ~ dnorm(500, 100^-2)
sigma_alpha.inre ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution

# Prior on beta hyper-parameters
mu_beta_inre ~ dnorm(0, 2^-2)
sigma_beta ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution
sigma_beta.inre ~ dt( 0, 1^-2,1)T(0,) # Truncated t-distribution


for(m in 1:n_pred){
ytilde[m] ~ dnorm(mu_pred.m[m], sigma.m^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]] *(xpred.m[m] - mean(xpred.m))
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)
}
}
"
IR_Jags.data2 <- list(y.i = Pisa2_Europe_Data$math,
                    x.i = Pisa2_Europe_Data$year_orig,
                    sigma = Pisa2_Europe_Data$sigma,
                    n = nrow(Pisa2_Europe_Data),
                    n_C = Pisa2_Europe_Data$Country %>% unique() %>% length(),
                    C = as.numeric(factor(Pisa2_Europe_Data$Country)),
                    IR = country_incomeregion$incomeregion_num,
                    n_pred = nrow(pred_grid2),
                    C_pred = pred_grid2$Country_num,
                    xpred.m = pred_grid2$year_orig,
                    n_IR = Pisa2_Europe_Data$Income_Region %>% unique() %>% length())

IR_Parnames <- c("alpha.j","beta.j","sigma_y","sigma.m","sigma_alpha","sigma_beta",
                 "mu_alpha.IR","mu_beta.IR","mu_alpha_inre","mu_beta_inre","yrep",
                 "ytilde","mu_pred.m", "mu.i","sigma_alpha.inre","sigma_beta.inre")
# model
IR_Model2 <- jags(data = IR_Jags.data2,
                parameters.to.save = IR_Parnames,
                model.file = textConnection(hmincome_region2),
                n.iter = 10000,
                n.burnin = 2000,
                n.chains = 4,
                n.thin = 4)

save(IR_Model2, file=here::here("IncomeRegion_Model.Rdata"))
```


### Pulling out the hierarchical model country-sigmas before and after covid

```{r}

RegionCovid_Samples <- Region_Model2$BUGSoutput$sims.matrix
IncomeCovid_Samples <- Income_Model2$BUGSoutput$sims.matrix
IRCovid_Samples <- IR_Model2$BUGSoutput$sims.matrix

#Sigmas
#Region
preCovid_RSigma <- spread_rvars(RegionCovid_Samples , sigma_alpha[region_num]) |>
  mutate(Region = region_names[region_num]) |>
  mutate(preCovid = median(sigma_alpha)) |>
  select(Region, preCovid)

postCovid_RSigma <- spread_rvars(Region_ModelSamples , sigma_alpha[region_num]) |>
  mutate(Region = region_names[region_num]) |>
  mutate(postCovid = median(sigma_alpha)) |>
  select(Region, postCovid)

Covid_RSigma <- preCovid_RSigma |>
  left_join(postCovid_RSigma, join_by(Region)) |>
  pivot_longer(c(preCovid, postCovid), names_to = "Sigma", values_to = "Estimates")

pdf("covid_impact_RH.pdf",
    width = 12,
    height = 9)
ggplot(Covid_RSigma,
       aes(x= Estimates, y = Region, color = Sigma))+
  geom_point()
dev.off()

#Income
preCovid_ISigma <- spread_rvars(IncomeCovid_Samples , sigma_alpha[income_num]) |>
  mutate(Income = income_names[income_num]) |>
 mutate(preCovid = median(sigma_alpha)) |>
  select(Income, preCovid)

postCovid_ISigma <- spread_rvars(Income_ModelSamples, sigma_alpha[income_num]) |>
  mutate(Income = income_names[income_num]) |>
  mutate(postCovid = median(sigma_alpha)) |>
  select(Income, postCovid)

Covid_ISigma <- preCovid_ISigma |>
  left_join(postCovid_ISigma, join_by(Income)) |>
  pivot_longer(c(preCovid, postCovid), names_to = "Sigma", values_to = "Estimates")

pdf("covid_impact_IH.pdf",
    width = 12,
    height = 9)
ggplot(Covid_ISigma,
       aes(x= Estimates, y = Income, color = Sigma))+
  geom_point()
dev.off()

#Income-Region
preCovid_IRSigma <- spread_rvars(IRCovid_Samples , sigma_alpha[IR_num]) |>
  mutate(IR = incomeregion_names[IR_num]) |>
  mutate(preCovid = median(sigma_alpha)) |>
  select(IR, preCovid)

postCovid_IRSigma <- spread_rvars(IR_ModelSamples , sigma_alpha[IR_num]) |>
  mutate(IR= incomeregion_names[IR_num]) |>
  mutate(postCovid = median(sigma_alpha)) |>
  select(IR, postCovid)

Covid_IRSigma <- preCovid_IRSigma |>
  left_join(postCovid_IRSigma, join_by(IR)) |>
  pivot_longer(c(preCovid, postCovid), names_to = "Sigma", values_to = "Estimates")

pdf("covid_impact_IRH.pdf",
    width = 12,
    height = 9)
ggplot(Covid_IRSigma,
       aes(x= Estimates, y = IR, color = Sigma))+
  geom_point()
dev.off()

```

#### Pulling the overall sigmas

```{r}
#Region
preCovid_RS <-spread_rvars(RegionCovid_Samples, sigma_y[i])|>
  mutate(Sigma = median(sigma_y), R_Model = "preCovid") |>
  select(Sigma, R_Model)

postCovid_RS <- spread_rvars(Region_ModelSamples , sigma_y[i]) |>
  mutate(Sigma = median(sigma_y),R_Model = "postCovid") |>
  select(Sigma, R_Model)

Covid_RS <- rbind(preCovid_RS, postCovid_RS)

pdf("covid_impact_RH2.pdf",
    width = 12,
    height = 9)
ggplot(data = Covid_RS,
       aes(y= Sigma, x = R_Model)) +
  geom_boxplot()
dev.off()

#Income
preCovid_IS <-spread_rvars(IncomeCovid_Samples, sigma_y[i])|>
  mutate(Sigma = median(sigma_y), I_Model = "preCovid") |>
  select(Sigma, I_Model)

postCovid_IS <- spread_rvars(Income_ModelSamples , sigma_y[i]) |>
  mutate(Sigma = median(sigma_y),I_Model = "postCovid") |>
  select(Sigma, I_Model)

Covid_IS <- rbind(preCovid_IS, postCovid_IS)

pdf("covid_impact_IH2.pdf",
    width = 12,
    height = 9)
ggplot(data = Covid_IS,
       aes(y= Sigma, x = I_Model)) +
  geom_boxplot()
dev.off()

#Income-Region
preCovid_IRS <-spread_rvars(IRCovid_Samples, sigma_y[i])|>
  mutate(Sigma = median(sigma_y), IR_Model = "preCovid") |>
  select(Sigma, IR_Model)

postCovid_IRS <- spread_rvars(IR_ModelSamples , sigma_y[i]) |>
  mutate(Sigma = median(sigma_y),IR_Model = "postCovid") |>
  select(Sigma, IR_Model)

Covid_IRS <- rbind(preCovid_IRS, postCovid_IRS)

pdf("covid_impact_IRH2.pdf",
    width = 12,
    height = 9)
ggplot(data = Covid_IRS,
       aes(y= Sigma, x = IR_Model)) +
  geom_boxplot()
dev.off()
```

Country-specific model

```{r Countrymodel}
if(file.exists(here::here("Country_Model.Rdata"))){
  load(here::here("Country_Model.Rdata"))
  countryJags <- FALSE
} else countryJags <- TRUE
```

```{r, eval = countryJags}
C_JAGS_Model2 = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i])
sigma_y[i] <- sqrt(sigma[i]^2 + sigma.m^2)
}

# Prior on country alphas

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha, sigma_alpha^-2)
beta.j[j] ~ dnorm(mu_beta, sigma_beta^-2)
}

# Prior on sigma, model variation
sigma.m ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution
mu_alpha ~ dnorm(500, 100^-2)
mu_beta ~ dnorm(0, 2^-2)
sigma_alpha ~ dt(0, 5^-2,1)T(0,) # Truncated t-distribution
sigma_beta ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution 


# Setting up the posterior
for(m in 1:n_pred){
ytilde[m] ~ dnorm(mu_pred.m[m], sigma.m^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]] *(xpred.m[m])
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)
}
}
"

## JAGS Model
C_Jags.data2 <- list(y.i = Pisa2_Europe_Data$math,
                    x.i = Pisa2_Europe_Data$year_orig,
                    sigma = Pisa2_Europe_Data$sigma,
                    n = nrow(Pisa2_Europe_Data),
                    n_C = Pisa2_Europe_Data$Country |> unique() |> length(),
                    C = as.numeric(factor(Pisa2_Europe_Data$Country)),
                    n_pred = nrow(pred_grid2),
                    C_pred = pred_grid2$Country_num,
                    xpred.m = pred_grid2$year_orig)

C_Parnames <- c("alpha.j","beta.j", "mu_alpha", "mu_beta","sigma_y","sigma.m",
                "sigma_alpha","sigma_beta","ytilde", "yrep","mu_pred.m","mu.i")

# model
C_Model2 <- jags(data = C_Jags.data2,
              parameters.to.save = C_Parnames,
              model.file = textConnection(C_JAGS_Model2),
              n.iter = 10000,
              n.burnin = 2000,
              n.chains = 4,
              n.thin = 4)

save(C_Model2, file=here::here("Country_Model.Rdata"))
```

```{r}
preCovid_RS <-spread_rvars(RegionCovid_Samples, sigma_y[i])|>
  mutate(Sigma = median(sigma_y), R_Model = "preCovid") |>
  select(Sigma, R_Model)
```

