---
title: "BRMS Model estimates"
author: "Oluwayomi Akinfenwa"
date: "13/12/2023"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(stringr)
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
library(bayesplot)
library(patchwork)
library(ggragged)
library(geofacet)
```

Loading the two R.data containing the learning-tower data set and the processed data with Region and Income classification.

```{r loading the data}
load(here::here("SavedData", "pisam.Rdata"))
```

**We have 406 observations and for this analysis, we decided to examine European countries**

### Filtering European countries alone

```{r Europe}
Pisa_Europe_Data <- Pisa_Data |> filter(Continent == "Europe") |> arrange(Country)
```

**For the European countries, we have 230 observations from 40 countries.**

### Visualising the data

```{r}
# Joining the Income and Region together to form one new column
Pisa_Europe_Data <- unite(Pisa_Europe_Data, col = "Income_Region", c("Income", "Region"), sep = "_", remove = FALSE)

#Creating the grid for the prediction
country_names <- levels(factor(Pisa_Europe_Data$Country))
region_names <- levels(factor(Pisa_Europe_Data$Region))
income_names <- levels(factor(Pisa_Europe_Data$Income))
incomeregion_names <- levels(factor(Pisa_Europe_Data$Income_Region))

## Obtaining the index for the data
mu_index <- 1:nrow(Pisa_Europe_Data)

## Obtaining the region indexes

country_region <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         

pred_grid <- Pisa_Europe_Data |> 
  modelr::data_grid(Country, year_orig) |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region)))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> 
  left_join(REGION, join_by(Country))
```


## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```

### Results

#### Estimates from the independent-country-specific model

```{r}
## Pulling the intercept results. The global intercept (b_Intercept) and the country offsets.

CountryInd_brmsI <- spread_rvars(CountryInd_BRMSModel, r_Country[Country,term], b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(Country = stringr::str_replace_all(Country, fixed("."), " ")) |>
  mutate(r_Country = r_Country+ b_Intercept) |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region, Income, term, rvar=r_Country)

## Pulling the slope results. The global slope (b_year_orig) as the slope estimates for all the countries
CountryInd_brmsS <- spread_rvars(CountryInd_BRMSModel, r_Country[Country,term], b_year_orig) |> mutate(term = "year_orig") |>
  mutate(Country = stringr::str_replace_all(Country, fixed("."), " "))  |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region, Income, term, rvar= b_year_orig)

## Tidying the estimates
CountryInd_brmsIS <- rbind(CountryInd_brmsI, CountryInd_brmsS)

CountryInd_brmsIS_Est <- CountryInd_brmsIS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)


## Credible interval
## Intercept Estimates
IndCountry_Int_BRMS_Est <- CountryInd_brmsI |> median_qi(rvar) |>
  select(c(Country,Region, Income,rvar, .lower, .upper))

## Slope Estimates
IndCountry_Slop_BRMS_Est <- CountryInd_brmsS |> median_qi(rvar) |>
  select(c(Country,Region, Income,rvar, .lower, .upper))
```

#### Estimates from the country-specific model

```{r}
## Pulling the intercept results. The global intercept (b_Intercept) and the country offsets.
Country_brmsI <- spread_rvars(Country_BRMSModel, r_Country[Country,term], b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(Country = stringr::str_replace_all(Country, fixed("."), " ")) |>
  mutate(r_Country = r_Country+ b_Intercept) |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region, Income, term, rvar=r_Country)

## Pulling the slope results. The global slope (b_year_orig) and the country offsets.
Country_brmsS <- spread_rvars(Country_BRMSModel, r_Country[Country,term], b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(Country = stringr::str_replace_all(Country, fixed("."), " ")) |>
  mutate(r_Country = r_Country+ b_year_orig) |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region, Income, term, rvar=r_Country)

## Tidying the estimates
Country_brmsIS <- rbind(Country_brmsI, Country_brmsS)

Country_brmsIS_Est <- Country_brmsIS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
Country_Int_BRMS_Est <- Country_brmsI |> median_qi(rvar) |>
  select(c(Country,Region, Income,rvar, .lower, .upper))

## Slope Estimates
Country_Slop_BRMS_Est <- Country_brmsS |> median_qi(rvar) |>
  select(c(Country,Region, Income,rvar, .lower, .upper))
```

#### Estimates from the Region hierarchical model

```{r}
brmsRI <- spread_rvars(Region_BRMSModel, r_Region[group1,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Region = r_Region+ b_Intercept) |>
  rename(rvar=r_Region, Region = group1) |>
  select(Region, term, rvar)

brmsRS <- spread_rvars(Region_BRMSModel, r_Region[group1,term], b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Region = r_Region+  b_year_orig) |>
  rename(rvar=r_Region, Region = group1)|>
  select(Region, term, rvar)


brmsRegion <- rbind(brmsRI, brmsRS) 

## The region country estimates

Rcountry_brmsI <- spread_rvars(Region_BRMSModel, r_Region[group1,term],r_Country[group,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_region, by = join_by(group==Country,group1==Region)) |> #this join everything from the country_region with its intercession from the model result
  mutate(r_Country =  r_Country+ r_Region+ b_Intercept) |>
  rename(rvar=r_Country,Region=group1, Country =group) |>
  select(Country,Region, Income, term, rvar)



Rcountry_brmsS <- spread_rvars(Region_BRMSModel, r_Region[group1,term],r_Country[group,term],b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_region, by = join_by(group==Country,group1==Region)) |>
  mutate(r_Country =  r_Country+ r_Region+ b_year_orig) |>
  rename(rvar=r_Country,Region=group1, Country =group) |>
  select(Country,Region, Income, term, rvar)

Rcountry_brms <- rbind(Rcountry_brmsI, Rcountry_brmsS) 
```

### Tidying the estimates from the Region hierarchical model

```{r}
#median estimates
RegionBRMS_IS_Est <- brmsRegion |> mutate(coef=median(rvar))|>
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

RcountryBRMS_IS_Est <- Rcountry_brms |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)
```

#### Estimates from the income hierarchical model

```{r}
brmsIncome_I <- spread_rvars(Income_BRMSModel, r_Income[group1,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Income = r_Income+ b_Intercept) |>
  rename(rvar=r_Income) |>
  select(group1, term, rvar)

brmsIncome_S <- spread_rvars(Income_BRMSModel, r_Income[group1,term], b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Income = r_Income+  b_year_orig) |>
  rename(rvar=r_Income)|>
  select(group1, term, rvar)


brmsIncome <- rbind(brmsIncome_I, brmsIncome_S)
```

pulling the intercepts and slopes for each country based on the influence of the Income hierarchy

```{r}
Icountry_brmsI <- spread_rvars(Income_BRMSModel, r_Income[group1,term],r_Country[group,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_income, by = join_by(group==Country,group1==Income)) |> #this join everything from the country_Income with its intercession from the model result
  mutate(r_Country =  r_Country+ r_Income+ b_Intercept) |>
  rename(rvar=r_Country, Country = group, Income = group1) |>
  select(Country, Income,Region, term, rvar)


Icountry_brmsS <- spread_rvars(Income_BRMSModel, r_Income[group1,term],r_Country[group,term],b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_income, by = join_by(group==Country,group1==Income)) |>
  mutate(r_Country =  r_Country+ r_Income+ b_year_orig) |>
  rename(rvar=r_Country, Country = group, Income = group1) |>
  select(Country, Income, Region, term, rvar)

Icountry_brms <- rbind(Icountry_brmsI, Icountry_brmsS) 
```

#### Tidying the estimates from the income model

```{r, fig.width=10, fig.height=8}
INCOME_BRMS_IS_EST <- brmsIncome |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

Income_BRMS_IS_Est <- Icountry_brms |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)
```

#### Estimates from the IncomeRegion hierarchical model

```{r}
brms_IncomeRegion_I <- spread_rvars(IncomeRegion_BRMSModel, r_Income_Region[group1,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Income_Region = r_Income_Region+ b_Intercept) |>
  rename(rvar=r_Income_Region, `Income_Region` = group1) |>
  select(Income_Region, term, rvar)

brms_IncomeRegion_S <- spread_rvars(IncomeRegion_BRMSModel, r_Income_Region[group1,term], b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Income_Region = r_Income_Region+  b_year_orig) |>
  rename(rvar=r_Income_Region, `Income_Region` = group1) |>
  select(Income_Region, term, rvar)


brms_IncomeRegion <- rbind(brms_IncomeRegion_I, brms_IncomeRegion_S)
```

pulling the intercepts and slopes for each country based on the influence of the Income-Region hierarchy.

```{r}
IRcountry_brmsI <- spread_rvars(IncomeRegion_BRMSModel, r_Income_Region[group1,term],r_Country[group,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_incomeregion, by = join_by(group==Country,group1==Income_Region)) |> #this join everything from the country_Income with its intercession from the model result
  mutate(r_Country =  r_Country+ r_Income_Region+ b_Intercept) |>
  rename(rvar=r_Country, Country = group, Income_Region = group1) |>
  select(Country, Income_Region,Region, term, rvar)


IRcountry_brmsS <- spread_rvars(IncomeRegion_BRMSModel, r_Income_Region[group1,term],r_Country[group,term],b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_incomeregion, by = join_by(group==Country,group1==Income_Region)) |>
  mutate(r_Country =  r_Country+ r_Income_Region+ b_year_orig) |>
  rename(rvar=r_Country, Country = group, Income_Region = group1) |>
  select(Country, Income_Region, Region, term, rvar)

IRcountry_brms <- rbind(IRcountry_brmsI, IRcountry_brmsS) 
```

#### Tidying the estimates from the model

```{r, fig.width=10, fig.height=8}
IR_BRMS_IS_EST <- brms_IncomeRegion |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

IRC_BRMS_IS_Est <- IRcountry_brms |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)
```

### Plotting the model fit on the data

#### Independent country model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  facet_wrap(~Country)+
  geom_abline(data=CountryInd_brmsIS_Est, aes(slope=year_orig, intercept= Intercept), color="black")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Independent country model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

#### Country model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  facet_wrap(~Country)+
  geom_abline(data=Country_brmsIS_Est, aes(slope=year_orig, intercept= Intercept), color="magenta3")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Country model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

#### Region model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_nested_wrap(vars(Region, Country), nrow = 5)+
  geom_abline(data= RcountryBRMS_IS_Est, aes(slope=year_orig, intercept= Intercept), color="blue3")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Region model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

#### Income model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_nested_wrap(vars(Income, Country), nrow = 5)+
  geom_abline(data=Income_BRMS_IS_Est, aes(slope=year_orig, intercept= Intercept), color="red3")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Income model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

#### IncomeRegion model fit on the data

```{r}
ggplot(Pisa_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_nested_wrap(vars(Income_Region, Country), nrow = 5)+
  geom_abline(data=IRC_BRMS_IS_Est, aes(slope=year_orig, intercept= Intercept), color="red3")+
  scale_x_continuous(labels = function(x) {x+2000}, breaks = seq(0,18,3))+
  xlab("year")+ ggtitle("Income model fit on the data")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
```

