---
title: "Exploratory data analysis section of the manuscript"
author: "Oluwayomi Akinfenwa"
date: "06/10/2023"
output:
  pdf_document:
    toc: yes
    toc_depth: '4'
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(lme4)
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
library(bayesplot)
library(patchwork)
library(ggragged)
```

Loading the two R.data containing the learning-tower data set and the processed data with Region and Income classification.

```{r loading the data}
load(here::here("SavedData", "pisam.Rdata"))
```

**We have 406 observations and for this analysis, we decided to examine European countries**

### Filtering European countries alone

```{r Europe}
Pisa_Europe_Data <- Pisa_Data |> filter(Continent == "Europe") |> arrange(Country)
```

**For the European countries, we have 230 observations from 40 countries.**

### Visualising the data

```{r}
# Joining the Income and Region together to form one new column
Pisa_Europe_Data <- unite(Pisa_Europe_Data, col = "Income_Region", c("Income", "Region"), sep = "_", remove = FALSE)

#Creating the grid for the prediction
country_names <- levels(factor(Pisa_Europe_Data$Country))
region_names <- levels(factor(Pisa_Europe_Data$Region))
income_names <- levels(factor(Pisa_Europe_Data$Income))
incomeregion_names <- levels(factor(Pisa_Europe_Data$Income_Region))

## Obtaining the index for the data
mu_index <- 1:nrow(Pisa_Europe_Data)

## Obtaining the region indexes

country_region <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- Pisa_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         

pred_grid <- Pisa_Europe_Data |> 
  modelr::data_grid(Country, year_orig) |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region)))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))

```

### Exploratory data analysis

Question

Can we fit a linear regression model using lm fit and use the estimates to create this plot.

### An independent linear regression fit

```{r}
Country_model <- lmer(math~ year_orig+(1+year_orig|Country), data = Pisa_Europe_Data)

Country_Model_IS <- coef(Country_model)$Country
Country_Model_IS$Country <- rownames(Country_Model_IS)
Country_Model_IS <- Country_Model_IS |>
  rename("slope" = "year_orig") |>
  mutate(slopesign = sign(slope)) |>
  left_join(Country_region, join_by(Country)) |>
  select(-c(Country_num, region_num)) |>
  arrange(slope)
```

#### The chosen plots

```{r}
##Merging the slope-sign with the Pisa data so that i can rearrange by the both country and slope-sign

Slopesign <- Country_Model_IS |>
  select(Country, slope)

Pisa_Europe_Data1 <- Pisa_Europe_Data |>
  left_join(Slopesign, join_by(Country))

Pisa_Europe_Data1$facet <- factor(Pisa_Europe_Data1$Region, 
                  levels = c("Western Europe", "Eastern Europe", "Northern Europe", "Southern Europe"))

Country_Model_IS$facet <- factor(Country_Model_IS$Region, 
                  levels = c("Western Europe", "Eastern Europe", "Northern Europe", "Southern Europe"))

color_flag <- c("lightseagreen", "darkolivegreen3", "indianred", "cyan1")

slope_color <- c("-1" ="magenta2", "1"= "blue2")


## In ascending slope

pdf("ascending.pdf",
    width = 11,
    height = 8)

ggplot(data = Pisa_Europe_Data1,
         aes(x=year_orig, y=math))+
  geom_point(aes(fill = Region), size = 1.5, shape = 21)+
   geom_abline(data=Country_Model_IS, 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  facet_ragged_rows(vars(facet), vars(reorder(Country, slope)),scales = "free_y",
                    switch = "y", labeller=label_wrap_gen(width=6))+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  scale_y_continuous(position = "right")+
   labs(x= " ", y = " ",  color = "Slope") +
  scale_fill_manual(values = color_flag)+
  scale_color_manual(values = slope_color, labels = c("negative", "positive"))+
  theme(legend.position = "bottom",
        plot.subtitle = element_text(family = "Serif"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, face = "bold"),strip.text.x = element_text(size = 9,face = "bold"),
        axis.text.y = element_text(size = 9,face = "bold"))

dev.off()
```


### INCOME-GROUPING

```{r}
## Coloring by region
pdf("income1.pdf",
    width = 12,
    height = 8)
middle_income <- ggplot(data = filter(Pisa_Europe_Data1, Income== "Middle Income"),
         aes(x=year_orig, y=math))+
  geom_point(aes(fill = Region), size = 1.5, shape = 21)+
   geom_abline(data= filter(Country_Model_IS, Income== "Middle Income"), 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  ggh4x::facet_wrap2(vars(Income, reorder(Country, slope)), ncol = 10,
  strip = ggh4x::strip_nested(bleed = TRUE))+
  labs(x = " ", y = " ") + 
  scale_fill_manual(values = color_flag)+
  scale_color_manual(values = slope_color, labels = c("negative", "positive"))+
  scale_y_continuous(position = "right",breaks = seq(350,490, 40))+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  theme(legend.position = "none", strip.text.x = element_text(size = 7.8,face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

high_income <- ggplot(data = filter(Pisa_Europe_Data1, Income== "High Income"),
         aes(x=year_orig, y=math))+
  geom_point(aes(fill = Region), size = 1.5, shape = 21)+
   geom_abline(data= filter(Country_Model_IS, Income== "High Income"), 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  scale_y_continuous(position = "right")+
  ggh4x::facet_wrap2(vars(Income, reorder(Country, slope)), ncol = 10, 
                     strip = ggh4x::strip_nested(bleed = TRUE))+
  scale_fill_manual(values = color_flag)+
  scale_color_manual(values = slope_color, labels = c("negative", "positive"))+
  labs(x = " ", y = " ") +
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  theme(legend.position = "none", strip.text.x = element_text(size = 7.8,face = "bold"),
        axis.text.x = element_blank())

high_income/middle_income +
  plot_layout(widths = 1, heights = c(3, 1))
dev.off()
```

```{r}
pdf("income2.pdf",
    width = 12,
    height = 8)
middle_income <- ggplot(data = filter(Pisa_Europe_Data1, Income== "Middle Income"),
         aes(x=year_orig, y=math))+
  geom_point(aes(fill = Income), size = 1.5, shape = 21)+
   geom_abline(data= filter(Country_Model_IS, Income== "Middle Income"), 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  ggh4x::facet_wrap2(vars(Income, reorder(Country, slope)), ncol = 10,
  strip = ggh4x::strip_nested(bleed = TRUE))+
  labs(x = " ", y = " ") + 
  scale_fill_manual(values = "lightseagreen")+
  scale_color_manual(values = slope_color, labels = c("negative", "positive"))+
  scale_y_continuous(position = "right",breaks = seq(350,490, 40))+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  theme(legend.position = "none", strip.text.x = element_text(size = 7.8,face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

high_income <- ggplot(data = filter(Pisa_Europe_Data1, Income== "High Income"),
         aes(x=year_orig, y=math))+
  geom_point(aes(fill = Income), size = 1.5, shape = 21)+
   geom_abline(data= filter(Country_Model_IS, Income== "High Income"), 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  scale_y_continuous(position = "right")+
  ggh4x::facet_wrap2(vars(Income, reorder(Country, slope)), ncol = 10, 
                     strip = ggh4x::strip_nested(bleed = TRUE))+
  scale_fill_manual(values = "sienna3")+
  scale_color_manual(values = slope_color, labels = c("negative", "positive"))+
  labs(x = " ", y = " ") +
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  theme(legend.position = "none", strip.text.x = element_text(size = 7.8,face = "bold"),
        axis.text.x = element_blank())

high_income/middle_income +
  plot_layout(widths = 1, heights = c(3, 1))

dev.off()
```
