---
title: "The Independent model, Bayesian hierarchical models for Country-specific, Region, Income and Income-Region"
author: "Oluwayomi Akinfenwa"
date: "09/02/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(tidybayes)
library(dplyr)
library(tidyr)
library(brms)
```

Loading the Rdata containing the PISA data for the European countries. This data is saved as Europe_Pisamaths.Rdata in the folder named PISA_Data.

```{r loading the data}
load(here::here("PISA_Data", "Europe_Pisamaths.Rdata"))

#Filtering the data for 2022 since we have decided to make predictions with the models for year 2022.
PISA_Europe_Data <- Pisa_Europe_Data |>
  filter(year != "2022")
```

**We have 202 observations for this analysis**

**We have decided to use BRMS for this analysis and include the JAGS Model as appendix**

## Setting the model specification in BRMS

### Writing BRMS model for country-level specifications

#### Specifying the models in BRMS

BRMS Stuffs

```{r}
#library(cmdstanr)
options(mc.cores = 4
    #brms.backend = "cmdstanr"
)

bayes_seed <-1234
```

Creating a folder to store all the plots

```{r, libraries, include = FALSE}
if (!dir.exists(here::here("Manuscript_Models")))
  dir.create(here::here("Manuscript_Models"))
```

#### Independent model with gloabl mean as the slope.

```{r}
if (file.exists(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))
  genBRMS <- FALSE
} else genBRMS <- TRUE

```

```{r, message=FALSE, eval= genBRMS}
#For the Independent linear model, we are interested in fitting a linear model omitting the countries with one data point.
#Hence, This model will be fitted excluding Belarus, Ukraine, and Bosnia& Herzergovina.
SCountry <- c("Belarus", "Bosnia& Herzegovina", "Ukraine")

SPISA_Europe_Data <- PISA_Europe_Data |>
  filter(!Country %in% SCountry)

Priors <- c(brms::prior(normal(500, 1000), class = Intercept),
            brms::prior(normal(0, 50), class = b),
            brms::prior(cauchy(30, 100), class = sigma))

CountryInd_BRMSModel <- brms::brm(
  brms::bf(math ~ (year_orig*Country)),
  data = SPISA_Europe_Data,
  iter = 12000, 
  prior = Priors,
  control = list(adapt_delta = 0.99, max_treedepth = 25),
  silent = 2, chains = 4, seed = bayes_seed)

save(CountryInd_BRMSModel, file=here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))
```

```{r}
if (file.exists(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))
  genBRMS <- FALSE
} else genBRMS <- TRUE

```

#### Country-specific model with a distribution on all the country.

```{r, message=FALSE, eval= genBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 5), class = b),
            brms::prior(cauchy(30, 10), class = sigma),
            brms::prior(cauchy(30, 10), class = sd, coef = Intercept, group=Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group=Country))


Country_BRMSModel <- brms::brm(
  brms::bf(math ~ year_orig + (1 + year_orig|Country)),
  data = PISA_Europe_Data,
  iter = 12000, 
  prior = Priors,
  control = list(adapt_delta = 0.93),
  chains = 4, seed = bayes_seed)

save(Country_BRMSModel, file=here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))
```

```{r}
if (file.exists(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))
  genBRMS <- FALSE
} else genBRMS <- TRUE

```

Running the brms model for region hierarchical model

```{r, message=FALSE, eval= genBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 5), class = b),
            brms::prior(cauchy(30, 10), class = sigma),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group= Region),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Region),
            brms::prior(cauchy(30, 10), class = sd, coef = Intercept, group= Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Country))


Region_BRMSModel <- brms::brm(
  brms::bf(math ~ year_orig + (1 + year_orig|Region)+ (1 + year_orig|Country)),
  data = PISA_Europe_Data,
  iter = 12000, 
  prior = Priors,
  control = list(adapt_delta = 0.99, max_treedepth = 20), silent=2,
  chains = 4, seed = bayes_seed)

save( Region_BRMSModel, file=here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))
```


```{r}
if (file.exists(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))
  GenBRMS <- FALSE
} else GenBRMS <- TRUE

```

Running the brms model for Income hierarchical model

```{r, message=FALSE, eval= GenBRMS}

Priors <-  c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 5), class = b),
            brms::prior(cauchy(30, 10), class = sigma),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group= Income),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Income),
            brms::prior(cauchy(30, 10), class = sd, coef = Intercept, group= Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Country))


Income_BRMSModel <- brms::brm(
  brms::bf(math ~ year_orig + (1 + year_orig|Income)+ (1 + year_orig|Country)),
  data = PISA_Europe_Data,
  iter = 12000, 
  prior = Priors,
  control = list(adapt_delta = 0.997, max_treedepth = 20), silent=2,
  chains = 4, seed = bayes_seed)

save( Income_BRMSModel, file=here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))
```

```{r}
if (file.exists(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
  GenBRMS <- FALSE
} else GenBRMS <- TRUE

```

Running the brms model for Income hierarchical model

```{r, message=FALSE, eval= GenBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 5), class = b),
            brms::prior(cauchy(30, 10), class = sigma),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group= Income_Region),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Income_Region),
            brms::prior(cauchy(30, 10), class = sd, coef = Intercept, group= Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Country))


IncomeRegion_BRMSModel <- brms::brm(
  brms::bf(math ~ year_orig + (1 + year_orig|Income_Region)+ (1 + year_orig|Country)),
  data = PISA_Europe_Data,
  iter = 12000, 
  prior = Priors,
  control = list(adapt_delta = 0.999, max_treedepth = 15), silent=2,
  chains = 4, seed = bayes_seed)

save( IncomeRegion_BRMSModel, file=here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```

#### Model comparison tests

```{r}
fit1 <- add_criterion(CountryInd_BRMSModel, "loo")

fit2 <- add_criterion(Country_BRMSModel, "loo")

fit3 <- add_criterion(Region_BRMSModel, "loo")

fit4 <- add_criterion(Income_BRMSModel, "loo")

fit5 <- add_criterion(IncomeRegion_BRMSModel, "loo")


#Comparing all the models
loo_compare(fit2, fit3, fit4, fit5, criterion = "loo")
```
The results above shows that model 1 (the independent linear model is the worse model), followed by the model 3(Region hierarchical model) and the best are the Country-specific model, the Income-Region model.

One of the advantages of the our proposed visualisation approach is its ability for model comparison and selection. Based on our visual, we choose fit 5 (the incomeregion hierarchical model as the best model).