---
title: "The Bayesian hierarchical models for Region, Income and Income-Region"
author: "Oluwayomi Akinfenwa"
date: "09/02/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
library(brms)
```

Loading the two Rdata containing the PISA data for the European countries. This data is saved as Europe_Pisamaths.Rdata in the folder called PISA_Data.

```{r loading the data}
load(here::here("PISA_Data", "Europe_Pisamaths.Rdata"))

#Filtering the data for 2022 since we have decided to make predictions with the models for year 2022.
PISA_Europe_Data <- Pisa_Europe_Data |>
  filter(year != "2022")
```

**We have 202 observations for this analysis**

### Creating the index for the variables in the data set.

```{r}
#Creating the indexes for the hierarchical variables.
country_names <- levels(factor(PISA_Europe_Data$Country))
region_names <- levels(factor(PISA_Europe_Data$Region))
income_names <- levels(factor(PISA_Europe_Data$Income))
incomeregion_names <- levels(factor(PISA_Europe_Data$Income_Region))

## Obtaining the region indexes

country_region <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         
INCOME_REGION <- REGION |>
  left_join(INCOME, join_by(Country))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> left_join(INCOME_REGION, join_by(Country))
```

**We have decided to use BRMS for this analysis and include the JAGS Model as appendix**

## Setting the model specification in BRMS

### Writing BRMS model for country-level specifications


### Specifying the models in BRMS

## BRMS Model

BRMS Stuffs

```{r}
#library(cmdstanr)
options(mc.cores = 4
    #brms.backend = "cmdstanr"
)

bayes_seed <-1234
```

#### Independent model with gloabl mean as the slope.

```{r}
if (file.exists(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))
  genBRMS <- FALSE
} else genBRMS <- TRUE

```

```{r, message=FALSE, eval= genBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 10), class = sigma))


CountryInd_BRMSModel <- brms::brm(
  brms::bf(math ~ (year_orig*Country)),
  data = PISA_Europe_Data,
  iter = 8000, 
  prior = Priors,
  control = list(adapt_delta = 0.93),
  chains = 4, seed = bayes_seed)

save(CountryInd_BRMSModel, file=here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))
```

```{r}
if (file.exists(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))
  genBRMS <- FALSE
} else genBRMS <- TRUE

```

#### Country-specific model with a distribution on all the country.

```{r, message=FALSE, eval= genBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 10), class = sigma),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group=Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group=Country))


Country_BRMSModel <- brms::brm(
  brms::bf(math ~ year_orig + (1 + year_orig||Country)),
  data = PISA_Europe_Data,
  iter = 8000, 
  prior = Priors,
  control = list(adapt_delta = 0.93),
  chains = 4, seed = bayes_seed)

save(Country_BRMSModel, file=here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))
```

```{r}
if (file.exists(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))
  genBRMS <- FALSE
} else genBRMS <- TRUE

```

Running the brms model for region hierarchical model

```{r, message=FALSE, eval= genBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 10), class = sigma),
            brms::prior(cauchy(0, 2), class = sd, coef = Intercept, group= Region),
            brms::prior(cauchy(0, 1), class = sd, coef = year_orig, group= Region),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group= Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Country))


Region_BRMSModel <- brms::brm(
  brms::bf(math ~ year_orig + (1 + year_orig||Region)+ (1 + year_orig||Country)),
  data = PISA_Europe_Data,
  iter = 10000, 
  prior = Priors,
  control = list(adapt_delta = 0.99), silent=2,
  chains = 4, seed = bayes_seed)

save( Region_BRMSModel, file=here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))
```


```{r}
if (file.exists(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))
  GenBRMS <- FALSE
} else GenBRMS <- TRUE

```

Running the brms model for Income hierarchical model

```{r, message=FALSE, eval= GenBRMS}

Priors <-  c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 5), class = sigma),
            brms::prior(cauchy(0, 2), class = sd, coef = Intercept, group= Income),
            brms::prior(cauchy(0, 1), class = sd, coef = year_orig, group= Income),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group= Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Country))


Income_BRMSModel <- brms::brm(
  brms::bf(math ~ year_orig + (1 + year_orig||Income)+ (1 + year_orig||Country)),
  data = PISA_Europe_Data,
  iter = 16000, 
  prior = Priors,
  control = list(adapt_delta = 0.995), silent=2,
  chains = 4, seed = bayes_seed)

save( Income_BRMSModel, file=here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))
```

```{r}
if (file.exists(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
  GenBRMS <- FALSE
} else GenBRMS <- TRUE

```

Running the brms model for Income hierarchical model

```{r, message=FALSE, eval= GenBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 10), class = sigma),
            brms::prior(cauchy(0, 2), class = sd, coef = Intercept, group= Income_Region),
            brms::prior(cauchy(0, 1), class = sd, coef = year_orig, group= Income_Region),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group= Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Country))


IncomeRegion_BRMSModel <- brms::brm(
  brms::bf(math ~ year_orig + (1 + year_orig||Income_Region)+ (1 + year_orig||Country)),
  data = PISA_Europe_Data,
  iter = 6000, 
  prior = Priors,
  control = list(adapt_delta = 0.93), silent=2,
  chains = 4, seed = bayes_seed)

save( IncomeRegion_BRMSModel, file=here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```
