---
title: "JAGS Model estimates"
author: "Oluwayomi Akinfenwa"
date: "08/03/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
library(bayesplot)
library(patchwork)
library(ggragged)
library(geofacet)
```

Loading the PISA data for the European countries Europe_Pisamaths.Rdata.
```{r loading the data}
load(here::here("PISA_Data", "Europe_Pisamaths.Rdata"))

#Filtering the data for 2022 since we have decided to make predictions with the models for year 2022.
PISA_Europe_Data <- Pisa_Europe_Data |>
  filter(year != "2022")
```

**We have 202 observations for this analysis**

### Creating the index for the variables in the data set.

```{r}
#Creating the indexes for the hierarchical variables.
country_names <- levels(factor(PISA_Europe_Data$Country))
region_names <- levels(factor(PISA_Europe_Data$Region))
income_names <- levels(factor(PISA_Europe_Data$Income))
incomeregion_names <- levels(factor(PISA_Europe_Data$Income_Region))

## Obtaining the region indexes

country_region <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         
INCOME_REGION <- REGION |>
  left_join(INCOME, join_by(Country))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> left_join(INCOME_REGION, join_by(Country))

# Specifying the base_year as 2018.
base_year <- 2018

## Creating the pred_grid.
pred_grid <- PISA_Europe_Data |>
  modelr::data_grid(Country,year) |>
  mutate(year_orig = year - base_year) |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region)))
```

## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "CountryInd_JAGSModel.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_JAGSModel.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_JAGSModel.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_JAGSModel.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_JAGSModel.Rdata"))
```

### Results

#### Estimates from the independent-country-specific model

```{r}
#For the Independent linear model, we are interested in fitting a linear model omitting the countries with one data point.
#note that the country names will be different because of the SCountry we excluded in the model.
SCountry <- c("Belarus", "Bosnia& Herzegovina", "Ukraine")

SPISA_Europe_Data <- PISA_Europe_Data |>
  filter(!Country %in% SCountry)
Scountry_names <- levels(factor(SPISA_Europe_Data$Country))
CountryInd_ModelSample <- CountryInd_JAGSModel$BUGSoutput$sims.matrix

JAGS_CountryInd_I <- spread_rvars(CountryInd_ModelSample , alpha.j[Country_index]) |>
  mutate(Country = Scountry_names[Country_index]) |>
  right_join(Country_region, join_by(Country== Country))|>
  mutate(term="Intercept") |>
  select(Country,Region,Income, term,rvar=alpha.j)

JAGS_CountryInd_S <- spread_rvars(CountryInd_ModelSample, beta.j[Country_index]) |>
  mutate(Country = Scountry_names[Country_index]) |>
  right_join(Country_region, join_by(Country== Country))|>
  mutate(term="year_orig") |>
  select(Country,Region,Income, term,rvar=beta.j)

## Tidying the estimates
JAGS_CountryInd_IS <- rbind(JAGS_CountryInd_I, JAGS_CountryInd_S)

JAGS_CountryInd_ISEst <- JAGS_CountryInd_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)


## Credible interval
## Intercept Estimates
JAGS_CountryInd_Int_Est <- JAGS_CountryInd_I |>
  mutate(Model = "Independent \nModel")|>
  select(Country, Model, rvar)

# Slope Estimates
JAGS_CountryInd_Slop_Est <- JAGS_CountryInd_S |>
  mutate(Model = "Independent \nModel")|>
  select(Country, Model, rvar)
```

#### Estimates from the country-specific model

```{r}
Country_ModelSample <- Country_JAGSModel$BUGSoutput$sims.matrix

JAGS_CountryI <- spread_rvars(Country_ModelSample , alpha.j[Country_index]) |>
  mutate(Country = country_names[Country_index], term="Intercept") |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region,Income, term,rvar=alpha.j)


JAGS_CountryS <- spread_rvars(Country_ModelSample , beta.j[Country_index]) |>
  mutate(Country = country_names[Country_index], term="year_orig") |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country,Region,Income, term,rvar=beta.j)

JAGS_CountryIS <- rbind(JAGS_CountryI, JAGS_CountryS)


JAGS_Country_IS_Est <- JAGS_CountryIS |> mutate(coef=median(rvar))|> 
  select(-rvar, Country)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
JAGS_Country_Int_Est <- JAGS_CountryI |> 
  mutate(Model = "Country \nModel")|>
  select(c(Country, Model,rvar))

## Slope Estimates
JAGS_Country_Slop_Est <- JAGS_CountryS |> 
  mutate(Model = "Country \nModel")|>
  select(c(Country, Model,rvar))

#The hierarchical estimate for the country-specific model is the b_intercept (global estimate)
country_mu_alpha <- spread_rvars(Country_ModelSample , mu_alpha)|> 
  rename(rvar = mu_alpha)

JAGS_Country_Int_est <- country_mu_alpha[rep (seq_len(nrow(country_mu_alpha)),
                              each = 40), ]  |>
  mutate(Country_index = 1:40) |>
  mutate(Country = country_names[Country_index], 
         Model = "Country \nModel") |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country, Model, rvar)
  
## Pulling the mu_beta from the country-specific model
country_mu_beta <- spread_rvars(Country_ModelSample , mu_beta)|> 
  rename(rvar = mu_beta)

JAGS_Country_Slop_est <- country_mu_beta[rep (seq_len(nrow(country_mu_beta)),
                              each = 40), ]  |>
  mutate(Country_index = 1:40) |>
  mutate(Country = country_names[Country_index], 
         Model = "Country \nModel") |>
  left_join(Country_region, join_by(Country== Country))|>
  select(Country, Model, rvar)
```

### Estimates from the region hierarchical model

```{r}
Region_ModelSamples <- Region_JAGSModel$BUGSoutput$sims.matrix
# get_variables(Region_ModelSamples)

## Hierarchical estimates
JAGS_Region_Int <- spread_rvars(Region_ModelSamples , mu_alpha.r[region_num]) |>
  mutate(Region = region_names[region_num], term = "Intercept") |>
  right_join(Country_region, by = join_by(Region==Region))|>
  rename(rvar =mu_alpha.r) |>
  select(Country,Region, Income, term, rvar)

JAGS_Region_Slop <- spread_rvars(Region_ModelSamples , mu_beta.r[region_num]) |>
  mutate(Region = region_names[region_num], term = "year_orig") |>
  right_join(Country_region, by = join_by(Region==Region))|>
  rename(rvar =mu_beta.r) |>
  select(Country,Region, Income, term, rvar)

JAGS_Region_IS <- rbind(JAGS_Region_Int, JAGS_Region_Slop)

## The region country estimates
JAGS_Rcountry_Int <- spread_rvars(Region_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(Country_region, by = join_by(Country==Country))|>
  rename(rvar =alpha.j,Country = Country) |>
  select(Country, Region,Income, term,rvar)


JAGS_Rcountry_Slop <- spread_rvars(Region_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(Country_region, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country = Country) |>
  select(Country, Region,Income, term,rvar)

JAGS_Rcountry_IS <- rbind(JAGS_Rcountry_Int, JAGS_Rcountry_Slop) 
```

### Tidying the estimates from the Region hierarchical model

```{r, fig.width=10, fig.height=8}
#median estimates
JAGS_Region_IS_Est <- JAGS_Region_IS |> mutate(coef=median(rvar))|> 
  pivot_wider(values_from=coef, names_from=term)

JAGS_Rcountry_IS_Est <- JAGS_Rcountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
JAGS_Region_Int_est <- JAGS_Region_Int |>
  mutate(Model = "Region \nModel")|>
  select(Country, Model, rvar)

#Country estimates
JAGS_Region_Int_Est <- JAGS_Rcountry_Int |>
  mutate(Model = "Region \nModel")|>
  select(Country, Model, rvar)

## Slope Estimates
#Hierarchy estimates
JAGS_Region_Slop_est <- JAGS_Region_Slop |> 
  mutate(Model = "Region \nModel")|>
  select(Country, Model, rvar)

#Country estimates
JAGS_Region_Slop_Est <- JAGS_Rcountry_Slop |> 
  mutate(Model = "Region \nModel")|>
  select(Country,Model, rvar)
```

### Estimates from the income hierarchical model

```{r}
Income_ModelSamples <- Income_JAGSModel$BUGSoutput$sims.matrix
# get_variables(Income_ModelSamples)
JAGS_Income_Int <- spread_rvars(Income_ModelSamples , mu_alpha.I[income_num]) |>
  mutate(Income = income_names[income_num], term = "Intercept") |>
  right_join(Country_income, by = join_by(Income==Income))|>
  rename(rvar =mu_alpha.I) |>
  select(Country,Region, Income, term,rvar)

JAGS_Income_Slop <- spread_rvars(Income_ModelSamples , mu_beta.I[income_num]) |>
  mutate(Income = income_names[income_num], term = "year_orig") |>
  right_join(Country_income, by = join_by(Income==Income))|>
  rename(rvar =mu_beta.I) |>
  select(Country,Region, Income, term,rvar)

JAGS_Income_IS <- rbind(JAGS_Income_Int, JAGS_Income_Slop)

## The income country estimates
JAGS_Icountry_Int <- spread_rvars(Income_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(Country_income, by = join_by(Country==Country))|>
  rename(rvar =alpha.j, Country=Country) |>
  select(Country,Region, Income,Region, term,rvar)

JAGS_Icountry_Slop <- spread_rvars(Income_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(Country_income, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country=Country) |>
  select(Country,Region, Income,Region, term,rvar)

JAGS_Icountry_IS <- rbind(JAGS_Icountry_Int, JAGS_Icountry_Slop) 
```

#### Tidying the estimates from the model

```{r}
JAGS_Income_IS_EST <- JAGS_Income_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

JAGS_Icountry_IS_Est <- JAGS_Icountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
JAGS_Income_Int_est <- JAGS_Income_Int |> 
  mutate(Model = "Income \nModel")|>
  select(Country, Model, rvar)
#Country estimates
JAGS_Income_Int_Est <- JAGS_Icountry_Int |>
  mutate(Model = "Income \nModel")|>
  select(Country, Model, rvar)

## Slope Estimates
#Hierarchy estimates
JAGS_Income_Slop_est <- JAGS_Income_Slop |>
  mutate(Model = "Income \nModel")|>
  select(Country, Model, rvar)
#Country estimates
JAGS_Income_Slop_Est <- JAGS_Icountry_Slop |>
  mutate(Model = "Income \n Model")|>
  select(Country, Model, rvar)
```

### Estimates from the incomeregion hierarchical model

```{r}
IR_ModelSamples <- IR_JAGSModel$BUGSoutput$sims.matrix
# get_variables(IR_ModelSamples)
JAGS_IncomeRegion_Int <- spread_rvars(IR_ModelSamples , mu_alpha.IR[income_num]) |>
  mutate(Income_Region = incomeregion_names[income_num], term = "Intercept") |>
  right_join(Country_incomeregion, by = join_by(Income_Region ==Income_Region ))|>
  rename(rvar =mu_alpha.IR) |>
  select(Country,Region,Income,Income_Region,term,rvar)

JAGS_IncomeRegion_Slop <- spread_rvars(IR_ModelSamples , mu_beta.IR[income_num]) |>
  mutate(Income_Region  = incomeregion_names[income_num], term = "year_orig") |>
  right_join(Country_incomeregion, by = join_by(Income_Region ==Income_Region ))|>
  rename(rvar =mu_beta.IR) |>
  select(Country,Region,Income,Income_Region,term,rvar)

JAGS_IncomeRegion_IS <- rbind(JAGS_IncomeRegion_Int, JAGS_IncomeRegion_Slop)

## The income country estimates
JAGS_IRcountry_Int <- spread_rvars(IR_ModelSamples , alpha.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "Intercept") |>
  right_join(Country_incomeregion, by = join_by(Country==Country))|>
  rename(rvar =alpha.j, Country=Country) |>
  select(Country,Region, Income, Income_Region, term,rvar)


JAGS_IRcountry_Slop <- spread_rvars(IR_ModelSamples , beta.j[country_num]) |>
  mutate(Country = country_names[country_num], term = "year_orig") |>
  right_join(Country_incomeregion, by = join_by(Country==Country))|>
  rename(rvar =beta.j,Country=Country) |>
  select(Country,Region,Income, Income_Region, term,rvar)

JAGS_IRcountry_IS <- rbind(JAGS_IRcountry_Int, JAGS_IRcountry_Slop) 
```

#### The median and credible interval estimates for the IncomeRegion model

```{r}
## Median
JAGS_IR_IS_EST <- JAGS_IncomeRegion_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

JAGS_IRcountry_IS_Est <- JAGS_IRcountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
JAGS_IncomeRegion_Int_est <- JAGS_IncomeRegion_Int |> 
  mutate(Model = "Income-Region \nModel")|>
  select(Country, Model,rvar)
#Country estimates
JAGS_Income_Region_Int_Est <- JAGS_IRcountry_Int |> 
  mutate(Model = "Income-Region \nModel")|>
  select(Country, Model,rvar)
## Slope Estimates
#Hierarchy estimates
JAGS_IncomeRegion_slop_est <- JAGS_IncomeRegion_Slop |> 
  mutate(Model = "Income-Region \nModel")|>
  select(Country, Model,rvar)
#Country estimates
JAGS_Income_Region_Slop_Est <- JAGS_IRcountry_Slop |>
  mutate(Model = "Income-Region \nModel")|>
  select(Country, Model,rvar)
```

### Plotting the model fit on the data

```{r}
if (!dir.exists(here::here("Saved_Plots/Regression_fits")))
 dir.create(here::here("Saved_Plots/Regression_fits"))
```

#### Independent country model fit on the data

```{r}

pdf("Saved_Plots/Regression_fits/JAGS_independent_fit.pdf",
    width = 12,
    height = 9)
ggplot(PISA_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  facet_wrap(~Country, nrow = 5)+
  geom_abline(data= JAGS_CountryInd_ISEst, aes(slope=year_orig, intercept= Intercept), color="green4")+
  scale_x_continuous(breaks = seq(-15,0,3),labels = function(x) x+2018)+
  xlab("year")+ ggtitle("Independent country model fit of average maths scores over time")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
dev.off()
```

#### Country model fit on the data

```{r}
pdf("Saved_Plots/Regression_fits/JAGS_country-specific_fit.pdf",
    width = 12,
    height = 9)
ggplot(PISA_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  facet_wrap(~Country, nrow = 5)+
  geom_abline(data=JAGS_Country_IS_Est, aes(slope=year_orig, intercept= Intercept), color="magenta4")+
  scale_x_continuous(breaks = seq(-15,0,3),labels = function(x) x+2018)+
  xlab("year")+ ggtitle("Country-specific model fit of average maths scores over time")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
dev.off()
```

#### Region model fit on the data

```{r}
pdf("Saved_Plots/Regression_fits/JAGS_region_model_fit.pdf",
    width = 12,
    height = 9)

ggplot(PISA_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_nested_wrap(vars(Region, Country), nrow = 5)+
  geom_abline(data= JAGS_Rcountry_IS_Est, aes(slope=year_orig, intercept= Intercept), color="blue3")+
  scale_x_continuous(breaks = seq(-15,0,3),labels = function(x) x+2018)+
  xlab("year")+ ggtitle("Region hierarchical model fit of average maths scores over time")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
dev.off()
```

#### Income model fit on the data

```{r}
pdf("Saved_Plots/Regression_fits/JAGS_income_model_fit.pdf",
    width = 12,
    height = 9) 

ggplot(PISA_Europe_Data, aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_nested_wrap(vars(Income, Country), nrow = 5)+
  geom_abline(data= JAGS_Icountry_IS_Est, aes(slope=year_orig, intercept= Intercept), color="red4")+
  scale_x_continuous(breaks = seq(-15,0,3),labels = function(x) x+2018)+
  xlab("year")+ ggtitle("Income hierarchical model fit of average maths scores over time")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))
dev.off()
```