---
title: "Visuals to compare the model estimates"
author: "Oluwayomi Akinfenwa"
date: "29/02/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(stringr)
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(brms)
library(bayesplot)
library(patchwork)
library(ggragged)
library(geofacet)
library(grid)
```

Loading the PISA data for the European countries - Europe_Pisamaths.Rdata.

```{r loading the data}
load(here::here("PISA_Data", "Europe_Pisamaths.Rdata"))

# We have decided to remove year 2022 from my data and make prediction for 2022.
# Hence i will filter year = 2022.
PISA_Europe_Data <- Pisa_Europe_Data |>
  filter(year != "2022")
```

### Creating the grid for the prediction

```{r}
country_names <- levels(factor(PISA_Europe_Data$Country))
region_names <- levels(factor(PISA_Europe_Data$Region))
income_names <- levels(factor(PISA_Europe_Data$Income))
incomeregion_names <- levels(factor(PISA_Europe_Data$Income_Region))

## Obtaining the index for the data
mu_index <- 1:nrow(PISA_Europe_Data)

## Obtaining the region indexes
country_region <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes
country_income <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes
country_incomeregion <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))

INCOME_REGION <- REGION |>
  left_join(INCOME, join_by(Country))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> 
  left_join(INCOME_REGION, join_by(Country))
```

## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```

### Pulling the estimates from all the fitted models

#### Estimates from the independent-country-specific model

```{r}
#my observations
# the global estimates is the estimate for Albania. Albania is used as the base country.
# also Bosnia was messed up and unitedkingdom merged together.
#hence, the str_replace_all might not work to fix this and I have to fix this manually.

CountryInd_draws <-posterior::as_draws_rvars(CountryInd_BRMSModel, 
                variable = "^b_Country|^b_Intercept", regex = TRUE) |>
  purrr::map_dfr(as_tibble, .id = "name")|>
  mutate(rvar=value+value[1])

#Albania is used as the base country, hence the intercept estimate is the rvar for Albania.
CountryInd_draws$rvar[1] <- CountryInd_draws$value[1]
  
  CountryInd_I <- CountryInd_draws |>
  mutate(Country = stringr::str_replace_all(name, stringr::fixed("b_Country"), "")) |>
  mutate(Country = stringr::str_replace_all(Country, stringr::fixed("b_Intercept"), "Albania")) |>
  mutate(Country = stringr::str_replace_all(Country, stringr::fixed("UnitedKingdom"), "United Kingdom")) |>
  right_join(Country_region, join_by(Country== Country))|>
    mutate(term = "year_orig") |>
  select(Country,Region, Income, term, rvar)

#Slope estimates
CountrySlop_draws <- posterior::as_draws_rvars(CountryInd_BRMSModel, 
                    variable = "^b_year_orig",regex = TRUE) |>
  purrr::map_dfr(as_tibble, .id = "name")|>
  mutate(rvar=value+value[1])

#Albania is used as the base country, hence the intercept estimate is the rvar for Albania.
CountrySlop_draws$rvar[1] <- CountrySlop_draws$value[1]

CountryInd_S <- CountrySlop_draws |>
  mutate(Country = stringr::str_replace_all(name, stringr::fixed("b_year_orig:Country"), "")) |>
  mutate(Country = stringr::str_replace_all(Country, stringr::fixed("b_year_orig"), "Albania")) |>
  mutate(Country = stringr::str_replace_all(Country, stringr::fixed("UnitedKingdom"), "United Kingdom")) |>
  right_join(Country_region, join_by(Country== Country))|>
  mutate(term = "year_orig") |>
  select(Country,Region, Income, term, rvar)

## Tidying the results
CountryInd_Int <- CountryInd_I |> mutate(Intercept= median(rvar)) |>
  select(Country, Region, Intercept)
CountryInd_Slop <- CountryInd_S |> mutate(year_orig= median(rvar)) |>
  select(Country, Region, year_orig)

CountryInd_IS_Est <- CountryInd_Int |>
  left_join(CountryInd_Slop, join_by(Country, Region))

CountryInd_Int_Est <- CountryInd_I |>
  mutate(Model = "Independent \nModel") |>
  select(Country, Model, rvar)

CountryInd_Slop_Est <- CountryInd_S|>
  mutate(Model = "Independent \nModel") |>
  select(Country, Model, rvar)
```

#### Estimates from the country-specific model

```{r}
## Pulling the intercept results. The global intercept (b_Intercept) and the country offsets.
Country_I <- spread_rvars(Country_BRMSModel, r_Country[Country,term], b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(Country = stringr::str_replace_all(Country, fixed("."), " ")) |>
  mutate(r_Country = r_Country+ b_Intercept) |>
  rename(rvar=r_Country) |>
  left_join(Country_region, join_by(Country== Country))

Country_Int <- Country_I|>
  select(Country,Region, term, rvar)

## Pulling the slope results. The global slope (b_year_orig) and the country offsets.
Country_S <- spread_rvars(Country_BRMSModel, r_Country[Country,term], b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(Country = stringr::str_replace_all(Country, fixed("."), " ")) |>
  mutate(r_Country = r_Country+ b_year_orig) |>
   rename(rvar=r_Country) |>
  left_join(Country_region, join_by(Country== Country))

Country_Slop <- Country_S|>
  select(Country,Region, term, rvar)

## Tidying the estimates
Country_IS <- rbind(Country_Int, Country_Slop)

Country_IS_Est <- Country_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Intercept Estimates
Country_Int_Est <- Country_I |>
  mutate(Model = "Country \nModel") |>
  select(c(Country, Model, rvar))

## Slope Estimates
Country_Slop_Est <- Country_S |>
  mutate(Model = "Country \nModel") |>
  select(c(Country,Model, rvar))

#The hierarchical estimate for the country-specific model is the b_intercept (global estimate)
Country_Int_est <- Country_I |>
  mutate(Model = "Country \nModel") |>
  select(c(Country, Model,rvar = b_Intercept))

Country_Slop_est <- Country_S |>
  mutate(Model = "Country \nModel") |>
  select(c(Country, Model,rvar= b_year_orig))
```

#### Estimates from the Region hierarchical model

```{r}
Region_int <- spread_rvars(Region_BRMSModel, r_Region[group1,term], b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Region = r_Region+ b_Intercept) |>
  rename(rvar=r_Region, Region = group1) |>
  select(Region, term, rvar)

Region_slop <- spread_rvars(Region_BRMSModel, r_Region[group1,term], b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Region = r_Region+  b_year_orig) |>
  rename(rvar=r_Region, Region = group1)|>
  select(Region, term, rvar)

Region_is <- rbind(Region_int,Region_slop) 

#Extending the estimates across all the countries

Region_Int <- Region_int |> 
  right_join(Country_region, by = join_by(Region == Region)) |>
  select(Country,Region, Income, term, rvar)

Region_Slop <- Region_slop |> 
  right_join(Country_region, by = join_by(Region == Region)) |>
  select(Country,Region, Income, term, rvar)

Region_IS <- rbind(Region_Int, Region_Slop)
  
## The region country estimates

Rcountry_Int <- spread_rvars(Region_BRMSModel, r_Region[group1,term],r_Country[group,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_region, by = join_by(group==Country,group1==Region)) |> #this join everything from the country_region with its intercession from the model result
  mutate(r_Country =  r_Country+ r_Region+ b_Intercept) |>
  rename(rvar=r_Country,Region=group1, Country =group) |>
  select(Country,Region, Income, term, rvar)

Rcountry_Slop <- spread_rvars(Region_BRMSModel, r_Region[group1,term],r_Country[group,term],b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_region, by = join_by(group==Country,group1==Region)) |>
  mutate(r_Country =  r_Country+ r_Region+ b_year_orig) |>
  rename(rvar=r_Country,Region=group1, Country =group) |>
  select(Country,Region, Income, term, rvar)

Rcountry_IS <- rbind(Rcountry_Int, Rcountry_Slop) 
```

### Tidying the estimates from the Region hierarchical model

```{r}
#median estimates
Region_IS_Est <- Region_IS |> mutate(coef=median(rvar))|>
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

Rcountry_IS_Est <- Rcountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
Region_Int_est <- Region_Int |>
  mutate(Model = "Region \nModel")|>
  select(Country, Model,rvar)
#Country estimates
Region_Int_Est <- Rcountry_Int |> 
  mutate(Model = "Region \nModel")|>
  select(c(Country,Model,rvar))
## Slope Estimates
#Hierarchy estimates
Region_Slop_est <- Region_Slop |>
  mutate(Model = "Region \nModel")|>
  select(c(Country,Model,rvar))
#Country estimates
Region_Slop_Est <- Rcountry_Slop |> 
  mutate(Model = "Region \nModel")|>
  select(Country, Model,rvar)
```

#### Estimates from the income hierarchical model

```{r}
Income_int <- spread_rvars(Income_BRMSModel, r_Income[group1,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Income = r_Income+ b_Intercept) |>
  rename(rvar=r_Income, Income= group1) |>
  select(Income, term, rvar)

Income_slop <- spread_rvars(Income_BRMSModel, r_Income[group1,term], b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Income = r_Income+  b_year_orig) |>
  rename(rvar=r_Income, Income= group1)|>
  select(Income, term, rvar)
Income_is <- rbind(Income_int, Income_slop)

#Extending the income hierarchical estimates across the countries.
Income_Int <- Income_int |>
  right_join(Country_income, by = join_by(Income ==Income))|>
  select(Country, Region, Income, term, rvar)

Income_Slop <- Income_slop |>
  right_join(Country_income, by = join_by(Income ==Income))|>
  select(Country, Region, Income, term, rvar)

Income_IS <- rbind(Income_Int, Income_Slop)
```

pulling the intercepts and slopes for each country based on the influence of the Income hierarchy

```{r}
Icountry_Int <- spread_rvars(Income_BRMSModel, r_Income[group1,term],r_Country[group,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_income, by = join_by(group==Country,group1==Income)) |> #this join everything from the country_Income with its intercession from the model result
  mutate(r_Country =  r_Country+ r_Income+ b_Intercept) |>
  rename(rvar=r_Country, Country = group, Income = group1) |>
  select(Country, Income,Region, term, rvar)


Icountry_Slop <- spread_rvars(Income_BRMSModel, r_Income[group1,term],r_Country[group,term],b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_income, by = join_by(group==Country,group1==Income)) |>
  mutate(r_Country =  r_Country+ r_Income+ b_year_orig) |>
  rename(rvar=r_Country, Country = group, Income = group1) |>
  select(Country, Income, Region, term, rvar)

Icountry_IS <- rbind(Icountry_Int, Icountry_Slop) 
```

#### Tidying the estimates from the income model

```{r, fig.width=10, fig.height=8}
#Hierarchical estimates
Income_IS_EST <- Income_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

#Country-estimates based on the hierarchical pulling.
Icountry_IS_Est <- Icountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
Income_Int_est <- Income_Int |> 
  mutate(Model = "Income \nModel")|>
  select(c(Country,Model,rvar))
#Country estimates
Income_Int_Est <- Icountry_Int |> 
  mutate(Model = "Income \nModel")|>
  select(Country, Model,rvar)
## Slope Estimates
#Hierarchy estimates
Income_Slop_est <- Income_Slop |> 
  mutate(Model = "Income \nModel")|>
  select(c(Country,Model,rvar))
#Country estimates
Income_Slop_Est <- Icountry_Slop |> 
  mutate(Model = "Income \nModel")|>
  select(Country, Model,rvar)
```

#### Estimates from the IncomeRegion hierarchical model

```{r}
IncomeRegion_int <- spread_rvars(IncomeRegion_BRMSModel, r_Income_Region[group1,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Income_Region = r_Income_Region+ b_Intercept) |>
  rename(rvar=r_Income_Region, `Income_Region` = group1) |>
  select(Income_Region, term, rvar)

IncomeRegion_slop <- spread_rvars(IncomeRegion_BRMSModel, r_Income_Region[group1,term], b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " ")) |>
  mutate(r_Income_Region = r_Income_Region+  b_year_orig) |>
  rename(rvar=r_Income_Region, `Income_Region` = group1) |>
  select(Income_Region, term, rvar)

IncomeRegion_is <- rbind(IncomeRegion_int, IncomeRegion_slop)

#Extending the income-region hierarchical estimates across the countries.
IncomeRegion_Int <- IncomeRegion_int |>
  right_join(Country_incomeregion, by = join_by(Income_Region ==Income_Region))|>
  select(Country, Income_Region, term, rvar)

IncomeRegion_Slop <- IncomeRegion_slop |>
  right_join(Country_incomeregion, by = join_by(Income_Region ==Income_Region))|>
  select(Country, Income_Region, term, rvar)


IncomeRegion_IS <- rbind(IncomeRegion_Int, IncomeRegion_Slop)
```

pulling the intercepts and slopes for each country based on the influence of the Income-Region hierarchy.

```{r}
IRcountry_Int <- spread_rvars(IncomeRegion_BRMSModel, r_Income_Region[group1,term],r_Country[group,term],b_Intercept) |>
  filter(term == "Intercept") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_incomeregion, by = join_by(group==Country,group1==Income_Region)) |> #this join everything from the country_Income with its intercession from the model result
  mutate(r_Country =  r_Country+ r_Income_Region+ b_Intercept) |>
  rename(rvar=r_Country, Country = group, Income_Region = group1) |>
  select(Country, Income_Region,Region, term, rvar)


IRcountry_Slop <- spread_rvars(IncomeRegion_BRMSModel, r_Income_Region[group1,term],r_Country[group,term],b_year_orig) |>
  filter(term == "year_orig") |>
  mutate(group1 = stringr::str_replace_all(group1, fixed("."), " "), 
         group = stringr::str_replace_all(group, fixed("."), " ")) |>
  right_join(Country_incomeregion, by = join_by(group==Country,group1==Income_Region)) |>
  mutate(r_Country =  r_Country+ r_Income_Region+ b_year_orig) |>
  rename(rvar=r_Country, Country = group, Income_Region = group1) |>
  select(Country, Income_Region, Region, term, rvar)

IRcountry_IS <- rbind(IRcountry_Int, IRcountry_Slop) 
```

#### Tidying the estimates from the model

```{r, fig.width=10, fig.height=8}
IR_IS_EST <- IncomeRegion_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

IRcountry_IS_Est <- IRcountry_IS |> mutate(coef=median(rvar))|> 
  select(-rvar)|>
  pivot_wider(values_from=coef, names_from=term)

## Credible interval
## Intercept Estimates
#Hierarchy estimates
IncomeRegion_Int_est <- IncomeRegion_Int |> 
  mutate(Model = "Income-Region \nModel")|>
  select(Country,Model,rvar)
#Country estimates
Income_Region_Int_Est <- IRcountry_Int |> 
  mutate(Model = "Income-Region \nModel")|>
  select(Country, Model,rvar)
## Slope Estimates
#Hierarchy estimates
IncomeRegion_Slop_est <- IncomeRegion_Slop |> 
  mutate(Model = "Income-Region \nModel")|>
  select(Country, Model,rvar)
#Country estimates
Income_Region_Slop_Est <- IRcountry_Slop |> 
  mutate(Model = "Income-Region \nModel")|>
  select(Country, Model,rvar)
```

A plot showing the model estimates and credible intervals (80% and 95%), facet by country and connecting the dots for the estimates from the 4 models (An independent model fits, Country-specific model and Region, Income, Income-Region hierarchical models).

```{r}
## Hierarchical estimates
##Intercepts
Combined_Int_estimates <- rbind(Country_Int_est,Region_Int_est, Income_Int_est,
                              IncomeRegion_Int_est) |>
  arrange(Country)

Combined_Slop_estimates <- rbind(Country_Slop_est,Region_Slop_est, Income_Slop_est,
                              IncomeRegion_Slop_est)|>
  arrange(Country)

Combined_Int_estimates$Model <- factor(Combined_Int_estimates$Model, 
                  levels = c("Country \nModel","Region \nModel", "Income \nModel", "Income-Region \nModel"))

Combined_Slop_estimates$Model <- factor(Combined_Slop_estimates$Model, 
                  levels = c("Country \nModel","Region \nModel", "Income \nModel", "Income-Region \nModel"))

## Countries estimates
Combined_Int_Estimates <- rbind(CountryInd_Int_Est,
                            Country_Int_Est,Region_Int_Est,
                            Income_Int_Est,Income_Region_Int_Est) |>
  arrange(Country)

Combined_Slop_Estimates <- rbind(CountryInd_Slop_Est,
                            Country_Slop_Est,Region_Slop_Est,
                            Income_Slop_Est,Income_Region_Slop_Est) |>
  arrange(Country)

Combined_Int_Estimates$Model <- factor(Combined_Int_Estimates$Model, 
                 levels = c("Independent \nModel","Country \nModel",
                             "Region \nModel", "Income \nModel",
                             "Income-Region \nModel"))

Combined_Slop_Estimates$Model <- factor(Combined_Slop_Estimates$Model, 
                  levels = c("Independent \nModel","Country \nModel",
                            "Region \nModel", "Income \nModel",
                             "Income-Region \nModel"))
```

```{r}
## Creating a grid for colors
Names <- country_region |>
  left_join(INCOME, join_by(Country == Country))

Region_color <- c("Eastern Europe" = "lightsteelblue2",
                  "Northern Europe"="lavenderblush2", 
                  "Southern Europe"= "bisque2",
                  "Western Europe"="#ACE1AF")

Income_color <- c("High Income" = "black",
                  "Middle Income" = "magenta3")

Colors <- Names |>
  select(Country, Region, Income) |>
  mutate(color_region = Region_color[Region],
         color_income = Income_color[Income]) |>
  as.data.frame()


color_flag <- c("Independent \nModel" ="darkolivegreen4" ,
                "Country \nModel" ="purple2",
                "Region \nModel" = "blue3",
                "Income \nModel" = "brown4",
                "Income-Region \nModel"= "darkgoldenrod3")

```

### The plots using the geo_facet to group the countries according to its position on the map.

```{r}
load(here::here("PISA_Data", "ISO Code.Rdata"))
C_codes <- ISO_Group |> filter(Continent == "Europe") |>
  select(name =Country, code = CNT)
 C_codes$name <- as.character(C_codes$name)
 C_codes <- C_codes |> arrange(name)


row<-c(7,5,3,4,5,5,6,4,2,1,1,5,3,7,4,1,2,6,2,4,
       2,4,6,7,4,6,3,1,3,6,4,2,5,3,5,6,1,5,3,2)

col<-c(6,4,7,2,6,8,5,5,4,7,6,2,4,7,6,1,1,4,7,4,
       6,3,7,4,8,6,3,4,5,1,7,8,7,6,5,2,5,3,8,2)

geo_grid <- cbind(row,col,C_codes)


## Comparing the model estimates
if (!dir.exists(here::here("Saved_Plots/Comparison_Visuals")))
  dir.create(here::here("Saved_Plots/Comparison_Visuals"))

Int <- ggplot(data = Combined_Int_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = Combined_Int_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.28, position=position_nudge(x = 0.20), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid, scales= "free_y")+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(
    axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 9.5, face = "plain",
                                    margin = margin(0.12,0,0.12,0, "cm")),
        axis.text.y = element_text(size = 9.5,face = "bold"),
      legend.position = "bottom")

Slope <- ggplot(data = Combined_Slop_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
    ggdist::stat_pointinterval(data = Combined_Slop_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.28, position=position_nudge(x = 0.20), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid, scales= "free_y")+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
        axis.text.y = element_text(size = 10,face = "bold"),
      legend.position = "bottom")
  
#-------------------------------------------------------------------------------

pdf("Saved_Plots/Comparison_Visuals/Interceptagain.pdf",
    width = 14,
    height = 10)
g <- get_geofacet_grob(Int) # for geo_facet plots
# g <- ggplotGrob(p) # for other ggplots

stript <- which(grepl('strip-t', g$layout$name)) 

for (i in stript){
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext,Colors$Country)
  if (!is.na(st)){
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
    r <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- Colors[st, "color_income"]
  } 
}

grid.draw(g)
dev.off()

###Slope
pdf("Saved_Plots/Comparison_Visuals/Slopeagain.pdf",
    width = 14,
    height = 10)

P <- get_geofacet_grob(Slope) # for geo_facet plots

stript <- which(grepl('strip-t', P$layout$name)) 

for (i in stript){
  j <- which(grepl('rect', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext,Colors$Country)
  if (!is.na(st)){
    P$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
    r <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- Colors[st, "color_income"]
  } 
}

grid.draw(P)
dev.off()
```

#### Comparing country estimates

```{r}
int <- ggplot(data = Combined_Int_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = Combined_Int_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid)+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(
    axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 9.5, face = "plain",
                                    margin = margin(0.12,0,0.12,0, "cm")),
        axis.text.y = element_text(size = 9.5,face = "bold"),
      legend.position = "bottom")

slop <- ggplot(data = Combined_Slop_Estimates)+
  geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
    ggdist::stat_pointinterval(data = Combined_Slop_estimates,
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
  facet_geo(~Country, grid = geo_grid, scales= "free_y")+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
        axis.text.y = element_text(size = 10,face = "bold"),
      legend.position = "bottom")
  
#-------------------------------------------------------------------------------

pdf("Saved_Plots/Comparison_Visuals/Comparing-countries-Intercept.pdf",
    width = 14,
    height = 10)
g <- get_geofacet_grob(int) # for geo_facet plots
# g <- ggplotGrob(p) # for other ggplots

stript <- which(grepl('strip-t', g$layout$name)) 

for (i in stript){
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext,Colors$Country)
  if (!is.na(st)){
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
    r <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- Colors[st, "color_income"]
  } 
}

grid.draw(g)
dev.off()

###Slope
pdf("Saved_Plots/Comparison_Visuals/Comparing-countries-Slope.pdf",
    width = 14,
    height = 10)

P <- get_geofacet_grob(slop) # for geo_facet plots

stript <- which(grepl('strip-t', P$layout$name)) 

for (i in stript){
  j <- which(grepl('rect', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext,Colors$Country)
  if (!is.na(st)){
    P$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- Colors[st, "color_region"]
    r <- which(grepl('text', P$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    P$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- Colors[st, "color_income"]
  } 
}

grid.draw(P)
dev.off()
```


### Selecting few countries to investigate.

Countries with one data point, and countries where the hierarchical structure downweight its estimate are worthy of careful observation.

Countries like; Albania, Belarus, Ukraine, Moldova, Macedonia,
Finland, Luxembourg, Liechtenstein, Czechia, Switzerland.

We want to investigate 10 countries. The first thing to do is to filter out the regression line on the data across the different fitted model for these countries.

```{r}
QCountries <- c("Albania", "Belarus", "Ukraine", "Moldova", "Macedonia",
                "Bosnia and Herzegovina","Finland", "Luxembourg", 
                "Liechtenstein", "Czechia", "Sweden", "Germany")

#Filtering the colors for the selected countries
QColors <- Colors |>
  filter(Country %in% QCountries)

pdf("Saved_Plots/Comparison_Visuals/few-country_fit.pdf",
    width = 12,
    height = 9)

ggplot(data = filter(PISA_Europe_Data, Country %in% QCountries), 
       aes(x=year_orig, y=math))+ 
  geom_point()+
  ggh4x::facet_wrap2(~Country, nrow = 4)+
  geom_abline(data=filter(CountryInd_IS_Est, Country %in% QCountries), aes(slope=year_orig, intercept= Intercept), color="lightseagreen")+
  geom_abline(data=filter(Country_IS_Est, Country %in% QCountries), 
              aes(slope=year_orig, intercept= Intercept), color="magenta3")+
  geom_abline(data=filter(Rcountry_IS_Est, Country %in% QCountries),
              aes(slope=year_orig, intercept= Intercept), color="blue3")+
geom_abline(data=filter(Icountry_IS_Est, Country %in% QCountries),
            aes(slope=year_orig, intercept= Intercept), color="yellow4")+
 geom_abline(data=filter(IRcountry_IS_Est, Country %in% QCountries),
             aes(slope=year_orig, intercept= Intercept), color="indianred")+
 scale_x_continuous(breaks = seq(-15,0,3),labels = function(x) x+2018) +
  xlab("year")+ ggtitle("Independent Model = lightseagreen \n Country-specific model = Magenta \n Region hierarchical model = blue \n Income hierarchical model = yellow \n Income-Region hierarchical model = Indianred")+
  theme_bw()+
  theme(panel.spacing=unit(1,"lines"),
        legend.position = "bottom",
        plot.subtitle = element_text(family = "Consolas"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

dev.off()

```

```{r}
## Intercept

A1 <- ggplot(data=filter(Combined_Int_Estimates, Country %in% QCountries))+
geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = filter(Combined_Int_estimates, Country %in% QCountries),
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
 ggh4x::facet_wrap2(~Country, scales= "free_y", nrow = 4)+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
      legend.position = "bottom")

#Comparing the country estimates 
a1 <- ggplot(data=filter(Combined_Int_Estimates, Country %in% QCountries))+
geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = filter(Combined_Int_estimates, Country %in% QCountries),
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
 ggh4x::facet_wrap2(~Country, nrow = 4)+
  labs(x = " ", y = "Intercept estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
      legend.position = "bottom")


pdf("Saved_Plots/Comparison_Visuals/FewerC_Intercept.pdf",
    width = 12,
    height = 9)

G <- ggplotGrob(A1)
# g$layout$name
Strip <- which(grepl('strip', G$layout$name)) 


for (i in Strip){
  j <- which(grepl('rect', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', G$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- G$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, QColors$Country)
  if (!is.na(st)){
    G$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- QColors[st, "color_region"]
    r <- which(grepl('text', G$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    G$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- QColors[st, "color_income"]
  }
}
grid.draw(G)
dev.off()

pdf("Saved_Plots/Comparison_Visuals/FewerC_Comparing-country-Intercept.pdf",
    width = 12,
    height = 9)

g <- ggplotGrob(a1)
# g$layout$name
Strip <- which(grepl('strip', g$layout$name)) 


for (i in Strip){
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, QColors$Country)
  if (!is.na(st)){
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- QColors[st, "color_region"]
    r <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- QColors[st, "color_income"]
  }
}
grid.draw(g)
dev.off()
```

```{r}
## Slope

A2 <- ggplot(data=filter(Combined_Slop_Estimates, Country %in% QCountries))+
geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = filter(Combined_Slop_estimates, Country %in% QCountries),
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3,alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
 ggh4x::facet_wrap2(~Country, scales= "free_y", nrow = 4)+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
      legend.position = "bottom")

#Comparing the country estimates 
a2 <- ggplot(data=filter(Combined_Slop_Estimates, Country %in% QCountries))+
geom_line(aes(x = Model, y = median(rvar), group = Country), linetype = "solid", color = "grey45")+
  ggdist::stat_pointinterval(aes(x = Model, ydist =rvar,color = Model),
                       point_size = 1.3, .width = c(.80,.95)) +
  ggdist::stat_pointinterval(data = filter(Combined_Slop_estimates, Country %in% QCountries),
             aes(x = Model, ydist = rvar, color = Model), .width = c(.80,.95),
             point_size = 1.3, alpha = 0.35, position=position_nudge(x = 0.15), width = 0.1)+
  scale_color_manual(values = color_flag)+
 ggh4x::facet_wrap2(~Country, nrow = 4)+
  labs(x = " ", y = "Slope estimates")+
  theme_bw()+
  theme(axis.text.x = element_blank(), 
        axis.ticks.x=element_blank(),
        strip.text.x = element_text(size = 10.5, face = "plain", margin = margin(0.13,0,0.13,0, "cm")),
      legend.position = "bottom")

pdf("Saved_Plots/Comparison_Visuals/FewerC_Slope.pdf",
    width = 12,
    height = 9)

G2 <- ggplotGrob(A2)
# g$layout$name
Strip2 <- which(grepl('strip', G2$layout$name)) 

for (i in Strip2){
  j <- which(grepl('rect', G2$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', G2$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- G2$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, QColors$Country)
  if (!is.na(st)){
    G2$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- QColors[st, "color_region"]
    r <- which(grepl('text', G2$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    G2$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- QColors[st, "color_income"]
  }
}
grid.draw(G2)
dev.off()

pdf("Saved_Plots/Comparison_Visuals/FewerC_Comparing-country-Slope.pdf",
    width = 12,
    height = 9)

g <- ggplotGrob(a2)
# g$layout$name
Strip <- which(grepl('strip', g$layout$name)) 


for (i in Strip){
  j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  k <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$childrenOrder))
  grobtext <- g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[1]]$label
  st <- match(grobtext, QColors$Country)
  if (!is.na(st)){
    g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- QColors[st, "color_region"]
    r <- which(grepl('text', g$grobs[[i]]$grobs[[1]]$children[[k]]$childrenOrder))
    g$grobs[[i]]$grobs[[1]]$children[[k]]$children[[r]]$gp$col <- QColors[st, "color_income"]
  }
}
grid.draw(g)
dev.off()
```

