---
title: "Model predictions from BRMS Model"
author: "Oluwayomi Akinfenwa"
date: "19/02/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(lme4)
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
library(bayesplot)
library(patchwork)
library(ggragged)
#library(geofacet)
```

Loading the PISA data for the European countries Europe_Pisamaths.Rdata.

```{r loading the data}
load(here::here("PISA_Data", "Europe_Pisamaths.Rdata"))

#We have decided to remove year 2022 from the analysis and make prediction for 2022.
#Hence I will filter year = 2022.

PISA_Europe_Data <- Pisa_Europe_Data |>
  filter(year != "2022")
```

#### Creating the grid for the prediction

```{r}
country_names <- levels(factor(PISA_Europe_Data$Country))
region_names <- levels(factor(PISA_Europe_Data$Region))
income_names <- levels(factor(PISA_Europe_Data$Income))
incomeregion_names <- levels(factor(PISA_Europe_Data$Income_Region))

## Obtaining the region indexes

country_region <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         
INCOME_REGION <- REGION |>
  left_join(INCOME, join_by(Country))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> left_join(INCOME_REGION, join_by(Country))
```

#### Creating pred_grid for model predictions

```{r}
#Creating a grid of the data.
pred <- PISA_Europe_Data |>
  modelr::data_grid(Country,year) 

#Creating a new data frame with year 2022 across all the countries
new_rows <- data.frame(
  year = 2022,
  Country = rep(unique(PISA_Europe_Data$Country)))

#Row-binding this data grid with the new grid for 2022.
Pred <- rbind(pred, new_rows)
# we now have 280 observations as the grid from 2003 to 2022 across the 40 countries

## Adding the numeric index
pred_grid <- Pred |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region))) |>
  mutate(year_orig = year - min(year))
```

## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```


### Pulling the posterior draws estimates for year 2022.

#### ytilde estimates from all the models

```{r}
Pred_grid <- pred_grid |> 
  select(c(Country,year,year_orig, Region, Income, Income_Region))

#We are interested in making predictions for 2022 only, 
# hence I want to filter year == 2022.
Pred_Grid <- Pred_grid |>
  filter(year == 2022)

#Independent model fit
CountryInd_model_pred <- Pred_Grid|>
  add_predicted_rvars(CountryInd_BRMSModel) |>
  rename(pred = .prediction)

#Country_specific model
Country_model_pred <- Pred_Grid|>
  add_predicted_rvars(Country_BRMSModel) |>
  rename(pred = .prediction)

#Region hierarchical model
Region_model_pred <- Pred_Grid|>
  add_predicted_rvars(Region_BRMSModel) |>
  rename(pred = .prediction)

#Income hierarchical model                         
Income_model_pred <- Pred_Grid|>
  add_predicted_rvars(Income_BRMSModel) |>
  rename(pred = .prediction)

#Income_Region hierarchical model
IR_model_pred <- Pred_Grid|>
  add_predicted_rvars(IncomeRegion_BRMSModel) |>
  rename(pred = .prediction)
```

### Based on the recommendations from our last meeting,we want to calculate the
### probability of the posterior prediction less than the observed PISA scores for year 2022.

```{r}
#the observed values for 2022
yobserved <- Pisa_Europe_Data |>
  filter(year == "2022")

#Independent model fit
IndCountry_Pred <- CountryInd_Model_Pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math)) |>
  mutate(diff = pred-math) |> median_qi(diff)

#Country_specific model
Country_Pred <- Country_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(diff = pred-math)|> median_qi(diff)

#Region hierarchical model
Region_Pred <- Region_Model_Pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(diff = pred-math)|> median_qi(diff)

#Income hierarchical model
Income_Pred <- Income_Model_Pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(diff = pred-math)|> median_qi(diff)

#Income-Region hierarchical model
IR_Pred <- IR_Model_Pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(diff = pred-math)|> median_qi(diff)
```


#### Visualising the probability of the pred values less than or equal the observed PISA 2022 scores.

```{r}
pdf("Saved_Plots/Pred_Prob_IndM.pdf",
    width = 10,
    height = 7)
ggplot(IndCountry_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country")+ggtitle("Independent country model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_Prob_CM.pdf",
    width = 10,
    height = 7)
ggplot(Country_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country") +ggtitle("Countrt-specific model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_Prob_RM.pdf",
    width = 10,
    height = 7)
ggplot(Region_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country")+ ggtitle("Region Hierarchical model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_Prob_IM.pdf",
    width = 10,
    height = 7)
ggplot(Income_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country") +ggtitle("Income Hierarchical model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_Prob_IRM.pdf",
    width = 10,
    height = 7)
ggplot(IR_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country")+ggtitle("Income-Region Hierarchical model \n The probability that the prediction is <= the observed value.")
dev.off()
```

#### Visualising the probability of the pred values less than or equal the observed PISA 2022 scores.

```{r}
pdf("Saved_Plots/Pred_diff_IndM.pdf",
    width = 10,
    height = 7)
ggplot(data =IndCountry_Pred)+
  geom_point(aes(x= diff, y= reorder(Country, diff))) +
  geom_errorbar(aes(xmin= .lower, xmax= .upper,y= reorder(Country, diff)))+
  geom_vline(aes(xintercept = 0), color = "burlywood4") +
  ylab("Country")+ggtitle("Independent country model \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_diff_CM.pdf",
    width = 10,
    height = 7)
ggplot(data = Country_Pred)+
  geom_point(aes(x= diff, y= reorder(Country, diff))) +
  geom_errorbar(aes(xmin= .lower, xmax= .upper,y= reorder(Country, diff)))+
  geom_vline(aes(xintercept = 0), color = "burlywood4") +
  ylab("Country") +ggtitle("Countrt-specific model \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_diff_RM.pdf",
    width = 10,
    height = 7)
ggplot(data = Region_Pred)+
  geom_point(aes(x= diff, y= reorder(Country, diff))) +
  geom_errorbar(aes(xmin= .lower, xmax= .upper,y= reorder(Country, diff)))+
  geom_vline(aes(xintercept = 0), color = "burlywood4") +
  ylab("Country")+ ggtitle("Region Hierarchical model \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_diff_IM.pdf",
    width = 10,
    height = 7)
ggplot(data = Income_Pred)+
  geom_point(aes(x= diff, y= reorder(Country, diff))) +
  geom_errorbar(aes(xmin= .lower, xmax= .upper,y= reorder(Country, diff)))+
  geom_vline(aes(xintercept = 0), color = "burlywood4") +
  ylab("Country") +ggtitle("Income Hierarchical model \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_diff_IRM.pdf",
    width = 10,
    height = 7)
ggplot(data = IR_Pred)+
  geom_point(aes(x= diff, y= reorder(Country, diff))) +
  geom_errorbar(aes(xmin= .lower, xmax= .upper,y= reorder(Country, diff)))+
  geom_vline(aes(xintercept = 0), color = "burlywood4") +
  ylab("Country")+ggtitle("Income-Region Hierarchical model \n The difference between the predicted value and the observed value.")
dev.off()
```

### Based on the recommendations from our last meeting, the distribution of the posterior draws for each country for year 2022 only.

```{r}
#Independent Country model
pdf("Saved_Plots/Pred_distr_IndM.pdf",
    width = 10,
    height = 7)
Pred_Grid |>
  add_predicted_draws(CountryInd_BRMSModel) |>
  ggplot(aes(x = .prediction, y = reorder(Country, .prediction))) +
  stat_slab()
dev.off()

#Country_specific model
pdf("Saved_Plots/Pred_distr_CM.pdf",
    width = 10,
    height = 7)
Pred_Grid |>
  add_predicted_draws(Country_BRMSModel) |>
  ggplot(aes(x = .prediction, y = reorder(Country, .prediction))) +
  stat_slab()
dev.off()


#Region hierarchical model
pdf("Saved_Plots/Pred_distr_RM.pdf",
    width = 10,
    height = 7)
Pred_Grid |>
  add_predicted_draws(Region_BRMSModel) |>
  ggplot(aes(x = .prediction, y = Country)) +
  stat_slab()
dev.off()


#Income hierarchical model
pdf("Saved_Plots/Pred_distr_IM.pdf",
    width = 10,
    height = 7)
Pred_Grid |>
  add_predicted_draws(Income_BRMSModel) |>
  ggplot(aes(x = .prediction, y =Country)) +
  stat_slab()
dev.off()


#Income-Region hierarchical model
pdf("Saved_Plots/Pred_distr_IRM.pdf",
    width = 10,
    height = 7)
Pred_Grid |>
  add_predicted_draws(IncomeRegion_BRMSModel) |>
  ggplot(aes(x = .prediction, y = Country)) +
  stat_slab()
dev.off()
```