---
title: "Model predictions from BRMS Model"
author: "Oluwayomi Akinfenwa"
date: "11/03/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading the indexing file containing the data and the country, region, income, income-region names and indexing.

```{r, data, include = FALSE}
sys.source("01_Indexing.R", envir = knitr::knit_global())
```

#### Creating pred_grid for model predictions

```{r}
##Setting the baseline year to 2018.
base_year <- 2018. 
#Creating a grid of the data.
#Recall that the Pisa_Europe_Data contains all the data set including the data for year 2018. 
Pred <- Pisa_Europe_Data |>
  modelr::data_grid(Country, year) |>
  mutate(year_orig = year - min(base_year))
# we now have 280 observations as the grid from 2003 to 2022 across the 40 countries.

## Adding the numeric index
pred_grid <- Pred |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num])

#We are interested in making predictions for 2022 only. Hence, I want to filter year == 2022.
Pred_grid <- pred_grid |>
  filter(year == 2022)

# For the independent model, recall that we excluded countries with one data points, the grid should only include the countries used in fitting the model.
# Grid for independent model.
SCountry <- c("Belarus", "Bosnia& Herzegovina", "Ukraine")
SPred_grid <- Pred_grid |>
  filter(!Country %in% SCountry)
```

## Loading the hierarchical models from the saved R.Data file

```{r}
#Independent-Country specific model
load(here::here("Manuscript_Models", "CountryInd_BRMSModel.Rdata"))

#Country specific model
load(here::here("Manuscript_Models", "Country_BRMSModel.Rdata"))

#Region hierarchical model
load(here::here("Manuscript_Models", "Region_BRMSModel.Rdata"))

#Income hierarchical model
load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))

#Income-Region hierarchical model
load(here::here("Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```

### Pulling the posterior draws estimates for the year 2022.

#### ytilde estimates from all the models

```{r}
#Independent model fit
CountryInd_model_pred <- SPred_grid|>
add_predicted_rvars(CountryInd_BRMSModel) |>
rename(pred = .prediction)

#Country_specific model
Country_model_pred <- Pred_grid|>
  add_predicted_rvars(Country_BRMSModel) |>
  rename(pred = .prediction)

#Region hierarchical model
Region_model_pred <- Pred_grid|>
  add_predicted_rvars(Region_BRMSModel) |>
  rename(pred = .prediction)

#Income hierarchical model                         
Income_model_pred <- Pred_grid|>
  add_predicted_rvars(Income_BRMSModel) |>
  rename(pred = .prediction)

#Income_Region hierarchical model
IR_model_pred <- Pred_grid|>
  add_predicted_rvars(IncomeRegion_BRMSModel) |>
  rename(pred = .prediction)
```

### Based on the recommendations from our last meeting, we want to calculate the
### probability of the posterior prediction less than the observed PISA scores for year 2022.

```{r}
#the observed values for 2022
yobserved <- Pisa_Europe_Data |>
  filter(year == "2022")

#Independent model fit
IndCountry_Pred <- CountryInd_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math)) |>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Country_specific model
Country_Pred <- Country_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Region hierarchical model
Region_Pred <- Region_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Income hierarchical model
Income_Pred <- Income_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Income-Region hierarchical model
IR_Pred <- IR_model_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 
```

#### Visualising the probability of the pred values less than or equal the observed PISA 2022 scores.

```{r}
# pdf("Saved_Plots/Pred_diff_IndM.pdf",
#     width = 10,
#     height = 7)
# ggplot(data =IndCountry_Pred)+
#   ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
#           color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
#   geom_point(aes(x= math0, y= Country),
#              shape=23, fill="blue", color="darkred", size=1.5)  +
#   xlab("Differences between predicted and observed")+
#   ggtitle("Independent country model \n The difference between the predicted value and the observed value.")
# dev.off()


pdf("Saved_Plots/Pred_differences/Pred_diff_CM.pdf",
    width = 10,
    height = 7)
ggplot(data = Country_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Country-specific model \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/Pred_diff_RM.pdf",
    width = 10,
    height = 7)
ggplot(data = Region_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Region Hierarchical \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/Pred_diff_IM.pdf",
    width = 10,
    height = 7)
ggplot(data = Income_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Income Hierarchical \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/Pred_diff_IRM.pdf",
    width = 10,
    height = 7)
ggplot(data = IR_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Income-Region Hierarchical model \n The difference between the predicted value and the observed value.")
dev.off()
```

#### Visualising the probability of the pred values less than or equal the observed PISA 2022 scores.

```{r}
pdf("Saved_Plots/Pred_Prob_IndM.pdf",
    width = 10,
    height = 7)
ggplot(IndCountry_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country")+ggtitle("Independent country model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_Prob_CM.pdf",
    width = 10,
    height = 7)
ggplot(Country_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country") +ggtitle("Countrt-specific model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_Prob_RM.pdf",
    width = 10,
    height = 7)
ggplot(Region_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country")+ ggtitle("Region Hierarchical model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_Prob_IM.pdf",
    width = 10,
    height = 7)
ggplot(Income_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country") +ggtitle("Income Hierarchical model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_Prob_IRM.pdf",
    width = 10,
    height = 7)
ggplot(IR_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country")+ggtitle("Income-Region Hierarchical model \n The probability that the prediction is <= the observed value.")
dev.off()
```