---
title: "Model predictions from BRMS Model"
author: "Oluwayomi Akinfenwa"
date: "11/03/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading the Rmd file containing the BRMS model fitting and extracting the model estimates.

```{r, libraries, include = FALSE}
source(knitr::purl("03_JAGS_Hierarchical_Models.Rmd"))
```

#### Creating pred_grid for model predictions

```{r}
#Independent country model predictions
JAGS_CountryInd_Pred <- spread_rvars(CountryInd_ModelSample , ytilde[Index]) |>
  left_join(Spred_grid, join_by(Index== Index)) |>
  select(Country, year, year_orig, Region, Income, Income_Region, pred=ytilde)

#Country-specific model predictions
JAGS_Country_Pred <- spread_rvars(Country_ModelSample , ytilde[Index]) |>
  left_join(pred_grid, join_by(Index== Index)) |>
  select(Country, year, year_orig, Region, Income, Income_Region, pred=ytilde)

 #Region hierarchical model predictions
JAGS_Region_Pred <- spread_rvars(Country_ModelSample , ytilde[Index]) |>
  left_join(pred_grid, join_by(Index== Index)) |>
  select(Country, year, year_orig, Region, Income, Income_Region, pred=ytilde)

#Income hierarchical  model predictions
JAGS_Income_Pred <- spread_rvars(Country_ModelSample , ytilde[Index]) |>
  left_join(pred_grid, join_by(Index== Index)) |>
  select(Country, year, year_orig, Region, Income, Income_Region, pred=ytilde)

#Income-Region hierarchical model predictions
JAGS_IR_Pred <- spread_rvars(Country_ModelSample , ytilde[Index]) |>
  left_join(pred_grid, join_by(Index== Index)) |>
  select(Country, year, year_orig, Region, Income, Income_Region, pred=ytilde)
```

### Pulling the posterior draws estimates for the year 2022.

#### Filtering year == 2022

```{r}
JAGS_CountryInd_pred <- JAGS_CountryInd_Pred |>
  filter(year == "2022")

JAGS_Country_pred <- JAGS_Country_Pred|>
  filter(year == "2022")

JAGS_Region_pred <- JAGS_Region_Pred |>
  filter(year == "2022")

JAGS_Income_pred <- JAGS_Income_Pred |>
  filter(year == "2022")

JAGS_IR_pred <- JAGS_IR_Pred |>
  filter(year == "2022")
```

### Based on the recommendations from our last meeting, we want to calculate the
### probability of the posterior prediction less than the observed PISA scores for year 2022.

```{r}
#the observed values for 2022
yobserved <- Pisa_Europe_Data |>
  filter(year == "2022")

#Independent model fit
JAGS_CountryInd_Pred <- JAGS_CountryInd_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math)) |>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Country_specific model
JAGS_Country_Pred <- JAGS_Country_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Region hierarchical model
JAGS_Region_Pred <- JAGS_Region_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Income hierarchical model
JAGS_Income_Pred <- JAGS_Income_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 

#Income-Region hierarchical model
JAGS_IR_Pred <- JAGS_IR_pred |>
  left_join(select(yobserved, Country, math), join_by(Country)) |>
  mutate(prob = posterior::Pr(pred <= math))|>
  mutate(pred0 = pred-median(pred),math0 = math- median(pred)) |>
  arrange(!is.na(math0), math0) |>
  mutate(Country = factor(Country, levels = Country)) 
```

#### Visualising the probability of the pred values less than or equal the observed PISA 2022 scores.

```{r}
# pdf("Saved_Plots/Pred_diff_IndM.pdf",
#     width = 10,
#     height = 7)
# ggplot(data =IndCountry_Pred)+
#   ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
#           color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
#   geom_point(aes(x= math0, y= Country),
#              shape=23, fill="blue", color="darkred", size=1.5)  +
#   xlab("Differences between predicted and observed")+
#   ggtitle("Independent country model \n The difference between the predicted value and the observed value.")
# dev.off()


pdf("Saved_Plots/Pred_differences/JAGS_Pred_diff_CM.pdf",
    width = 10,
    height = 7)
ggplot(data = JAGS_Country_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Country-specific model \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/JAGS_Pred_diff_RM.pdf",
    width = 10,
    height = 7)
ggplot(data = JAGS_Region_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Region Hierarchical \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/JAGS_Pred_diff_IM.pdf",
    width = 10,
    height = 7)
ggplot(data = JAGS_Income_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Income Hierarchical \n The difference between the predicted value and the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/JAGS_Pred_diff_IRM.pdf",
    width = 10,
    height = 7)
ggplot(data = JAGS_IR_Pred)+
  ggdist::stat_pointinterval(aes(xdist = pred0, y= Country),
          color ="burlywood4", .width = c(.50, .80, .95), point_size = 1.4) +
  geom_point(aes(x= math0, y= Country),
             shape=23, fill="blue", color="darkred", size=1.5)  +
  xlab("Differences between predicted and observed") +ggtitle("Income-Region Hierarchical model \n The difference between the predicted value and the observed value.")
dev.off()
```

#### Visualising the probability of the pred values less than or equal the observed PISA 2022 scores.

```{r}
pdf("Saved_Plots/Pred_differences/JAGS_Pred_Prob_IndM.pdf",
    width = 10,
    height = 7)
ggplot(JAGS_CountryInd_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country")+ggtitle("Independent country model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/JAGS_Pred_Prob_CM.pdf",
    width = 10,
    height = 7)
ggplot(JAGS_Country_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country") +ggtitle("Countrt-specific model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/JAGS_Pred_Prob_RM.pdf",
    width = 10,
    height = 7)
ggplot(JAGS_Region_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country")+ ggtitle("Region Hierarchical model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/JAGS_Pred_Prob_IM.pdf",
    width = 10,
    height = 7)
ggplot(JAGS_Income_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country") +ggtitle("Income Hierarchical model \n The probability that the prediction is <= the observed value.")
dev.off()


pdf("Saved_Plots/Pred_differences/JAGS_Pred_Prob_IRM.pdf",
    width = 10,
    height = 7)
ggplot(JAGS_IR_Pred,
       aes(x= prob, y= reorder(Country, prob)))+
  geom_point() +
  geom_vline(xintercept = 0.5, color = "red4") +
  ylab("Country")+ggtitle("Income-Region Hierarchical model \n The probability that the prediction is <= the observed value.")
dev.off()
```