---
title: "The Bayesian hierarchical models for Region, Income and Income-Region"
author: "Oluwayomi Akinfenwa"
date: "30/01/2024"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
#library(brms)
```

Loading the PISA data for the European countries Europe_Pisamaths.Rdata.

```{r loading the data}
load(here::here("Saved_PISA_Data", "Europe_Pisamaths.Rdata"))

# Tidying the data
Pisa_Europe_Data <- Pisa_Europe_Data |>
  rename(se_y = sigma) |>
  mutate(weight = 1/ (se_y^2))
```

We have decided to remove year 2022 from the analysis and make prediction for 2022.
Hence I will filter year = 2022.

```{r}
PISA_Europe_Data <- Pisa_Europe_Data |>
  filter(year != "2022")
```

#### Creating the grid for the prediction

```{r}
country_names <- levels(factor(PISA_Europe_Data$Country))
region_names <- levels(factor(PISA_Europe_Data$Region))
income_names <- levels(factor(PISA_Europe_Data$Income))
incomeregion_names <- levels(factor(PISA_Europe_Data$Income_Region))

## Obtaining the region indexes

country_region <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

REGION <- country_region |> select(Country, Region)

## Obtaining the income indexes

country_income <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income=first(Income)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(income_num = as.numeric(as.factor(Income)))
         
INCOME <- country_income |> select(Country, Income)

## Obtaining the income_region indexes

country_incomeregion <- PISA_Europe_Data |> group_by(Country) |>
  summarise(Income_Region=first(Income_Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(incomeregion_num = as.numeric(as.factor(Income_Region)))
         
INCOME_REGION <- REGION |>
  left_join(INCOME, join_by(Country))

Country_region <- country_region |> left_join(INCOME, join_by(Country))
Country_income <- country_income |> left_join(REGION, join_by(Country))
Country_incomeregion <- country_incomeregion |> left_join(INCOME_REGION, join_by(Country))
```

#### Creating pred_grid for model predictions

```{r}
#Creating a grid of the data.
pred <- PISA_Europe_Data |>
  modelr::data_grid(Country,year) 

#Creating a new data frame with year 2022 across all the countries
new_rows <- data.frame(
  year = 2022,
  Country = rep(unique(PISA_Europe_Data$Country)))

#Row-binding this data grid with the new grid for 2022.
Pred <- rbind(pred, new_rows)
# we now have 280 observations as the grid from 2003 to 2022 across the 40 countries

# We want to copy the weights from the PISA data as the weight for predictions,
# Where the weights for 2022 will be the weights for the previous year 2018, 
# and the remaining missing weights will be the maximum weight for the country it belongs.
A <- PISA_Europe_Data |>
  select(Country, year, se_y)

Grid <- merge(Pred, A, by = c("year", "Country"), all.x = TRUE)

# Specifying the weights for 2022 as the sample weight of the year 2018.
pred_grid <- Grid |>
  group_by(Country) |>
  mutate(se_pred = ifelse(year == 2022, se_y[year == 2018], se_y)) #If year = 2022, copy the weight for 2018 else return W.

pred_grid <- pred_grid |>
  group_by(Country) |>
  mutate(se_pred = ifelse(is.na(se_pred), max(se_pred, na.rm = TRUE), se_pred),
         year_orig = year - min(year)) |>
  arrange(Country) |>
  tibble::as_tibble()

## Adding the numeric index
Pred_grid <- pred_grid |>
  mutate(Country_num = as.numeric(as.factor(Country)),
  Region = country_region$Region[Country_num],
  Income = country_income$Income[Country_num],
  Income_Region = country_incomeregion$Income_Region[Country_num]) |>
  mutate(region_num = as.numeric(as.factor(Region)),
         income_num = as.numeric(as.factor(Income)),
         incomeregion_num = as.numeric(as.factor(Income_Region)))
```

## Setting the model parameter specification for JAGS

### Writing JAGS model for country-level specifications

```{r Ind_Countrymodel}
if (!dir.exists(here::here("BAYSM_2024/Manuscript_Models")))
  dir.create(here::here("BAYSM_2024/Manuscript_Models"))

if(file.exists(here::here("Manuscript_Models",
                          "Ind_Country_Model.Rdata"))){
  load(here::here("Manuscript_Models",
                          "Ind_Country_Model.Rdata"))
  countryJags <- FALSE
} else countryJags <- TRUE
```

```{r, eval = countryJags}
Ind_C_JAGS_Model = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i])
sigma_y[i] <- sqrt(sigma[i]^2 + sigma.m^2)
}

# Prior on country alphas and betas

for (j in 1:n_C){
alpha.j[j] ~ dnorm(500, 100^-2)
beta.j[j] ~ dnorm(0, 2^-2)
}

sigma.m ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Setting up the posterior
for(m in 1:n_pred){
ytilde[m] ~ dnorm(mu_pred.m[m], sigma.pred[m]^-2)
sigma.pred[m] <- sqrt((se.pred[m]^2) + (sigma.m^2))
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]]*(xpred.m[m])
}

# Setting up yrep for posterior predictive checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)
}
}
"

## JAGS Model
Ind_C_Jags.data <- list(y.i = PISA_Europe_Data$math,
                    x.i = PISA_Europe_Data$year_orig,
                    n = nrow(PISA_Europe_Data),
                    sigma = PISA_Europe_Data$se_y,
                    n_C = PISA_Europe_Data$Country |> unique() |> length(),
                    C = as.numeric(factor(PISA_Europe_Data$Country)),
                    se.pred = Pred_grid$se_pred,
                    n_pred = nrow(Pred_grid),
                    C_pred = Pred_grid$Country_num,
                    xpred.m = Pred_grid$year_orig)

Ind_C_Parnames <- c("alpha.j","beta.j","sigma_y","sigma.m",
          "ytilde", "yrep","mu_pred.m","mu.i")

# model
Ind_C_Model <- jags(data = Ind_C_Jags.data,
              parameters.to.save = Ind_C_Parnames,
              model.file = textConnection(Ind_C_JAGS_Model),
              n.iter = 10000,
              n.burnin = 2000,
              n.chains = 4,
              n.thin = 4)

save(Ind_C_Model, file=here::here("BAYSM_2024/Manuscript_Models", "Ind_Country_Model.Rdata"))
```

#### Country-specific model

```{r Countrymodel}
if (!dir.exists(here::here("Manuscript_Models")))
  dir.create(here::here("Manuscript_Models"))

if(file.exists(here::here("Manuscript_Models",
                          "Country_Model.Rdata"))){
  load(here::here("Manuscript_Models",
                          "Country_Model.Rdata"))
  countryJags <- FALSE
} else countryJags <- TRUE
```

```{r, eval = countryJags}
C_JAGS_Model = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i])
sigma_y[i] <- sqrt(sigma[i]^2 + sigma.m^2)
}

# Prior on country alphas

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha, sigma_alpha^-2)
beta.j[j] ~ dnorm(mu_beta, sigma_beta^-2)
}

# Prior on sigma, model variation
sigma.m ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution
mu_alpha ~ dnorm(500, 100^-2)
mu_beta ~ dnorm(0, 2^-2)
sigma_alpha ~ dt(0, 5^-2,1)T(0,) # Truncated t-distribution
sigma_beta ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution 

# Setting up the posterior
for(m in 1:n_pred){
sigma.pred[m] <- sqrt((se.pred[m]^2) + (sigma.m^2))
ytilde[m] ~ dnorm(mu_pred.m[m], sigma.pred[m]^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]]*(xpred.m[m])
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)
}
}
"

## JAGS Model
C_Jags.data <- list(y.i = PISA_Europe_Data$math,
                    x.i = PISA_Europe_Data$year_orig,
                    sigma = PISA_Europe_Data$se_y,
                    n = nrow(PISA_Europe_Data),
                    n_C = PISA_Europe_Data$Country |> unique() |> length(),
                    C = as.numeric(factor(PISA_Europe_Data$Country)),
                    se.pred = Pred_grid$se_pred,
                    n_pred = nrow(Pred_grid),
                    C_pred = Pred_grid$Country_num,
                    xpred.m = Pred_grid$year_orig)

C_Parnames <- c("alpha.j","beta.j", "mu_alpha", "mu_beta","sigma_y","sigma.m",
                "sigma_alpha","sigma_beta","ytilde", "yrep","mu_pred.m","mu.i")

# model
C_Model <- jags(data = C_Jags.data,
              parameters.to.save = C_Parnames,
              model.file = textConnection(C_JAGS_Model),
              n.iter = 10000,
              n.burnin = 2000,
              n.chains = 4,
              n.thin = 4)

save(C_Model, file=here::here("BAYSM_2024/Manuscript_Models", "Country_Model.Rdata"))
```

**This C_MODEL fits a separate linear regression for each country, with a distribution on the hyper parameter.**

# Hierarchical Model

## Region-based Country specific intercept and slope

### Region as a hierarchical structure.

```{r Regionmodel}
if (!dir.exists(here::here("Manuscript_Models")))
  dir.create(here::here("Manuscript_Models"))

if(file.exists(here::here("Manuscript_Models",
                          "Region_Model.Rdata"))){
  load(here::here("Manuscript_Models",
                          "Region_Model.Rdata"))
  regionJags <- FALSE
} else regionJags <- TRUE
```

```{r, eval = regionJags}
hmregion = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i] )
sigma_y[i] <- sqrt(sigma[i]^2 + sigma.m^2)
}

# Prior on alphas to vary by region

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha.r[R[j]], sigma_alpha[R[j]]^-2)
beta.j[j] ~ dnorm(mu_beta.r[R[j]], sigma_beta^-2)
}

for (r in 1:n_R){
mu_alpha.r[r] ~ dnorm(mu_alpha_eur, sigma_alpha.r^-2)
mu_beta.r[r] ~ dnorm(mu_beta_eur, sigma_beta.r^-2)
sigma_alpha[r] ~ dt( 0, 5^-2,1)T(0,) # Truncated t-distribution
}

# Prior on sigma, model variation
sigma.m ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on alpha hyper-parameters
mu_alpha_eur ~ dnorm(500, 100^-2)
sigma_alpha.r ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution

# Prior on beta hyper-parameters
mu_beta_eur ~ dnorm(0, 2^-2)
sigma_beta ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution 
sigma_beta.r ~ dt( 0, 1^-2,1)T(0,) # Truncated t-distribution


# Setting up the posterior
for(m in 1:n_pred){
sigma.pred[m] <- sqrt((se.pred[m]^2) + (sigma.m^2))
ytilde[m] ~ dnorm(mu_pred.m[m], sigma.pred[m]^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]]*(xpred.m[m])
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)
}
}
"

## JAGS Model

R_Jags.data <- list(y.i = PISA_Europe_Data$math,
                  x.i = PISA_Europe_Data$year_orig,
                  sigma = PISA_Europe_Data$se_y,
                  n = nrow(PISA_Europe_Data),
                  n_C = PISA_Europe_Data$Country %>% unique() %>% length(),
                  C = as.numeric(factor(PISA_Europe_Data$Country)),
                  R = country_region$region_num,
                  n_pred = nrow(Pred_grid),
                  se.pred = Pred_grid$se_pred,
                  C_pred = Pred_grid$Country_num,
                  xpred.m = Pred_grid$year_orig,
                  n_R = PISA_Europe_Data$Region %>% unique() %>% length())

R_Parnames <- c( "alpha.j","beta.j","sigma_y","sigma.m","sigma_alpha","sigma_beta",
                 "mu_alpha.r","mu_beta.r","mu_alpha_eur","mu_beta_eur", "ytilde", 
                 "yrep","mu_pred.m", "mu.i" ,"sigma_alpha.r", "sigma_beta.r")

# model
Region_Model <- jags(data = R_Jags.data,
              parameters.to.save = R_Parnames,
              model.file = textConnection(hmregion),
              n.iter = 10000,
              n.burnin = 2000,
              n.chains = 4,
              n.thin = 4)

save(Region_Model, file=here::here("BAYSM_2024/Manuscript_Models", "Region_Model.Rdata"))
```

**R_Model fits a hierarchical model on the PISA_Europe_Data by estimating the model parameters based on the estimates from its different level of hierarchy (geographical region)**

### Income as a hierarchical structure.

```{r Incomemodel}
if (!dir.exists(here::here("Manuscript_Models")))
  dir.create(here::here("Manuscript_Models"))

if(file.exists(here::here("Manuscript_Models",
                          "Income_Model.Rdata"))){
  load(here::here("Manuscript_Models",
                          "Income_Model.Rdata"))
  incomeJags <- FALSE
} else incomeJags <- TRUE
```

```{r, eval = incomeJags}
hmincome = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i])
sigma_y[i] <- sqrt(sigma[i]^2 + sigma.m^2)
}

# Prior on alphas to vary by income

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha.I[I[j]], sigma_alpha[I[j]]^-2)
beta.j[j] ~ dnorm(mu_beta.I[I[j]], sigma_beta^-2)
}

for (r in 1:n_I){
mu_alpha.I[r] ~ dnorm(mu_alpha_inc, sigma_alpha.inc^-2)
mu_beta.I[r] ~ dnorm(mu_beta_inc, sigma_beta.inc^-2)
sigma_alpha[r] ~ dt( 0, 5^-2,1)T(0,) # Truncated t-distribution
}

# Prior on sigma, model variation
sigma.m ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on alpha hyper-parameters
mu_alpha_inc ~ dnorm(500, 100^-2)
sigma_alpha.inc ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution

# Prior on beta hyper-parameters
mu_beta_inc ~ dnorm(0, 2^-2)
sigma_beta ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution
sigma_beta.inc ~ dt( 0, 1^-2,1)T(0,) # Truncated t-distribution


# Setting up the posterior
for(m in 1:n_pred){
sigma.pred[m] <- sqrt((se.pred[m]^2) + (sigma.m^2))
ytilde[m] ~ dnorm(mu_pred.m[m], sigma.pred[m]^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]]*(xpred.m[m])
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)
}
}
"

## JAGS Model

I_Jags.data <- list(y.i = PISA_Europe_Data$math,
                    x.i = PISA_Europe_Data$year_orig,
                    sigma = PISA_Europe_Data$se_y,
                    n = nrow(PISA_Europe_Data),
                    n_C = PISA_Europe_Data$Country %>% unique() %>% length(),
                    C = as.numeric(factor(PISA_Europe_Data$Country)),
                    I = country_income$income_num,
                    se.pred = Pred_grid$se_pred,
                    n_pred = nrow(Pred_grid),
                    C_pred = Pred_grid$Country_num,
                    xpred.m = Pred_grid$year_orig,
                    n_I = PISA_Europe_Data$Income %>% unique() %>% length())

I_Parnames <- c("alpha.j","beta.j","sigma_y","sigma.m","sigma_alpha","sigma_beta",
                 "mu_alpha.I","mu_beta.I","mu_alpha_inc","mu_beta_inc", "ytilde", 
                "yrep","mu_pred.m", "mu.i" ,"sigma_alpha.inc", "sigma_beta.inc")
 
# model
Income_Model <- jags(data = I_Jags.data,
                parameters.to.save = I_Parnames,
                model.file = textConnection(hmincome),
                n.iter = 10000,
                n.burnin = 2000,
                n.chains = 4,
                n.thin = 4)

save(Income_Model, file=here::here("BAYSM_2024/Manuscript_Models", "Income_Model.Rdata"))
```

**I_Model fits a hierarchical model on the Pisa_Europe_Data by estimating the model parameters based on the estimates from its different level of hierarchy (income classification)**

### Income_Region as a hierarchical structure.

```{r IncomeRegionmodel}
if (!dir.exists(here::here("Manuscript_Models")))
  dir.create(here::here("Manuscript_Models"))

if(file.exists(here::here("Manuscript_Models",
                          "IncomeRegion_Model.Rdata"))){
  load(here::here("Manuscript_Models",
                          "IncomeRegion_Model.Rdata"))
  incomeregionJags <- FALSE
} else incomeregionJags <- TRUE
```

```{r, eval=incomeregionJags}
hmincome_region = "
model{
# Data model
for (i in 1:n){
y.i[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)

mu.i[i] <- alpha.j[C[i]] + beta.j[C[i]]*(x.i[i])
sigma_y[i] <- sqrt(sigma[i]^2 + sigma.m^2)
}

# Prior on alphas to vary by income

for(j in 1:n_C){
alpha.j[j] ~ dnorm(mu_alpha.IR[IR[j]], sigma_alpha[IR[j]]^-2)
beta.j[j] ~ dnorm(mu_beta.IR[IR[j]], sigma_beta^-2)
}

for (r in 1:n_IR){
mu_alpha.IR[r] ~ dnorm(mu_alpha_inre, sigma_alpha.inre^-2)
mu_beta.IR[r] ~ dnorm(mu_beta_inre, sigma_beta.inre^-2)
sigma_alpha[r] ~ dt( 0, 100^-2,1)T(0,) # Truncated t-distribution
}

#sigma_alpha ~ dt( 0, 5^-2,1)T(0,) # Truncated t-distribution
# Prior on sigma, model variation
sigma.m ~ dt (30, 10^-2,1)T(0,) # Truncated t-distribution

# Prior on alpha hyper-parameters
mu_alpha_inre ~ dnorm(500, 100^-2)
sigma_alpha.inre ~ dt( 0, 100^-2,1)T(0,) # Truncated t-distribution

# Prior on beta hyper-parameters
mu_beta_inre ~ dnorm(0, 2^-2)
sigma_beta ~ dt( 0, 2^-2,1)T(0,) # Truncated t-distribution
sigma_beta.inre ~ dt( 0, 1^-2,1)T(0,) # Truncated t-distribution


for(m in 1:n_pred){
sigma.pred[m] <- sqrt((se.pred[m]^2) + (sigma.m^2))
ytilde[m] ~ dnorm(mu_pred.m[m], sigma.pred[m]^-2)
mu_pred.m[m] <- alpha.j[C_pred[m]] + beta.j[C_pred[m]]*(xpred.m[m])
}

# Setting up yrep for posterior predictive  checks
for (i in 1:n){
yrep[i] ~ dnorm(mu.i[i], sigma_y[i]^-2)
}
}
"

#JAGS Data
IR_Jags.data <- list(y.i = PISA_Europe_Data$math,
                    x.i = PISA_Europe_Data$year_orig,
                    sigma = PISA_Europe_Data$se_y,
                    n = nrow(PISA_Europe_Data),
                    n_C = PISA_Europe_Data$Country %>% unique() %>% length(),
                    C = as.numeric(factor(PISA_Europe_Data$Country)),
                    IR = country_incomeregion$incomeregion_num,
                    se.pred = Pred_grid$se_pred,
                    n_pred = nrow(Pred_grid),
                    C_pred = Pred_grid$Country_num,
                    xpred.m = Pred_grid$year_orig,
                    n_IR = PISA_Europe_Data$Income_Region %>% unique() %>% length())

IR_Parnames <- c("alpha.j","beta.j","sigma_y","sigma.m","sigma_alpha","sigma_beta",
                 "mu_alpha.IR","mu_beta.IR","mu_alpha_inre","mu_beta_inre","yrep",
                 "ytilde","mu_pred.m", "mu.i","sigma_alpha.inre","sigma_beta.inre")
# model
IR_Model <- jags(data = IR_Jags.data,
                parameters.to.save = IR_Parnames,
                model.file = textConnection(hmincome_region),
                n.iter = 10000,
                n.burnin = 2000,
                n.chains = 4,
                n.thin = 4)

save(IR_Model, file=here::here("BAYSM_2024/Manuscript_Models", "IncomeRegion_Model.Rdata"))
```


## Specifying the models in BRMS

BRMS Stuffs

```{r}
#library(cmdstanr)
options(mc.cores = 4
    #brms.backend = "cmdstanr"
)

bayes_seed <-1234
```

#### Independent model with gloabl mean as the slope.

```{r}
if (file.exists(here::here("BAYSM_2024/Manuscript_Models", "CountryInd_BRMSModel.Rdata"))){
  load(here::here("BAYSM_2024/Manuscript_Models", "CountryInd_BRMSModel.Rdata"))
  genBRMS <- FALSE
} else genBRMS <- TRUE

```

```{r, message=FALSE, eval= genBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 10), class = sigma))


CountryInd_BRMSModel <- brms::brm(
 brms::bf(math|se(se_y, sigma = TRUE) ~ year_orig + (1 ||Country)),
  data = PISA_Europe_Data,
  iter = 6000, 
  prior = Priors,
  control = list(adapt_delta = 0.93),
  chains = 4, seed = bayes_seed)

save(CountryInd_BRMSModel, file=here::here("BAYSM_2024/Manuscript_Models", "CountryInd_BRMSModel.Rdata"))
```

```{r}
if (file.exists(here::here("BAYSM_2024/Manuscript_Models", "Country_BRMSModel.Rdata"))){
  load(here::here("BAYSM_2024/Manuscript_Models", "Country_BRMSModel.Rdata"))
  genBRMS <- FALSE
} else genBRMS <- TRUE

```

#### Independent model with gloabl mean as the slope.

```{r, message=FALSE, eval= genBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 10), class = sigma),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group=Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group=Country))


Country_BRMSModel <- brms::brm(
   brms::bf(math|se(se_y, sigma = TRUE) ~ year_orig +(1 + year_orig||Country)),
  data = PISA_Europe_Data,
  iter = 6000, 
  prior = Priors,
  control = list(adapt_delta = 0.93),
  chains = 4, seed = bayes_seed)

save(Country_BRMSModel, file=here::here("BAYSM_2024/Manuscript_Models", "Country_BRMSModel.Rdata"))
```

```{r}
if (file.exists(here::here("BAYSM_2024/Manuscript_Models", "Region_BRMSModel.Rdata"))){
  load(here::here("BAYSM_2024/Manuscript_Models", "Region_BRMSModel.Rdata"))
  genBRMS <- FALSE
} else genBRMS <- TRUE

```

Running the brms model for region hierarchical model

```{r, message=FALSE, eval= genBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 10), class = sigma),
            brms::prior(cauchy(0, 2), class = sd, coef = Intercept, group= Region),
            brms::prior(cauchy(0, 1), class = sd, coef = year_orig, group= Region),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group= Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Country))


Region_BRMSModel <- brms::brm(
  brms::bf(math|se(se_y, sigma = TRUE) ~ year_orig + (1 + year_orig||Region)+ 
             (1 + year_orig||Country)),
  data = PISA_Europe_Data,
  iter = 6000, 
  prior = Priors,
  control = list(adapt_delta = 0.93), silent=2,
  chains = 4, seed = bayes_seed)

save( Region_BRMSModel, file=here::here("BAYSM_2024/Manuscript_Models", "Region_BRMSModel.Rdata"))
```


```{r}
if (file.exists(here::here("BAYSM_2024/Manuscript_Models", "Income_BRMSModel.Rdata"))){
  load(here::here("Manuscript_Models", "Income_BRMSModel.Rdata"))
  GenBRMS <- FALSE
} else GenBRMS <- TRUE

```

Running the brms model for Income hierarchical model

```{r, message=FALSE, eval= GenBRMS}

Priors <-  c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 10), class = sigma),
            brms::prior(cauchy(0, 2), class = sd, coef = Intercept, group= Income),
            brms::prior(cauchy(0, 1), class = sd, coef = year_orig, group= Income),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group= Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Country))


Income_BRMSModel <- brms::brm(
  brms::bf(math|se(se_y, sigma = TRUE) ~ year_orig + (1 + year_orig||Income)+ 
             (1 + year_orig||Country)),
  data = PISA_Europe_Data,
  iter = 6000, 
  prior = Priors,
  control = list(adapt_delta = 0.9), silent=2,
  chains = 4, seed = bayes_seed)

save( Income_BRMSModel, file=here::here("BAYSM_2024/Manuscript_Models", "Income_BRMSModel.Rdata"))
```

```{r}
if (file.exists(here::here("BAYSM_2024/Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))){
  load(here::here("BAYSM_2024/Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
  GenBRMS <- FALSE
} else GenBRMS <- TRUE

```

Running the brms model for Income hierarchical model

```{r, message=FALSE, eval= GenBRMS}

Priors <- c(brms::prior(normal(500, 100), class = Intercept),
            brms::prior(normal(0, 2), class = b),
            brms::prior(cauchy(0, 10), class = sigma),
            brms::prior(cauchy(0, 2), class = sd, coef = Intercept, group= Income_Region),
            brms::prior(cauchy(0, 1), class = sd, coef = year_orig, group= Income_Region),
            brms::prior(cauchy(0, 5), class = sd, coef = Intercept, group= Country),
            brms::prior(cauchy(0, 2), class = sd, coef = year_orig, group= Country))


IncomeRegion_BRMSModel <- brms::brm(
  brms::bf(math|se(se_y, sigma = TRUE) ~ year_orig + (1 + year_orig||Income_Region)+
             (1 + year_orig||Country)),
  data = PISA_Europe_Data,
  iter = 6000, 
  prior = Priors,
  control = list(adapt_delta = 0.93), silent=2,
  chains = 4, seed = bayes_seed)

save( IncomeRegion_BRMSModel, file=here::here("BAYSM_2024/Manuscript_Models", "IncomeRegion_BRMSModel.Rdata"))
```