---
title: "Cross-checking the reading and science data for some selcetef countries"
author: "Oluwayomi Akinfenwa"
date: "11/22/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

- `pisa.Rdata` gives the result of `learningtower::load_student("all")`

```{r learningtower}
library(learningtower)
library(dplyr)

pisaFile <- here::here("SavedData", "pisa.Rdata")
if (file.exists(pisaFile)){
  load(pisaFile)
}else {
  dir.create(here::here("SavedData"))
  pisa <- learningtower::load_student("all")
  save( pisa, file=pisaFile)
}

data(countrycode)

read_pisa_data <- pisa |>
  mutate(country = recode_factor(country, "ROM" = "ROU"),
         year = as.numeric(as.character(year))) |>
  select(year, country, student_id, read, stu_wgt) |>
  summarise(read = weighted.mean(read, stu_wgt, na.rm = T), 
            .by = c(year, country)) |>
  mutate(year_orig = year - min(year))

science_pisa_data <- pisa |>
  mutate(country = recode_factor(country, "ROM" = "ROU"),
         year = as.numeric(as.character(year))) |>
  select(year, country, student_id, science, stu_wgt) |>
  summarise(science = weighted.mean(science, stu_wgt, na.rm = T), 
            .by = c(year, country)) |>
  mutate(year_orig = year - min(year))
```

The documentation for learning-tower says: 
*In the student_subset_2018 and school data, there are three common columns, school_id, country and year. It should be noted that school_id is only meaningful within a country within a specific year; meaning that when we join the two data, we need to use the keys c("school_id", "country", "year").*
So we cannot look at school data over time.

In the pisa data, Romania changes from ROM in 2000 to ROU in other years. These are all now ROU. The pisa data has 99 countries.

*The pisa_data has 433 observations from 99 countries because Romania has two country code*

### Loading the UNSD data for geographical classification of countries.

```{r regions}
UNSD <- read.csv(here::here("UNSD — Methodology.csv"))

Regions <- UNSD |> select(c("ISO.alpha3.Code","Region.Name", 
                               "Sub.region.Name"))

# left joining the UNSD with the countrycode from PISA
country_reg <- countrycode |>
  filter(country != "ROM") |>
  left_join(Regions, join_by(country == ISO.alpha3.Code))

# Renaming the variables
names(country_reg)[2] <- 'Country'
names(country_reg)[3] <- 'Continent'
names(country_reg)[4] <- 'Region'

```

*The UNSD csv file has 249 countries and 18 countries that are not in the pisa/ countrycode data are also not in this unsd data. Leaving us with 99-18 = `81 countries`*.

### Loading the income classification from the WDI package.

```{r}
library(WDI)
WDI <- WDI_data$country

WDI <- WDI |> 
  select(c("iso3c", "income")) |>
  mutate(income = recode_factor(income,
        "Lower middle income" = "Middle Income",
        "Upper middle income" = "Middle Income",
        "High income" = "High Income"))

names(WDI)[2] <- "Income"

# Joining the WDI data with the countrycode data.

countrycode_reg_inc <- country_reg |>
  left_join(WDI, join_by(country == iso3c))
```

*The WDI data has 299 countries. we observe that the same countries that are missing in the pisa_data when compared with UNSD data is also missing in the WDI data*

Hence, we proceed to joining the pisa_data with the country, region, and income information(countrycode_reg_inc).

```{r pisa_data}
pisaFileReads <- here::here("SavedData", "pisar.Rdata")
pisaFileSciences <- here::here("SavedData", "pisas.Rdata")

## Reading
Read_Pisa_Data <- read_pisa_data |>
  left_join(countrycode_reg_inc, join_by(country)) |>
  na.omit()

Read_Pisa_Data <- Read_Pisa_Data |> 
  select(-country)

## Science
Science_Pisa_Data <- science_pisa_data |>
  left_join(countrycode_reg_inc, join_by(country)) |>
  na.omit()

Science_Pisa_Data <- Science_Pisa_Data |> 
  select(-country)

save(Read_Pisa_Data, file =pisaFileReads)
save(Science_Pisa_Data, file =pisaFileSciences)
```

*The original pisa data set has 433 observations, By merging the two data set, we have 406 observations in total with 7 variables - year, math score, year_orig, country, continent, region, and income*



