---
title: "Exploratory data analysis on reading and science data"
author: "Oluwayomi Akinfenwa"
date: "23/11/2023"
output:
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
  bookdown::html_document2:
    toc: no
    toc_float: yes
    toc_depth: 4
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')
```

### Loading necessary packages

```{r, libraries, include = FALSE}
library(lme4)
library(tidybayes)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rjags)
library(R2jags)
library(bayesplot)
library(patchwork)
library(ggragged)
```

Loading the two R.data containing the learning-tower data set and the processed data with Region and Income classification.

```{r loading the data}
load(here::here("SavedData", "pisam.Rdata"))
load(here::here("SavedData", "pisar.Rdata"))
load(here::here("SavedData", "pisas.Rdata"))
```

**We have 406 observations and for this analysis, we decided to examine European countries**

### Filtering European countries alone

```{r Europe}
Math_Pisa_Europe_Data <- Pisa_Data |> filter(Continent == "Europe") |> arrange(Country)


Read_Pisa_Europe_Data <- Read_Pisa_Data |> filter(Continent == "Europe") |> arrange(Country)

Science_Pisa_Europe_Data <- Science_Pisa_Data |> filter(Continent == "Europe") |> arrange(Country)

# Joining the Income and Region together to form one new column
Math_Pisa_Europe_Data <- unite(Math_Pisa_Europe_Data, col = "Income_Region", c("Income", "Region"), sep = "_", remove = FALSE)

Read_Pisa_Europe_Data <- unite(Read_Pisa_Europe_Data, col = "Income_Region", c("Income", "Region"), sep = "_", remove = FALSE)

Science_Pisa_Europe_Data <- unite(Science_Pisa_Europe_Data, col = "Income_Region", c("Income", "Region"), sep = "_", remove = FALSE)
```

```{r}
## Obtaining the region indexes
Mcountry_region <- Math_Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

Rcountry_region <- Read_Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))

Scountry_region <- Science_Pisa_Europe_Data |> group_by(Country) |>
  summarise(Region=first(Region)) |>
  mutate(Country_num = as.numeric(as.factor(Country))) |>
  mutate(region_num = as.numeric(as.factor(Region)))
```


### Fitting lm model on reading and science data

```{r}
library(broom)
## The function reframe- creates a new data-frame by applying functions t columns of an existing data frame.

Math_model_est <-Math_Pisa_Europe_Data |>
  nest_by(Country) |>
  mutate(mod = list(lm(math ~ year_orig, data = data))) |>
  reframe(tidy(mod))|>
   select(Country, term, estimate)

Read_model_est <-Read_Pisa_Europe_Data |>
  nest_by(Country) |>
  mutate(mod = list(lm(read ~ year_orig, data = data))) |>
  reframe(tidy(mod))|>
   select(Country, term, estimate)


Science_model_est <-Science_Pisa_Europe_Data |> nest_by(Country) |>
  mutate(model = list(lm(science ~ year_orig, data = data))) |>
  reframe(tidy(model))|>
   select(Country, term, estimate)


### Tidying the estimates
 Math_Model_IS <-  Math_model_est  |>
   pivot_wider(values_from = estimate, names_from = term) |>
   rename("slope" = "year_orig") |>
  mutate(slopesign = sign(slope)) |>
  left_join(Mcountry_region, join_by(Country)) |>
  select(-c(Country_num, region_num)) |>
  arrange(slope)
  
  

 Read_Model_IS <-  Read_model_est  |>
   pivot_wider(values_from = estimate, names_from = term) |>
  rename("slope" = "year_orig") |>
  mutate(slopesign = sign(slope)) |>
  left_join(Rcountry_region, join_by(Country)) |>
  select(-c(Country_num, region_num)) |>
  arrange(slope)

 Science_Model_IS <-Science_model_est  |>
   pivot_wider(values_from = estimate, names_from = term) |>
   rename("slope" = "year_orig") |>
  mutate(slopesign = sign(slope)) |>
  left_join(Scountry_region, join_by(Country)) |>
  select(-c(Country_num, region_num)) |>
  arrange(slope)

```


**For the European countries, we have 230 observations from 40 countries.**


### Exploratory data analysis

```{r}
##Merging the slope-sign with the Pisa data so that i can rearrange by the both country and slope-sign

##Maths
M_Slopesign <-  Math_Model_IS |>
  select(Country, slope)

Math_Pisa_Europe_Data1 <- Math_Pisa_Europe_Data |>
  left_join(M_Slopesign, join_by(Country))

Math_Pisa_Europe_Data1$facet <- factor(Math_Pisa_Europe_Data1$Region, 
                  levels = c("Western Europe", "Eastern Europe", "Northern Europe", "Southern Europe"))

Math_Model_IS$facet <- factor(Math_Model_IS$Region, 
                  levels = c("Western Europe", "Eastern Europe", "Northern Europe", "Southern Europe"))

##Reads
R_Slopesign <-  Read_Model_IS |>
  select(Country, slope)

Read_Pisa_Europe_Data1 <- Read_Pisa_Europe_Data |>
  left_join(R_Slopesign, join_by(Country))

Read_Pisa_Europe_Data1$facet <- factor(Read_Pisa_Europe_Data1$Region, 
                  levels = c("Western Europe", "Eastern Europe", "Northern Europe", "Southern Europe"))

Read_Model_IS$facet <- factor(Read_Model_IS$Region, 
                  levels = c("Western Europe", "Eastern Europe", "Northern Europe", "Southern Europe"))


##Science
S_Slopesign <-  Science_Model_IS |>
  select(Country, slope)

Science_Pisa_Europe_Data1 <- Science_Pisa_Europe_Data |>
  left_join(S_Slopesign, join_by(Country))

Science_Pisa_Europe_Data1$facet <- factor(Science_Pisa_Europe_Data1$Region, 
                  levels = c("Western Europe", "Eastern Europe", "Northern Europe", "Southern Europe"))

Science_Model_IS$facet <- factor(Science_Model_IS$Region, 
                  levels = c("Western Europe", "Eastern Europe", "Northern Europe", "Southern Europe"))
```


### The plot

```{r}
pdf("Math.fit.pdf",
    width = 12,
    height = 8)
ggplot(data = Math_Pisa_Europe_Data1,
         aes(x=year_orig, y=math))+
  geom_point(color = "grey25")+
   geom_abline(data=Math_Model_IS, 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  facet_ragged_rows(vars(facet), vars(reorder(Country, slope)),scales = "free_y",
                    switch = "y", labeller=label_wrap_gen(width=6))+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  scale_y_continuous(position = "right")+
   labs(x= " ", y = " ",  color = "Slope") + scale_color_manual(values = c("maroon", "blue3"), labels = c("negative", "positive"), na.translate = F)+
  theme(legend.position = "bottom",
        plot.subtitle = element_text(family = "Serif"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, face = "bold"),strip.text.x = element_text(size = 9,face = "bold"),
        axis.text.y = element_text(size = 9,face = "bold"))+
  ggtitle("Separate linear model fit on average math scores across the country")
dev.off()
```

```{r}
pdf("Read.fit.pdf",
    width = 12,
    height = 8)
ggplot(data = Read_Pisa_Europe_Data1,
         aes(x=year_orig, y=read))+
  geom_point(color = "grey25")+
   geom_abline(data=Read_Model_IS, 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  facet_ragged_rows(vars(facet), vars(reorder(Country, slope)),scales = "free_y",
                    switch = "y", labeller=label_wrap_gen(width=6))+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  scale_y_continuous(position = "right")+
   labs(x= " ", y = " ",  color = "Slope") + scale_color_manual(values = c("maroon", "blue3"), labels = c("negative", "positive"), na.translate = F)+
  theme(legend.position = "bottom",
        plot.subtitle = element_text(family = "Serif"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, face = "bold"),strip.text.x = element_text(size = 9,face = "bold"),
        axis.text.y = element_text(size = 9,face = "bold"))+
  ggtitle("Separate linear model fit on average reading scores across the country")
dev.off()
```

```{r}
pdf("Science.fit.pdf",
    width = 12,
    height = 8)
ggplot(data = Science_Pisa_Europe_Data1,
         aes(x=year_orig, y=science))+
  geom_point(color = "grey25")+
   geom_abline(data=Science_Model_IS, 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  facet_ragged_rows(vars(facet), vars(reorder(Country, slope)),scales = "free_y",
                    switch = "y", labeller=label_wrap_gen(width=6))+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  scale_y_continuous(position = "right")+
   labs(x= " ", y = " ",  color = "Slope") + scale_color_manual(values = c("maroon", "blue3"), labels = c("negative", "positive"), na.translate = F)+
  theme(legend.position = "bottom",
        plot.subtitle = element_text(family = "Serif"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, face = "bold"),strip.text.x = element_text(size = 9,face = "bold"),
        axis.text.y = element_text(size = 9,face = "bold"))+
  ggtitle("Separate linear model fit on average Science scores across the country")
dev.off()
```

### Filter out Germany, Liechtenstein, Luxembourg, and United Kingdom.

```{r}
Q <- c("Germany", "Liechtenstein", "Luxembourg", "United Kingdom")

M <- ggplot(data = filter(Math_Pisa_Europe_Data1, Country %in% Q),
         aes(x=year_orig, y=math))+
  geom_point(color = "grey25")+
   geom_abline(data=filter(Math_Model_IS, Country %in% Q), 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  facet_wrap(~Country, scales = "free_y")+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  scale_y_continuous(position = "right")+
   labs(x= " ", y = " ",  color = "Slope") + scale_color_manual(values = c("maroon", "blue3"), labels = c("negative", "positive"), na.translate = F)+
  theme(legend.position = "none",
        plot.subtitle = element_text(family = "Serif"),
        plot.title = element_text(size = 9,face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, face = "bold"),strip.text.x = element_text(size = 9,face = "bold"),
        axis.text.y = element_text(size = 8,face = "bold"))+
  ggtitle("lm fit on average math scores")

R <- ggplot(data = filter(Read_Pisa_Europe_Data1, Country %in% Q),
         aes(x=year_orig, y=read))+
  geom_point(color = "grey25")+
   geom_abline(data=filter(Read_Model_IS, Country %in% Q), 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  facet_wrap(~Country, scales = "free_y")+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  scale_y_continuous(position = "right")+
   labs(x= " ", y = " ",  color = "Slope") + scale_color_manual(values = c("maroon", "blue3"), labels = c("negative", "positive"), na.translate = F)+
  theme(legend.position = "none",
        plot.subtitle = element_text(family = "Serif"),
        plot.title = element_text(size = 9,face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, face = "bold"),strip.text.x = element_text(size = 9,face = "bold"),
        axis.text.y = element_text(size = 8,face = "bold"))+
  ggtitle("lm fit on average reading scores")

S <- ggplot(data = filter(Science_Pisa_Europe_Data1, Country %in% Q),
         aes(x=year_orig, y=science))+
  geom_point(color = "grey25")+
   geom_abline(data=filter(Science_Model_IS, Country %in% Q), 
               aes(slope=slope, intercept= `(Intercept)`,color = factor(slopesign)))+
  facet_wrap(~Country, scales = "free_y")+
  scale_x_continuous(labels = function(x) x+2000, breaks = seq(0,18,3))+
  scale_y_continuous(position = "right")+
   labs(x= " ", y = " ",  color = "Slope") + scale_color_manual(values = c("maroon", "blue3"), labels = c("negative", "positive"), na.translate = F)+
  theme(legend.position = "none",
        plot.subtitle = element_text(family = "Serif"),
        plot.title = element_text(size = 9,face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5, face = "bold"),strip.text.x = element_text(size = 9,face = "bold"),
        axis.text.y = element_text(size = 8,face = "bold"))+
  ggtitle("lm on average science scores")

M+R+S
```

